### 2018-09-09 article.tex
Initial commit.

\documentclass[a4paper,11pt]{article}

\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[ansinew]{inputenc}
\usepackage{bbold}
\usepackage{bold-extra}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{tkz-berge}
\usepackage{amsfonts}
\usepackage{gensymb}
\usepackage{mathtools}
\usepackage{subfigure}
\usepackage{theorem}
\usepackage{bm}
\usepackage{xcolor}
\usepackage[unicode]{hyperref}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{lipsum}
\usetikzlibrary{positioning}
\usepackage{tikz}
\usepackage{empheq}
\usepackage{booktabs}
\usepackage{authblk}
\usetikzlibrary{arrows,shapes}
\usetikzlibrary{arrows}

%\usepackage{3dplot} %requires 3dplot.sty to be in same directory, or in your LaTeX installation
%\usepackage{amsmath,amsfonts,amssymb,amsthm,epsfig,epstopdf,titling,url,array}
\usepackage{xstring}

%\theoremstyle{definition}
%\newtheorem{defn}{Definition}[section]
%\newtheorem{conj}{Conjecture}[section]
%\newtheorem{exmp}{Example}[section]
\makeatletter
\newcommand{\change@uppercase@math}{%
  \count@=`\A
  \loop
    \mathcode\count@\count@
    \ifnum\count@<`\Z
    \advance\count@\@ne
  \repeat}

\newcommand{\LSTM}[1]{
  \mathrm{LSTM}(
  %(\begingroup\change@uppercase@math#1\endgroup)
}

\newcommand{\ENC}[1]{
  \mathrm{ENC}(
  %(\begingroup\change@uppercase@math#1\endgroup)
}

\newcommand{\DEC}[1]{
  \mathrm{DEC}(
  %(\begingroup\change@uppercase@math#1\endgroup)
}

\newcommand{\UPDATE}[1]{
  \mathrm{UPDATE}(
  %(\begingroup\change@uppercase@math#1\endgroup)
}

\newcommand{\READ}[1]{
  \mathrm{READ}(
 % (\begingroup\change@uppercase@math#1\endgroup)
}

\newcommand{\CIRC}[1]{
  \mathrm{circ}(
 % (\begingroup\change@uppercase@math#1\endgroup)
}

\newcommand{\RNN}[1]{
  \mathrm{RNN}(
 % (\begingroup\change@uppercase@math#1\endgroup)
}

\newcommand{\ReLU}[1]{
  \mathrm{ReLU}(
 % (\begingroup\change@uppercase@math#1\endgroup)
}

\newcommand{\softmax}[1]{
  \mathrm{softmax}(
 % (\begingroup\change@uppercase@math#1\endgroup)
}

\makeatother

\newcommand*\GetListMember[2]{\StrBetween[#2,\number\numexpr#2+1]{,#1,},,\par}%
\newcommand{\tikzmark}[1]{\tikz[overlay,remember picture] \node (#1) {};}

\def\spvec#1{\left(\vcenter{\halign{\hfil$##$\hfil\cr \spvecA#1;;}}\right)}
\def\spvecA#1;{\if;#1;\else #1\cr \expandafter \spvecA \fi}

\newlength{\MidRadius}
\newcommand*{\CircularSequence}[3]{%
    % #1 = outer circle radius
    % #2 = inner circle radius
    % #3 = seqeunce
    \StrCount{#3}{,}[\NumberOfElements]
    \pgfmathsetmacro{\AngleSep}{360/(\NumberOfElements+1)}
    \pgfmathsetlength{\MidRadius}{(#1+#2)/2}
    \draw [red,  ultra thick] circle (#2);
    \draw [blue, ultra thick] circle (#1);
%    \draw [thick,->] (0, 0) -- (1.0, 0);
%    \draw [thick,->] (0, 0) -- (0.0, 1.0);
    \foreach [count = \Count] \Angle in {0,\AngleSep,..., 360} {%
        \draw [gray, ultra thick] (\Angle:#2) -- (\Angle:#1);
        \pgfmathsetmacro{\MidPoint}{\Angle+\AngleSep/2}
        \node at (\MidPoint:\MidRadius) {\GetListMember{#3}{\Count}};
    }%7
}%

\author{Povilas Daniu\v{s}is, Audrius Indriulionis, Andrius Budrionis}

\title{Computer Vision-based System for Blinds and Visually Impaired}

\begin{document}
\pgfdeclarelayer{background}
\pgfsetlayers{background,main}

\maketitle

\section{Introduction}

According to \cite{Bourne} more than $250$ million persons have moderate to severe vision impairment ($\approx 36$ million are blind). During past decades significant effort was devoted by various authors to develop computer vision and other sensor based aids (e.g. \cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara}) for helping the blind and visually impaired users to perceive the world around. However, computer vision is rapidly evolving field, and systems based on aforementioned approaches often lack accuracy and reliability in real-world conditions. In this article we describe system, which allow to use are modern computer vision methods for compensation of lost or impaired vision function in humans. We assume that mobile device equivalent or very similar to smartphone is used by the visually impaired person to perceive visual information from the environment. Since most of computer vision algorithms require rather intensive computational power exceeding than that of smartphone, we also assume that image processing itself is conducted in separate machine, connected to the mobile device via Internet, and calculated audio or tactile feedback signal is transmited to the mobile device for presentation to the user.

\section{Method}

\section{System}

\section{Discussion}

\begin{thebibliography}{1}

\bibitem{Bourne} Bourne RRA, Flaxman SR, Braithwaite T, Cicinelli MV, Das A, Jonas JB, et al.; Vision Loss Expert Group. Magnitude, temporal trends, and projections of the global prevalence of blindness and distance and near vision impairment: a systematic review and meta-analysis. Lancet Glob Health.  2017 Sep;5(9):e888-97.

\bibitem{Caraiman} Caraiman, S., Morar, A., Owczarek, M.,Burlacu, A., Rzeszotarski, D., Botezatu, N., Herghelegiu, P., Moldoveanu, F., Strumillo, P., Moldoveanu, A. Computer Vision for the Visually Impaired: the Sound of Vision System. IEEE International Conference on Computer Vision Workshops, pp. 1480-1489, 2017.
\bibitem{Csapo} Csap\'{o}, A., Wers\'{e}nyi, G., Nagy, H., Stockman, T. A survey of assistive technologies and applications for blind users on mobile platforms: a review and foundation for research. Journal on Multimodal User Interfaces. Vol. 9, issule 4,  pp. 275-286, 2015.
\bibitem{Poggi} Poggi, M., Mattoccia, S. A wearable mobility aid for the visually impaired based on embedded 3d vision and deep learning. Proceeding of IEEE Symposium on Compututers and Communication, pp. 208-213, 2016.
\bibitem{Zientara} Zientara, P.,A., Lee, S., Smith, G., H., Brenner, R., Itti, L., Rosson M., B., Carroll, J., M., Irick K., M., Narayanan, V. Third Eye: A shopping assistant for the visually impaired. Computer Vol. 50, Issue 2, pp. 16-24, 2017.

\end{thebibliography}

\end{document}

### 2018-09-09 article.tex
small fix.

@@
 However, computer vision is rapidly evolving field, and systems based on aforementioned approaches often lack accuracy and reliability in real-world conditions.
-In this article we describe system, which allow to use are modern computer vision methods for compensation of lost or impaired vision function in humans.
+In this article we describe realistic system, which allow to use are modern computer vision methods for compensation of lost or impaired vision function in humans.
 We assume that mobile device equivalent or very similar to smartphone is used by the visually impaired person to perceive visual information from the environment.

### 2018-09-13 article.tex
some input.

--- 2018-09-09 article.tex
@@
 However, computer vision is rapidly evolving field, and systems based on aforementioned approaches often lack accuracy and reliability in real-world conditions.
-In this article we describe system, which allow to use are modern computer vision methods for compensation of lost or impaired vision function in humans.
-We assume that mobile device equivalent or very similar to smartphone is used by the visually impaired person to perceive visual information from the environment.
+In this article we describe realistic system, which allow to use modern computer vision methods for compensation of lost or impaired vision function in humans.
+We assume that mobile device equivalent or very similar to smartphone is used to perceive visual information from the environment.
 Since most of computer vision algorithms require rather intensive computational power exceeding than that of smartphone, we also assume that image processing itself is conducted in separate machine, connected to the mobile device via Internet, and calculated audio or tactile feedback signal is transmited to the mobile device for presentation to the user.

### 2018-09-13 article.tex
update.

@@
 \usetikzlibrary{arrows}
+\usepackage{pdfpages}
+\usepackage{wrapfig}
 
@@
 
-\title{Computer Vision-based System for Blinds and Visually Impaired}
+\title{Computer Vision-based System for Impaired Human Vision Compensation}
 
@@
 In this article we describe realistic system, which allow to use modern computer vision methods for compensation of lost or impaired vision function in humans.
-We assume that mobile device equivalent or very similar to smartphone is used to perceive visual information from the environment.
-Since most of computer vision algorithms require rather intensive computational power exceeding than that of smartphone, we also assume that image processing itself is conducted in separate machine, connected to the mobile device via Internet, and calculated audio or tactile feedback signal is transmited to the mobile device for presentation to the user.
+We assume that mobile device equivalent or very similar to smartphone is used by the visually impaired person to perceive visual information from the environment by inbuilt or auxiliary cameras.
+Since most of computer vision algorithms require rather intensive computational power exceeding than that of smartphone, we also assume that image processing itself can be conducted in separate machine, connected to the mobile device via Internet, and calculated audio or tactile feedback signal is transmited to the mobile device for presentation to the user.
+%Such a set up is realistic in urban areas, where population.
 
 \section{Method}
+\label{sec:method}
 
+\newpage
 \section{System}
+\label{sec:system}
+
+\begin{wrapfigure}{r}{0.4\textwidth}
+  \begin{center}
+    \includegraphics[scale=0.7]{./img/diagram.pdf}  
+  \end{center}
+  \caption{Schematics of FRP device.}
+  \label{fig:schematics}
+\end{wrapfigure}
+
+Following the above methodology we suggest impaired human vision compensation system (\textbf{HVCS}), consisting of \textbf{Device} and \textbf{Inference} components (see Fig.~\ref{fig:schematics}).
+
+\textbf{Device} subsystem is continuously carried by the user.
+It consists of sensors and actuators, integrated into smartphone-based computation core, which was chosen due its avialability to wide population, and capability to carry out required computations or forward them to external server via Internet connection.
+Sensors are mounted forehead belt include: RGB camera, depth camera, IMU.
+Actuator set consists of bone conductive headphones, and head belt for presenting tactile-feedback to the user.
+%We suggest to use bone conductive headphones, ...
+
+\textbf{Inference} subsystem consists of server computer with internet connection and set of computer vision algorithms, selected according to our methodology (see.
+Sec.~\ref{sec:method}): Faster RCNN object detector \cite{?}, trained to detect important objects (doors, floors, elevators,...), CNN-RNN-based scene description \cite{?}, place recognition \cite{?}, face recognition \cite{?}, obstacle detection \cite{?}, and possibly other modules.
+
+HVCS operation cycle is started by \textbf{Device} reading sensor data and transmitting it to the server for an analysis.
+Server calculates feedback signal and transmits it back to the device for presenting to the user.
 
 \section{Discussion}
+\label{sec:discussion}
+
+In this article we outlined an idea of computer vision-based sensor, which can help to partially compensate impaired or lost human sight.
 

### 2018-09-14 article.tex
Update article.tex
Smart Device Diagram was updated

@@
 
+According to \cite{Bourne} more than $250$ million persons have moderate to severe vision impairment ($\approx 36$ million are blind).
+During past decades significant effort was devoted by various authors to develop computer vision and other sensor based aids (e.g.
+\cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara}) for helping the blind and visually impaired users to perceive the world around.
+However, computer vision is rapidly evolving field, and systems based on aforementioned approaches often lack accuracy and reliability in real-world conditions.
+In this article we describe realistic system, which allow to use modern computer vision methods for compensation of lost or impaired vision function in humans.
+We assume that mobile device equivalent or very similar to smartphone is used to perceive visual information from the environment.
+Since most of computer vision algorithms require rather intensive computational power exceeding than that of smartphone, we also assume that image processing itself is conducted in separate machine, connected to the mobile device via Internet, and calculated audio or tactile feedback signal is transmited to the mobile device for presentation to the user.
+
 \section{Method}
@@
   \begin{center}
-    \includegraphics[scale=0.7]{./img/diagram.pdf}  
+    \includegraphics[scale=0.7]{./img/SmartDevice_diagram.pdf}  
   \end{center}
@@
 \textbf{Inference} subsystem consists of server computer with internet connection and set of computer vision algorithms, selected according to our methodology (see.
-Sec.~\ref{sec:method}): Faster RCNN object detector \cite{?}, trained to detect important objects (doors, floors, elevators,...), CNN-RNN-based scene description \cite{?}, place recognition \cite{?}, face recognition \cite{?}, obstacle detection \cite{?}, and possibly other modules.
+Sec.~\ref{sec:method}): Faster RCNN object detector \cite{?}, trained to detect important objects (doors, floors, elevators,...), CNN-RNN-based scene description \cite{Liu},\cite{Ren}, \cite{Dai}, place recognition \cite{Ohn-Bar}, face recognition \cite{Amos}, obstacle detection \cite{Laina}, and possibly other modules.
 
@@
 In this article we outlined an idea of computer vision-based sensor, which can help to partially compensate impaired or lost human sight.
+The developed head mounted tactile device is deveolped for head position and orientation tracking and could capture an image in front of visually impaired people.
+The tactile device with integrated 3D deph camera is integrated with smartphone by bluetooth which could preprocess the labeled image features.
+The developed high quality self navigation system is based on the computer vision methods especially enhancing the capabilities to detect and classify objects (e.g bus station, street crossings, ) with their surrounding objects.
+The authors expect to increase the capabilies of potentially blind to secure navigate especially for the planed destination (e.g.
+"home-office").
 
 \begin{thebibliography}{1}
+\bibitem{Amos} Amos, B., Ludwiczuk, B., and Satyanarayanan, M. Openface:
+A general-purpose face recognition library with mobile applications. Technical report, CMU-CS-16-118, CMU School of Computer Science, 2016.
 
@@
 275-286, 2015.
+\bibitem{Dai} Dai, J., Li, Y., He, K., Sun J. R-FCN: Object Detection via Region-based Fully Convolutional Networks. In Advances in neural information processing systems, pp. 379-387, 2016.
 \bibitem{Poggi} Poggi, M., Mattoccia, S.
@@
 16-24, 2017.
+\bibitem{Liu} Liu, Ch., Mao, J., Sha, F., Yuille, A. Attention Correctness in Neural Image Captioning. Proceedings of the Thirty-First AAAI Conference on Artificial Intelligence, pp. 4176-4182, 2017.
+\bibitem{Laina} Laina, I., Rupprecht, C., Belagiannis, V., Tombari, F., Navab, N.
+Deeper depth prediction with fully convolutional residual networks.
+Fourth International Conference on 3D Vision (3DV), pp.
+239-248, 2016.
+\bibitem{Ohn-Bar}  Ohn-Bar, E., Kitani, K., Asakawa, Ch. Personalized Dynamics Models for Adaptive Assistive Navigation Interfaces. arXiv:1804.04118, [cs.LG], 2018.
+\bibitem{Ren} Ren, Sh., He, K., Girshick, R., and Sun, J.
+Faster R-CNN: Towards real-time object detection with region proposal networks.
+In Advances in neural information processing systems, pp.
+91-99, 2015.
 

### 2018-09-16 article.tex
Method section added

@@
 \label{sec:method}
+Following the principles of participatory design \cite{Kensing}, \cite{Carroll} we included the final users into the design process of the system.
+Two visually impaired persons participated in discussion and focus group meetings together with the project team to identify the key properties of the solution.
+During the six discussion sessions major attention was paid to:
+\begin{enumerate}
+\item Functionality and key features of the solution addressing real-life scenarios of visually impaired persons;
+\item Technical feasibility, connecting user needs to the latest development in computer vision and assisted technologies;
+\item Interface between the visually impaired person and the assisted technology;
+\item Appearance, usability and potential costs of the final product. 
+\end{enumerate}
+Design process involved testing of the existing technological solutions (mobile phone apps) for assisting visually impaired persons {\color{red}(which ones have we tested?)}.
+Semi-structured tests were performed by the visually impaired participants accompanied by a researcher from a project group.
+Strengths and weaknesses of the existing solutions are reflected in the design of the proposed system.
 
 \newpage
+%patarciau skyreli vadint "Results" o ne "System".
 \section{System}
@@
 
+\bibitem{Kensing} Kensing, F., Simonsen, J., and Bødker, K. MUST: A Method for Participatory Design. Hum-Comput Interact, vol. 13, no. 2, pp. 167–198, Jun. 1998.
+
+\bibitem{Carroll} Carroll, J. M., Rosson, M. B. Participatory design in community informatics. Des. Stud., vol. 28, no. 3, pp. 243–261, May 2007.
+
 \end{thebibliography}

### 2018-09-20 article.tex
small changes.

@@
 In this article we describe realistic system, which allow to use modern computer vision methods for compensation of lost or impaired vision function in humans.
-We assume that mobile device equivalent or very similar to smartphone is used by the visually impaired person to perceive visual information from the environment by inbuilt or auxiliary cameras.
+The article is organized as follows: in Section~\ref{sec:method} we describe our method, Section~\ref{sec:results} contains schematic and description of human vision compensation system (HVCS), which is the result of this research, and Section~\ref{sec:discussion} is devoted for the discussion.
+
+%We assume that mobile device equivalent or very similar to smartphone is used by the visually impaired person to perceive visual information from the environment by inbuilt or auxiliary cameras.
 Since most of computer vision algorithms require rather intensive computational power exceeding than that of smartphone, we also assume that image processing itself can be conducted in separate machine, connected to the mobile device via Internet, and calculated audio or tactile feedback signal is transmited to the mobile device for presentation to the user.
-%Such a set up is realistic in urban areas, where population.
 
-According to \cite{Bourne} more than $250$ million persons have moderate to severe vision impairment ($\approx 36$ million are blind).
+%According to \cite{Bourne} more than $250$ million persons have moderate to severe vision impairment ($\approx 36$ million are blind).
 During past decades significant effort was devoted by various authors to develop computer vision and other sensor based aids (e.g.
@@
 \label{sec:method}
+
 Following the principles of participatory design \cite{Kensing}, \cite{Carroll} we included the final users into the design process of the system.
@@
 
-\newpage
+%\newpage
 %patarciau skyreli vadint "Results" o ne "System".
-\section{System}
-\label{sec:system}
+\section{Results}
+\label{sec:results}
 
@@
   \begin{center}
-    \includegraphics[scale=0.7]{./img/SmartDevice_diagram.pdf}  
+    \includegraphics[scale=0.7]{./img/cropped_diagram.pdf}  
   \end{center}
@@
 It consists of sensors and actuators, integrated into smartphone-based computation core, which was chosen due its avialability to wide population, and capability to carry out required computations or forward them to external server via Internet connection.
-Sensors are mounted forehead belt include: RGB camera, depth camera, IMU.
+Sensors are mounted on forehead belt include: RGB camera, depth camera, IMU.
 Actuator set consists of bone conductive headphones, and head belt for presenting tactile-feedback to the user.
@@
 \textbf{Inference} subsystem consists of server computer with internet connection and set of computer vision algorithms, selected according to our methodology (see.
-Sec.~\ref{sec:method}): Faster RCNN object detector \cite{?}, trained to detect important objects (doors, floors, elevators,...), CNN-RNN-based scene description \cite{Liu},\cite{Ren}, \cite{Dai}, place recognition \cite{Ohn-Bar}, face recognition \cite{Amos}, obstacle detection \cite{Laina}, and possibly other modules.
+Sec.~\ref{sec:method}): Faster RCNN object detector \cite{?}, trained to detect important objects (doors, floors, elevators, stairs, corridor junctions, etc.), CNN-RNN-based scene description \cite{Liu},\cite{Ren}, \cite{Dai}, place recognition \cite{Ohn-Bar}, face recognition \cite{Amos}, obstacle detection \cite{Laina}, and possibly other modules.
 
@@
 "home-office").
+
+Work left (outdoor/indoor) etc.
 
@@
 
-\bibitem{Kensing} Kensing, F., Simonsen, J., and Bødker, K. MUST: A Method for Participatory Design. Hum-Comput Interact, vol. 13, no. 2, pp. 167–198, Jun. 1998.
+\bibitem{Kensing} Kensing, F., Simonsen, J., and B\o dker, K. MUST: A Method for Participatory Design. Hum-Comput Interact, vol. 13, no. 2, pp. 167-198, Jun. 1998.
 
-\bibitem{Carroll} Carroll, J. M., Rosson, M. B. Participatory design in community informatics. Des. Stud., vol. 28, no. 3, pp. 243–261, May 2007.
+\bibitem{Carroll} Carroll, J. M., Rosson, M. B. Participatory design in community informatics. Des. Stud., vol. 28, no. 3, pp. 243-261, May 2007.
 

### 2018-09-23 article.tex
Some changes to the content, mostly Introduction. I made several comments on Results and Discussion. Please take a look at them

@@
 
-According to \cite{Bourne} more than $250$ million persons have moderate to severe vision impairment ($\approx 36$ million are blind).
-During past decades significant effort was devoted by various authors to develop computer vision and other sensor based aids (e.g.
-\cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara}) for helping the blind and visually impaired users to perceive the world around.
-However, computer vision is rapidly evolving field, and systems based on aforementioned approaches often lack accuracy and reliability in real-world conditions.
-In this article we describe realistic system, which allow to use modern computer vision methods for compensation of lost or impaired vision function in humans.
-The article is organized as follows: in Section~\ref{sec:method} we describe our method, Section~\ref{sec:results} contains schematic and description of human vision compensation system (HVCS), which is the result of this research, and Section~\ref{sec:discussion} is devoted for the discussion.
+More than $250$ million poople worldwide have moderate to severe vision impairment, while ($\approx 36$ million are blind) \cite{Bourne}.
+During the past decades significant effort was devoted to develop computer vision and other sensor based aids (e.g.
+\cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara}) for helping the blind and visually impaired users to perceive the surrounding world.
+However, computer vision is rapidly evolving field, and systems based on the aforementioned approaches often lack accuracy and reliability in real-world conditions.
+In this article we describe a system, which employs modern computer vision techniques for compensation of lost or impaired vision function in humans.
+Many of the previuosly proposed electronic aids for the blind count on highly specialised hardware, for instance smart glassess \cite{Zientara}, Microsoft Kinnect sensors \cite{Owayjan}, helmet-mounted photosensors and cameras \cite{Larisa}.
+Such advanced and costly technology brings additional complexity into daily tasks, which visually impaired people currently manage by the help of the white cane.
+This project puts major emphasis on developing a tool, which seamlesly integrates with the hardware visually impaired person already has on-hand and is used to (smartphone).
+This paper describes the high level architecture of the proposed technology aid for visually impaired people.
+
+%The article is organized as follows: in Section~\ref{sec:method} we describe our method, Section~\ref{sec:results} presents the schematic description of human vision compensation system (HVCS).
+Limitations and further implications of the proposed system are discussed in the Section~\ref{sec:discussion}.
 
@@
 
-%\newpage
-%patarciau skyreli vadint "Results" o ne "System".
 \section{Results}
@@
 
-Following the above methodology we suggest impaired human vision compensation system (\textbf{HVCS}), consisting of \textbf{Device} and \textbf{Inference} components (see Fig.~\ref{fig:schematics}).
+Following the above methodology we suggest the impaired human vision compensation system (\textbf{HVCS}), consisting of \textbf{Device} and \textbf{Inference} components (see Fig.~\ref{fig:schematics}).
 
-\textbf{Device} subsystem is continuously carried by the user.
-It consists of sensors and actuators, integrated into smartphone-based computation core, which was chosen due its avialability to wide population, and capability to carry out required computations or forward them to external server via Internet connection.
+%padalijimas i 2 komponentus man nelabai aiskus. As dalinciau i input (kameros, sensoriai), output (ausines, vibratoriu matricos), processing (local, remote). 
+% tai kas dabar yra prie Inference, siulau perprazuot kaip Functionality, ka as minejau Method.
+Taip pat visa Results skyreli reiktu labiau susiet su Method.
+Reiktu, kad visi 4 Method pamineti punktai isrysketu ir Results.
+%Results skyrelyje nereiktu taip stipriai fokusuotis i kitu grupiu tyrimus ir juos cituoti. Rezultatai juk musu.
+\textbf{Device} subsystem is a computational device the user currently uses for completing other daily tasks.
+It consists of sensors and actuators, integrated into smartphone-based computation core, which was chosen due its avialability to wide population, and capability to perform the required computations or forward visual information to the external server via Internet connection.
 Sensors are mounted on forehead belt include: RGB camera, depth camera, IMU.
@@
 \label{sec:discussion}
+%Didzioji Discussion teksto dalis man labiau tinka prie Results/Conclusion.
+Gal galim padiskutioti daugiau apie Limitations, Future Implications, Lessons Learned ar pan...
+Cia galime savo siuloma sistema lyginti su anksciau publikuotais rezultatais.
 
 In this article we outlined an idea of computer vision-based sensor, which can help to partially compensate impaired or lost human sight.
-The developed head mounted tactile device is deveolped for head position and orientation tracking and could capture an image in front of visually impaired people.
+The developed head-mounted tactile device is developed for head position and orientation tracking and could capture an image in front of visually impaired people.
 The tactile device with integrated 3D deph camera is integrated with smartphone by bluetooth which could preprocess the labeled image features.
@@
 
+\bibitem{Owayjan} Owayjan, M., Hayek, A., Nassrallah, H., Eldor, M.
+Smart Assistive Navigation System for Blind and Visually Impaired Individuals.
+2015 International Conference on Advances in Biomedical Engineering (ICABME), 2015.
+
+\bibitem{Larisa} Dunai, L.
+D., Lengua, I.
+L., Tortajada, I., Brusola Simon, F.
+Obstacle detectors for visually impaired people.
+2014 International Conference on Optimization of Electrical and Electronic Equipment (OPTIM), 2014.
+
 \end{thebibliography}

### 2018-09-25 bare_conf.tex
IEEE style added.

%% bare_conf.tex
%% V1.3
%% 2007/01/11
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%
%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices can trigger bugs that do  ***
% *** not appear when using other class files.                            ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[10pt,conference,compsocconf]{IEEEtran}
%\documentclass[10pt]{IEEEtran}
\usepackage{times}
\usepackage{color}
\usepackage{caption}
\usepackage{graphicx}

\captionsetup{font=footnotesize,justification=centering,labelsep=period}

% Add the compsoc option for Computer Society conferences.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

%\usepackage{mdwmath}
%\usepackage{mdwtab}
% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
% especially mdwmath.sty and mdwtab.sty which are used to format equations
% and tables, respectively. The MDWtools set is already installed on most
% LaTeX systems. The lastest version and documentation is available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

%\usepackage{eqparbox}
% Also of notable interest is Scott Pakin's eqparbox package for creating
% (automatically sized) equal width boxes - aka "natural width parboxes".
% Available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/

% *** SUBFIGURE PACKAGES ***
%\usepackage[tight,footnotesize]{subfigure}
% subfigure.sty was written by Steven Douglas Cochran. This package makes it
% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
% work, it is a good idea to load it with the tight package option to reduce
% the amount of white space around the subfigures. subfigure.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at:
% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
% subfigure.sty has been superceeded by subfig.sty.

%\usepackage[caption=false]{caption}
%\usepackage[font=footnotesize]{subfig}
% subfig.sty, also written by Steven Douglas Cochran, is the modern
% replacement for subfigure.sty. However, subfig.sty requires and
% automatically loads Axel Sommerfeldt's caption.sty which will override
% IEEEtran.cls handling of captions and this will result in nonIEEE style
% figure/table captions. To prevent this problem, be sure and preload
% caption.sty with its "caption=false" package option. This is will preserve
% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
% (recommended due to many improvements over 1.2) of subfig.sty supports
% the caption=false option directly:
%\usepackage[caption=false,font=footnotesize]{subfig}
%
% The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
% The latest version and documentation of caption.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Documentation is contained in the stfloats.sty comments as well as in the
% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
% does not allow \baselineskip to stretch. Authors submitting work to the
% IEEE should note that IEEE rarely uses double column equations and
% that authors should try to avoid such use. Do not be tempted to use the
% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
% not format its papers in such ways.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
% Read the url.sty source comments for usage information. Basically,
% \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

%\parskip 6pt plus 2pt minus 1pt
\parskip 3pt plus 2pt minus 1pt

\pagestyle{empty}
\begin{document}
\pagenumbering{gobble}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{\textbf{\Large Computer Vision-based System for Impaired Human Vision Compensation}} % \\[-1.5ex] and subtitle}\\[0.2ex]}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{~\\[-0.4ex]\large Michael Shell\\[0.3ex]\normalsize}
\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
Georgia Institute of Technology\\
Atlanta, Georgia 30332--0250\\
Email: {\tt ...}}
\and
\IEEEauthorblockN{~\\[-0.4ex]\large Homer Simpson\\[0.3ex]\normalsize}
\IEEEauthorblockA{Twentieth Century Fox\\
Springfield, USA\\
Email: {\tt homer@thesimpsons.com}}
\and
\IEEEauthorblockN{~\\[-0.4ex]\large James Kirk\\ and Montgomery Scott\\[0.3ex]\normalsize}
\IEEEauthorblockA{Starfleet Academy\\
San Francisco, California 96678-2391\\
Telephone: (800) 555--1212\\
Fax: (888) 555--1212}}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

\begin{abstract}
%\boldmath
The abstract goes here.
The abstract goes here.
The abstract goes here.
The abstract goes here.
The abstract goes here.
The abstract goes here.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

% no keywords

\begin{IEEEkeywords}
Anything; Something; Everything else.%
\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
\label{sec:introduction}

More than $250$ million poople worldwide have moderate to severe vision impairment, while ($\approx 36$ million are blind) \cite{Bourne}. During the past decades significant effort was devoted to develop computer vision and other sensor based aids (e.g. \cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara}) for helping the blind and visually impaired users to perceive the surrounding world. However, computer vision is rapidly evolving field, and systems based on the aforementioned approaches often lack accuracy and reliability in real-world conditions. In this article we describe a system, which employs modern computer vision techniques for compensation of lost or impaired vision function in humans. Many of the previuosly proposed electronic aids for the blind count on highly specialised hardware, for instance smart glassess \cite{Zientara}, Microsoft Kinnect sensors \cite{Owayjan}, helmet-mounted photosensors and cameras \cite{Larisa}. Such advanced and costly technology brings additional complexity into daily tasks, which visually impaired people currently manage by the help of the white cane. This project puts major emphasis on developing a tool, which seamlesly integrates with the hardware visually impaired person already has on-hand and is used to (smartphone). This paper describes the high level architecture of the proposed technology aid for visually impaired people.

\section{Method}
\label{sec:method}

Following the principles of participatory design \cite{Kensing}, \cite{Carroll} we included the final users into the design process of the system. Two visually impaired persons participated in discussion and focus group meetings together with the project team to identify the key properties of the solution. During the six discussion sessions major attention was paid to:
\begin{enumerate}
\item Functionality and key features of the solution addressing real-life scenarios of visually impaired persons;
\item Technical feasibility, connecting user needs to the latest development in computer vision and assisted technologies;
\item Interface between the visually impaired person and the assisted technology;
\item Appearance, usability and potential costs of the final product. 
\end{enumerate}
Design process involved testing of the existing technological solutions (mobile phone apps) for assisting visually impaired persons {\color{red}(which ones have we tested?)}. Semi-structured tests were performed by the visually impaired participants accompanied by a researcher from a project group. Strengths and weaknesses of the existing solutions are reflected in the design of the proposed system.

\section{Results}
\label{sec:results}

%\begin{wrapfigure}{r}{0.4\textwidth}
\begin{figure}
  \begin{center}
    \includegraphics[scale=0.7]{./img/cropped_diagram.pdf}  
  \end{center}
  \caption{Schematics of FRP device.}
  \label{fig:schematics}
\end{figure}
%\end{wrapfigure}

Following the above methodology we suggest the impaired human vision compensation system (\textbf{HVCS}), consisting of \textbf{Device} and \textbf{Inference} components (see Fig.~\ref{fig:schematics}).

%padalijimas i 2 komponentus man nelabai aiskus. As dalinciau i input (kameros, sensoriai), output (ausines, vibratoriu matricos), processing (local, remote). 
% tai kas dabar yra prie Inference, siulau perprazuot kaip Functionality, ka as minejau Method. Taip pat visa Results skyreli reiktu labiau susiet su Method. Reiktu, kad visi 4 Method pamineti punktai isrysketu ir Results. 
%Results skyrelyje nereiktu taip stipriai fokusuotis i kitu grupiu tyrimus ir juos cituoti. Rezultatai juk musu.
\textbf{Device} subsystem is a computational device the user currently uses for completing other daily tasks. It consists of sensors and actuators, integrated into smartphone-based computation core, which was chosen due its avialability to wide population, and capability to perform the required computations or forward visual information to the external server via Internet connection. Sensors are mounted on forehead belt include: RGB camera, depth camera, IMU. Actuator set consists of bone conductive headphones, and head belt for presenting tactile-feedback to the user. %We suggest to use bone conductive headphones, ...

\textbf{Inference} subsystem consists of server computer with internet connection and set of computer vision algorithms, selected according to our methodology (see. Sec.~\ref{sec:method}): Faster RCNN object detector \cite{?}, trained to detect important objects (doors, floors, elevators, stairs, corridor junctions, etc.), CNN-RNN-based scene description \cite{Liu},\cite{Ren}, \cite{Dai}, place recognition \cite{Ohn-Bar}, face recognition \cite{Amos}, obstacle detection \cite{Laina}, and possibly other modules.

HVCS operation cycle is started by \textbf{Device} reading sensor data and transmitting it to the server for an analysis. Server calculates feedback signal and transmits it back to the device for presenting to the user.

\section{Discussion}
\label{sec:discussion}
%Didzioji Discussion teksto dalis man labiau tinka prie Results/Conclusion. Gal galim padiskutioti daugiau apie Limitations, Future Implications, Lessons Learned ar pan... Cia galime savo siuloma sistema lyginti su anksciau publikuotais rezultatais.

In this article we outlined an idea of complex computer vision-based sensor architecture, which can help to partially compensate impaired or lost human sight. Main improvements comparing to similar previous work (\cite{?}, \cite{?}) is: ability to use efficient (but still computationally intensive) modern computer vision algorithms via Internet connection, present the signal to the user by combined bone conductive headphone-tactile actuator, low cost and consequently increased potential availability of the device. Suggested architecture can be used as basis for various computer vision-based systems, allowing to help visually impaired users in everyday routines (e.g. outdoor/indoor navigation,...). On the other side, due to remotelly carried visual analysis, in some cases the suggested system may suffer from too large latency, its reliability depends on stability and quality of Internet connection. Such a problem partially may be solved in near future, when 5G networks will prevail.

%The developed head-mounted tactile device is developed for head position and orientation tracking and could capture an image in front of visually impaired people. The tactile device with integrated 3D deph camera is integrated with smartphone by bluetooth which could preprocess the labeled image features. The developed high quality self navigation system is based on the computer vision methods especially enhancing the capabilities to detect and classify objects (e.g bus station, street crossings, ) with their surrounding objects. The authors expect to increase the capabilies of potentially blind to secure navigate especially for the planed destination (e.g. "home-office"). Work left (outdoor/indoor) etc.

% conference papers do not normally have an appendix

% use section* for acknowledgement
%\section*{Acknowledgment}
%The authors would like to thank...

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
%
% As suggested below, edit bibtemplate_samples.bib to reflect
% your bibliography. See bibtemplate.text for referencing.
%

\bibliographystyle{IEEEtran}
%\bibliography{bibtemplate_samples}

\begin{thebibliography}{1}
\bibitem{Amos} Amos, B., Ludwiczuk, B., and Satyanarayanan, M. Openface:
A general-purpose face recognition library with mobile applications. Technical report, CMU-CS-16-118, CMU School of Computer Science, 2016.

\bibitem{Bourne} Bourne RRA, Flaxman SR, Braithwaite T, Cicinelli MV, Das A, Jonas JB, et al.; Vision Loss Expert Group. Magnitude, temporal trends, and projections of the global prevalence of blindness and distance and near vision impairment: a systematic review and meta-analysis. Lancet Glob Health.  2017 Sep;5(9):e888-97.

\bibitem{Caraiman} Caraiman, S., Morar, A., Owczarek, M.,Burlacu, A., Rzeszotarski, D., Botezatu, N., Herghelegiu, P., Moldoveanu, F., Strumillo, P., Moldoveanu, A. Computer Vision for the Visually Impaired: the Sound of Vision System. IEEE International Conference on Computer Vision Workshops, pp. 1480-1489, 2017.
\bibitem{Csapo} Csap\'{o}, A., Wers\'{e}nyi, G., Nagy, H., Stockman, T. A survey of assistive technologies and applications for blind users on mobile platforms: a review and foundation for research. Journal on Multimodal User Interfaces. Vol. 9, issule 4,  pp. 275-286, 2015.
\bibitem{Dai} Dai, J., Li, Y., He, K., Sun J. R-FCN: Object Detection via Region-based Fully Convolutional Networks. In Advances in neural information processing systems, pp. 379-387, 2016.
\bibitem{Poggi} Poggi, M., Mattoccia, S. A wearable mobility aid for the visually impaired based on embedded 3d vision and deep learning. Proceeding of IEEE Symposium on Compututers and Communication, pp. 208-213, 2016.
\bibitem{Zientara} Zientara, P.,A., Lee, S., Smith, G., H., Brenner, R., Itti, L., Rosson M., B., Carroll, J., M., Irick K., M., Narayanan, V. Third Eye: A shopping assistant for the visually impaired. Computer Vol. 50, Issue 2, pp. 16-24, 2017.
\bibitem{Liu} Liu, Ch., Mao, J., Sha, F., Yuille, A. Attention Correctness in Neural Image Captioning. Proceedings of the Thirty-First AAAI Conference on Artificial Intelligence, pp. 4176-4182, 2017.
\bibitem{Laina} Laina, I., Rupprecht, C., Belagiannis, V., Tombari, F., Navab, N. Deeper depth prediction with fully convolutional residual networks. Fourth International Conference on 3D Vision (3DV), pp. 239-248, 2016.
\bibitem{Ohn-Bar}  Ohn-Bar, E., Kitani, K., Asakawa, Ch. Personalized Dynamics Models for Adaptive Assistive Navigation Interfaces. arXiv:1804.04118, [cs.LG], 2018.
\bibitem{Ren} Ren, Sh., He, K., Girshick, R., and Sun, J.  Faster R-CNN: Towards real-time object detection with region proposal networks. In Advances in neural information processing systems, pp. 91-99, 2015.

\bibitem{Kensing} Kensing, F., Simonsen, J., and B\o dker, K. MUST: A Method for Participatory Design. Hum-Comput Interact, vol. 13, no. 2, pp. 167-198, Jun. 1998.

\bibitem{Carroll} Carroll, J. M., Rosson, M. B. Participatory design in community informatics. Des. Stud., vol. 28, no. 3, pp. 243-261, May 2007.

\bibitem{Owayjan} Owayjan, M., Hayek, A., Nassrallah, H., Eldor, M. Smart Assistive Navigation System for Blind and Visually Impaired Individuals. 2015 International Conference on Advances in Biomedical Engineering (ICABME), 2015.

\bibitem{Larisa} Dunai, L. D., Lengua, I. L., Tortajada, I., Brusola Simon, F. Obstacle detectors for visually impaired people. 2014 International Conference on Optimization of Electrical and Electronic Equipment (OPTIM), 2014.

\end{thebibliography}

% that's all folks
\end{document}

### 2018-09-26 bare_conf.tex
minor text updates

@@
 \and
-\IEEEauthorblockN{~\\[-0.4ex]\large James Kirk\\ and Montgomery Scott\\[0.3ex]\normalsize}
-\IEEEauthorblockA{Starfleet Academy\\
-San Francisco, California 96678-2391\\
-Telephone: (800) 555--1212\\
-Fax: (888) 555--1212}}
+\IEEEauthorblockN{~\\[-0.4ex]\large Andrius Budrionis\\[0.3ex]\normalsize}
+\IEEEauthorblockA{Vilnius Gediminas Technical University\\
+Vilnius, Lithuania\\
+Norwegian Centre for E-health Research\\
+University Hospital of North Norway\\
+Tromsø, Norway}}
 
@@
 \begin{IEEEkeywords}
-Anything; Something; Everything else.%
+Computer vision; Mobile application; Travel aid; Tactile. %
 \end{IEEEkeywords}
@@
 Many of the previuosly proposed electronic aids for the blind count on highly specialised hardware, for instance smart glassess \cite{Zientara}, Microsoft Kinnect sensors \cite{Owayjan}, helmet-mounted photosensors and cameras \cite{Larisa}.
-Such advanced and costly technology brings additional complexity into daily tasks, which visually impaired people currently manage by the help of the white cane.
+Such advanced and costly technology brings additional complexity into daily tasks, which visually impaired people currently manage by the help of a white cane.
 This project puts major emphasis on developing a tool, which seamlesly integrates with the hardware visually impaired person already has on-hand and is used to (smartphone).
-This paper describes the high level architecture of the proposed technology aid for visually impaired people.
+This paper describes a high level architecture of the proposed technology aid for visually impaired people.
 
@@
 \end{enumerate}
-Design process involved testing of the existing technological solutions (mobile phone apps) for assisting visually impaired persons {\color{red}(which ones have we tested?)}.
+Design process involved testing of the existing tmobile phone app (Seeing AI) for assisting visually impaired persons.
 Semi-structured tests were performed by the visually impaired participants accompanied by a researcher from a project group.
@@
 %padalijimas i 2 komponentus man nelabai aiskus. As dalinciau i input (kameros, sensoriai), output (ausines, vibratoriu matricos), processing (local, remote). 
-% tai kas dabar yra prie Inference, siulau perprazuot kaip Functionality, ka as minejau Method.
+% tai kas dabar yra prie Inference, siulau perfrazuot kaip Functionality, ka as minejau Method.
 Taip pat visa Results skyreli reiktu labiau susiet su Method.
@@
 \textbf{Device} subsystem is a computational device the user currently uses for completing other daily tasks.
-It consists of sensors and actuators, integrated into smartphone-based computation core, which was chosen due its avialability to wide population, and capability to perform the required computations or forward visual information to the external server via Internet connection.
+It consists of sensors and actuators, integrated into smartphone-based computational core, which was chosen due its avialability to wide population, and capability to perform the required computations or forward visual information to the external server via the Internet connection.
 Sensors are mounted on forehead belt include: RGB camera, depth camera, IMU.

### 2018-09-28 article.tex
IEEE style added.
article.tex
Results section is updated
Discussion  section is updated

@@
 \section{Introduction}
+\label{sec:introduction}
 
@@
 
+The key functionality of smart device enables to label the road 'home-office' on the real map that helps  visually impaired community expand the knowledge about the assitive roads for safe navigation.
+The composed solution of labeled object  location and direction detection assisted by smartphone device enables to trust the new developed technology for visually impaired people.
+
+Technical feasibility
+After the survey of visually impaired people needs the authors came to conclusion from 5 to 8 object class should be detected the position and orientation and the key feasibility of device should help to learn the "home-office" road in most efficient way.
+The recent developments of computing vision algorithms show the more promising results integrating the smartphone devices for image capturing and preprocessing.
+The computational resources are allocated to perform
+%Interface
+Light weighted and head mounted tactile device receives the information from server about the object location, including distance and direction to it.
+The bone headphone device will be used for assistive information provided through internet server...
+
 Following the above methodology we suggest the impaired human vision compensation system (\textbf{HVCS}), consisting of \textbf{Device} and \textbf{Inference} components (see Fig.~\ref{fig:schematics}).
@@
 Actuator set consists of bone conductive headphones, and head belt for presenting tactile-feedback to the user.
+The smartphone device would be integrated with sensors due to capture the street image.
+The low resources computational device preprocess the image and sends to server to detect the object.
 %We suggest to use bone conductive headphones, ...
@@
 
+What are main advantages in our proposed solution? What is the reason there is no proposed solution at all?
+What exact technical solution should be implemented/developed?
+What feasibility and key features are most important for visually impaired people?
 \begin{thebibliography}{1}

### 2018-09-30 bare_conf.tex
text changes, Results section is rewritten

@@
 
-More than $250$ million poople worldwide have moderate to severe vision impairment, while ($\approx 36$ million are blind) \cite{Bourne}.
+More than $250$ million people worldwide have moderate to severe vision impairment, while ($\approx 36$ million are blind) \cite{Bourne}.
 During the past decades significant effort was devoted to develop computer vision and other sensor based aids (e.g.
@@
 In this article we describe a system, which employs modern computer vision techniques for compensation of lost or impaired vision function in humans.
-Many of the previuosly proposed electronic aids for the blind count on highly specialised hardware, for instance smart glassess \cite{Zientara}, Microsoft Kinnect sensors \cite{Owayjan}, helmet-mounted photosensors and cameras \cite{Larisa}.
+Many of the previously proposed electronic aids for the blind count on highly specialized hardware, for instance smart glasses \cite{Zientara}, Microsoft Kinnect sensors \cite{Owayjan}, helmet-mounted photo sensors and cameras \cite{Larisa}.
 Such advanced and costly technology brings additional complexity into daily tasks, which visually impaired people currently manage by the help of a white cane.
-This project puts major emphasis on developing a tool, which seamlesly integrates with the hardware visually impaired person already has on-hand and is used to (smartphone).
+This project puts major emphasis on developing a tool, which seamlessly integrates with the hardware visually impaired person already has on-hand and is used to (smartphone).
 This paper describes a high level architecture of the proposed technology aid for visually impaired people.
@@
 \end{enumerate}
-Design process involved testing of the existing tmobile phone app (Seeing AI) for assisting visually impaired persons.
+Design process involved testing of the existing mobile phone app (Seeing AI) for assisting visually impaired persons.
 Semi-structured tests were performed by the visually impaired participants accompanied by a researcher from a project group.
@@
 \label{sec:results}
+
+User-centered design sessions with visually impaired persons provided substantial input for the design of the proposed system (Fig.~\ref{fig:schematics}).
+The process made it clear that understanding of the user needs was limited in the project group.
+Based on the results of the user-centered design process, we present the outline of the system for impaired human vision compensation.
+
+The key part of the proposed system is a smartphone device, connecting user interface and data processing components into a well-functioning ecosystem.
+Smartphone was selected due to its high availability and capability to perform required computations or forward visual information to the external server via the Internet connection.
+The cornerstone of the proposed solution is a wearable forehead belt, integrating two cameras and a tactile feedback device.
+Bone conductive headphones are suggested to facilitate audio feedback.
 
@@
 \end{figure}
+
 %\end{wrapfigure}
 
-Following the above methodology we suggest the impaired human vision compensation system (\textbf{HVCS}), consisting of \textbf{Device} and \textbf{Inference} components (see Fig.~\ref{fig:schematics}).
+%Following the above methodology we suggest the impaired human vision compensation system (\textbf{HVCS}), consisting of \textbf{Device} and \textbf{Inference} components (see Fig.~\ref{fig:schematics}).
 
@@
 %Results skyrelyje nereiktu taip stipriai fokusuotis i kitu grupiu tyrimus ir juos cituoti. Rezultatai juk musu.
-\textbf{Device} subsystem is a computational device the user currently uses for completing other daily tasks.
+
+Discussions on functionality and key features of the solution revealed a gap between the aims of the existing tools, which are often focused on advanced navigation and scene description features, and actual user needs.
+The end users highlighted that a simplistic solution for navigating is lacking.
+They were not excited about advanced object detection and scene description techniques, which may overcomplicate their daily life.
+Major focus was put on a easy to use and minimalistic tool, which can be trusted.
+Direction and approximate distance to obstacle were highlighted as major requirements.
+To our surprise, only 5-8 distinctive object classes (for instance, buss stop, pedestrian crossing, doors, stairs, etc) were of major importance while navigating.
+Additional information, such as type of a passing car, blossoming flowers in the park or person passing riding a bicycle was considered as overwhelming and distractive.
+
+Social networking functionality was accepted as a potentially important feature allowing other users/volunteers to describe certain objects (for instance, temporary road works) with exact location and description.
+Navigating around such obstacles can be challenging for computer vision-based tools and may decrease user's trust in the tool.
+Integration of additional information from other users, governmental organizations and volunteers could be of high value for the visually impaired people.
+
+%Povilai, paziurek ar cia viskas OK, pridek ka nors nuo saves
+Computer vision technology is under rapid development and during last years made major breakthrough in performance and efficiency.
+Deep learning neural networks, which are de facto standard in modern image/video processing, are now well supported by software libraries and dedicated hardware built-in even in relatively low-power computational devices, such as smartphones.
+These devices are equipped with high-quality cameras, 4G Internet connectivity and sufficient computational power to perform initial data processing locally.
+The maturity of the aforementioned technologies suggest that our proposed computational aid for visually impaired persons may be highly feasible.
+
+The cornerstone of this project is the interface between the visually impaired person and the assistive technology.
+We are proposing a combination of audio and tactile feedback, which may improve the interaction between the assitive technology and the user.
+Similar interfaces were suggested by research communities earlier \cite{Zientara}, \cite{Poggi}, however, current knowledge on user preferences and evaluation of various options of tactile feedback (placement on the body, frequencies, strength, etc.) is limited.
+
+Appearance, usability and cost of the final solution is of major importance to the users.
+The proposed assistive technology should replace/supplement the tool that visually impaired persons used for decades - the white cane.
+Using a white cane requires little to none training, has very low costs and is relatively reliable.
+It provides information on the surrounding objects 1-2 meters in front of the user.
+While the cane can used to detect a nearby obstacle, electronic travel aid could be beneficial for longer range (10-20m) route planning and object recognition.
+However, it should integrate seamlessly into the existing navigation practices of visually impaired people.
+
+%The proposed system  consists of three major parts: is a computational device the user currently uses for completing other daily tasks.
 It consists of sensors and actuators, integrated into smartphone-based computational core, which was chosen due its avialability to wide population, and capability to perform the required computations or forward visual information to the external server via the Internet connection.
@@
 
-\textbf{Inference} subsystem consists of server computer with internet connection and set of computer vision algorithms, selected according to our methodology (see.
+%\textbf{Inference} subsystem consists of server computer with internet connection and set of computer vision algorithms, selected according to our methodology (see.
 Sec.~\ref{sec:method}): Faster RCNN object detector \cite{?}, trained to detect important objects (doors, floors, elevators, stairs, corridor junctions, etc.), CNN-RNN-based scene description \cite{Liu},\cite{Ren}, \cite{Dai}, place recognition \cite{Ohn-Bar}, face recognition \cite{Amos}, obstacle detection \cite{Laina}, and possibly other modules.
 
-HVCS operation cycle is started by \textbf{Device} reading sensor data and transmitting it to the server for an analysis.
+%HVCS operation cycle is started by \textbf{Device} reading sensor data and transmitting it to the server for an analysis.
 Server calculates feedback signal and transmits it back to the device for presenting to the user.
@@
 
+\bibitem{Poggi} Poggi, M., Mattoccia, S.
+A wearable mobility aid for the visually impaired based on embedded 3D vision and deep learning.
+2016 IEEE Symposium on Computers and Communication (ISCC), 2016
+
 \end{thebibliography}

### 2018-10-04 bare_conf.tex
some modifications of text.

@@
 % affiliations
-\author{\IEEEauthorblockN{~\\[-0.4ex]\large Michael Shell\\[0.3ex]\normalsize}
-\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
-Georgia Institute of Technology\\
-Atlanta, Georgia 30332--0250\\
-Email: {\tt ...}}
+\author{\IEEEauthorblockN{~\\[-0.4ex]\large Povilas Daniu\v{s}is\\[0.3ex]\normalsize}
+\IEEEauthorblockA{Vilnius Gediminas Technical University\\
+Vilnius, Lithuania}
 \and
-\IEEEauthorblockN{~\\[-0.4ex]\large Homer Simpson\\[0.3ex]\normalsize}
-\IEEEauthorblockA{Twentieth Century Fox\\
-Springfield, USA\\
-Email: {\tt homer@thesimpsons.com}}
+\IEEEauthorblockN{~\\[-0.4ex]\large Audrius Indriulionis\\[0.3ex]\normalsize}
+\IEEEauthorblockA{Vilnius Gediminas Technical University\\
+Vilnius, Lithuania}
 \and
@@
 %\boldmath
-The abstract goes here.
-The abstract goes here.
-The abstract goes here.
-The abstract goes here.
-The abstract goes here.
-The abstract goes here.
+In this short article we describe and discuss architecture of computer vision-based system for partial compensation of lost or impaired human vision.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Computer vision; Mobile application; Travel aid; Tactile. %
+Computer vision; Mobile application; Aid for blind and visually impaired; Tactile feedback; Impaired human vision compensation.%
 \end{IEEEkeywords}
@@
 The key part of the proposed system is a smartphone device, connecting user interface and data processing components into a well-functioning ecosystem.
-Smartphone was selected due to its high availability and capability to perform required computations or forward visual information to the external server via the Internet connection.
-The cornerstone of the proposed solution is a wearable forehead belt, integrating two cameras and a tactile feedback device.
-Bone conductive headphones are suggested to facilitate audio feedback.
+Smartphone was selected due to its high availability and capability to perform required computations or forward visual information for processing to the external server via the Internet connection.
+
+The cornerstones of the proposed solution are its inferface and external server, capable running computationally demanding vision processing algorithms.
+
+The interface consists of a wearable forehead belt, integrating RGB and depth cameras, tactile feedback device and bone conductive headphones.
+Altough more expensive than standard ones, bone conductive headphones allow the user to perceive audio information from the surrounding environment, which is essential for the visually impaired people.
+
+External server processes received visual data according to user request with computer vision algorithms: faster RCNN object detector \cite{Ren}, trained to detect important objects, CNN-RNN-based scene description \cite{Liu}, place recognition \cite{Ohn-Bar}, face recognition \cite{Amos}, obstacle detection \cite{Laina}, and other algorithms, and transmits feedback signal back to the smartphone device for presenting to the user via the above described interface.
 
@@
   \end{center}
-  \caption{Schematics of FRP device.}
+  \caption{Schematics of vision compensation device.}
   \label{fig:schematics}
@@
 The end users highlighted that a simplistic solution for navigating is lacking.
-They were not excited about advanced object detection and scene description techniques, which may overcomplicate their daily life.
+%They were not excited about advanced object detection and scene description techniques, which may overcomplicate their daily life. 
 Major focus was put on a easy to use and minimalistic tool, which can be trusted.
-Direction and approximate distance to obstacle were highlighted as major requirements.
+Object detection, and direction and approximate distance to obstacle were highlighted as major requirements.
 To our surprise, only 5-8 distinctive object classes (for instance, buss stop, pedestrian crossing, doors, stairs, etc) were of major importance while navigating.
 Additional information, such as type of a passing car, blossoming flowers in the park or person passing riding a bicycle was considered as overwhelming and distractive.
+Another important functionality required by end users was navigation aid.
 
-Social networking functionality was accepted as a potentially important feature allowing other users/volunteers to describe certain objects (for instance, temporary road works) with exact location and description.
+%Social networking functionality was accepted as a potentially important feature allowing other users/volunteers to describe certain objects (for instance, temporary road works) with exact location and description.
 Navigating around such obstacles can be challenging for computer vision-based tools and may decrease user's trust in the tool.
@@
 Deep learning neural networks, which are de facto standard in modern image/video processing, are now well supported by software libraries and dedicated hardware built-in even in relatively low-power computational devices, such as smartphones.
-These devices are equipped with high-quality cameras, 4G Internet connectivity and sufficient computational power to perform initial data processing locally.
+These devices are also equipped with 4G Internet connectivity and sufficient computational power to perform initial data processing locally.
 The maturity of the aforementioned technologies suggest that our proposed computational aid for visually impaired persons may be highly feasible.
@@
 Appearance, usability and cost of the final solution is of major importance to the users.
-The proposed assistive technology should replace/supplement the tool that visually impaired persons used for decades - the white cane.
+The proposed assistive technology should supplement the tool that visually impaired persons used for decades - the white cane.
 Using a white cane requires little to none training, has very low costs and is relatively reliable.
@@
 
-%\textbf{Inference} subsystem consists of server computer with internet connection and set of computer vision algorithms, selected according to our methodology (see.
-Sec.~\ref{sec:method}): Faster RCNN object detector \cite{?}, trained to detect important objects (doors, floors, elevators, stairs, corridor junctions, etc.), CNN-RNN-based scene description \cite{Liu},\cite{Ren}, \cite{Dai}, place recognition \cite{Ohn-Bar}, face recognition \cite{Amos}, obstacle detection \cite{Laina}, and possibly other modules.
+%\textbf{Inference} subsystem consists of server computer with internet connection and set of computer vision algorithms, selected according to our methodology ed (see.
+Sec.~\ref{sec:method}): Faster RCNN object detector \cite{?}, trainto detect important objects (doors, floors, elevators, stairs, corridor junctions, etc.), CNN-RNN-based scene description \cite{Liu},\cite{Ren}, \cite{Dai}, place recognition \cite{Ohn-Bar}, face recognition \cite{Amos}, obstacle detection \cite{Laina}, and possibly other modules.
 
@@
 In this article we outlined an idea of complex computer vision-based sensor architecture, which can help to partially compensate impaired or lost human sight.
-Main improvements comparing to similar previous work (\cite{?}, \cite{?}) is: ability to use efficient (but still computationally intensive) modern computer vision algorithms via Internet connection, present the signal to the user by combined bone conductive headphone-tactile actuator, low cost and consequently increased potential availability of the device.
-Suggested architecture can be used as basis for various computer vision-based systems, allowing to help visually impaired users in everyday routines (e.g.
-outdoor/indoor navigation,...).
+Main improvements comparing to similar previous work (\cite{?}, \cite{?}) are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via Internet connection, present the signal to the user by combined bone conductive headphone-tactile actuator, low cost and consequently increased potential availability of the device.
+The suggested system integrates well with the main blind person's aid - the white cane.
+The hardware architecture can be used as the basis for various computer vision-based software modules, allowing to help visually impaired users in everyday routines (e.g.
+outdoor/indoor navigation, object/face recognition, obstacle detection, navigation).
 On the other side, due to remotelly carried visual analysis, in some cases the suggested system may suffer from too large latency, its reliability depends on stability and quality of Internet connection.
-Such a problem partially may be solved in near future, when 5G networks will prevail.
+
+%Such a problem partially may be solved in near future, when 5G networks will prevail.
 
@@
 275-286, 2015.
-\bibitem{Dai} Dai, J., Li, Y., He, K., Sun J. R-FCN: Object Detection via Region-based Fully Convolutional Networks. In Advances in neural information processing systems, pp. 379-387, 2016.
+%\bibitem{Dai} Dai, J., Li, Y., He, K., Sun J. R-FCN: Object Detection via Region-based Fully Convolutional Networks. In Advances in neural information processing systems, pp. 379-387, 2016.
 \bibitem{Poggi} Poggi, M., Mattoccia, S.

### 2018-10-04 bare_conf.tex
small fixes in Discussion.

@@
 In this article we outlined an idea of complex computer vision-based sensor architecture, which can help to partially compensate impaired or lost human sight.
-Main improvements comparing to similar previous work (\cite{?}, \cite{?}) are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via Internet connection, present the signal to the user by combined bone conductive headphone-tactile actuator, low cost and consequently increased potential availability of the device.
+Main advantages of therein suggested system are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via Internet connection, present the signal to the user by combined bone conductive headphone-tactile actuator, low cost and consequently increased potential availability of the device.
 The suggested system integrates well with the main blind person's aid - the white cane.

### 2018-10-04 bare_conf.tex
removed bibliography duplicate \cite{Poggi}.
some text modification.

@@
 
-The cornerstones of the proposed solution are its inferface and external server, capable running computationally demanding vision processing algorithms.
+The cornerstones of the proposed solution are its inferface and external server, capable running computationally demanding modern image processing algorithms.
 
@@
 
-External server processes received visual data according to user request with computer vision algorithms: faster RCNN object detector \cite{Ren}, trained to detect important objects, CNN-RNN-based scene description \cite{Liu}, place recognition \cite{Ohn-Bar}, face recognition \cite{Amos}, obstacle detection \cite{Laina}, and other algorithms, and transmits feedback signal back to the smartphone device for presenting to the user via the above described interface.
+External server processes received visual data according to user request with computer vision algorithms: faster RCNN object detector \cite{Ren}, trained to detect important objects, CNN-RNN-based scene description \cite{Liu}, place recognition \cite{Ohn-Bar}, face recognition \cite{Amos}, obstacle detection \cite{Laina}, among others.
+After completing an analysis this server transmits feedback signal back to the smartphone device for presenting it to the user via the above described interface.
 
@@
 Discussions on functionality and key features of the solution revealed a gap between the aims of the existing tools, which are often focused on advanced navigation and scene description features, and actual user needs.
-The end users highlighted that a simplistic solution for navigating is lacking.
+For example, the end users highlighted that a simplistic solution for navigating is lacking.
 %They were not excited about advanced object detection and scene description techniques, which may overcomplicate their daily life. 
 Major focus was put on a easy to use and minimalistic tool, which can be trusted.
-Object detection, and direction and approximate distance to obstacle were highlighted as major requirements.
+Reliable object detection, direction and approximate distance to an obstacle were highlighted as major requirements.
 To our surprise, only 5-8 distinctive object classes (for instance, buss stop, pedestrian crossing, doors, stairs, etc) were of major importance while navigating.
 Additional information, such as type of a passing car, blossoming flowers in the park or person passing riding a bicycle was considered as overwhelming and distractive.
-Another important functionality required by end users was navigation aid.
 
@@
 
-\bibitem{Poggi} Poggi, M., Mattoccia, S.
+%\bibitem{Poggi} Poggi, M., Mattoccia, S.
 A wearable mobility aid for the visually impaired based on embedded 3D vision and deep learning.

### 2018-10-04 bare_conf.tex
typo fixed.
bibliography fixed.

@@
 Many of the previously proposed electronic aids for the blind count on highly specialized hardware, for instance smart glasses \cite{Zientara}, Microsoft Kinnect sensors \cite{Owayjan}, helmet-mounted photo sensors and cameras \cite{Larisa}.
-Such advanced and costly technology brings additional complexity into daily tasks, which visually impaired people currently manage by the help of a white cane.
+Such systems often lack convenience and brings additional complexity into daily tasks, which visually impaired people currently manage by the help of a white cane.
 This project puts major emphasis on developing a tool, which seamlessly integrates with the hardware visually impaired person already has on-hand and is used to (smartphone).
-This paper describes a high level architecture of the proposed technology aid for visually impaired people.
+%This paper describes a high level architecture of the proposed technology aid for visually impaired people %(kartojasi su In this article we describe a system, which employs modern computer vision ...)
 
@@
 In this article we outlined an idea of complex computer vision-based sensor architecture, which can help to partially compensate impaired or lost human sight.
-Main advantages of therein suggested system are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via Internet connection, present the signal to the user by combined bone conductive headphone-tactile actuator, low cost and consequently increased potential availability of the device.
-The suggested system integrates well with the main blind person's aid - the white cane.
+Main advantages of therein suggested system are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via Internet connection, present the signal to the user by combined bone conductive headphone-tactile actuator, comparatively low cost and consequently increased potential availability of the device.
+The suggested system also integrates well with the main blind person's aid - the white cane.
 The hardware architecture can be used as the basis for various computer vision-based software modules, allowing to help visually impaired users in everyday routines (e.g.
-outdoor/indoor navigation, object/face recognition, obstacle detection, navigation).
+outdoor/indoor navigation, object/face recognition, obstacle detection, etc.).
 On the other side, due to remotelly carried visual analysis, in some cases the suggested system may suffer from too large latency, its reliability depends on stability and quality of Internet connection.
-
-%Such a problem partially may be solved in near future, when 5G networks will prevail.
 
@@
 1480-1489, 2017.
+
+\bibitem{Carroll} Carroll, J. M., Rosson, M. B. Participatory design in community informatics. Des. Stud., vol. 28, no. 3, pp. 243-261, May 2007.
+
 \bibitem{Csapo} Csap\'{o}, A., Wers\'{e}nyi, G., Nagy, H., Stockman, T.
@@
 275-286, 2015.
-%\bibitem{Dai} Dai, J., Li, Y., He, K., Sun J. R-FCN: Object Detection via Region-based Fully Convolutional Networks. In Advances in neural information processing systems, pp. 379-387, 2016.
-\bibitem{Poggi} Poggi, M., Mattoccia, S.
-A wearable mobility aid for the visually impaired based on embedded 3d vision and deep learning.
-Proceeding of IEEE Symposium on Compututers and Communication, pp.
-208-213, 2016.
-\bibitem{Zientara} Zientara, P.,A., Lee, S., Smith, G., H., Brenner, R., Itti, L., Rosson M., B., Carroll, J., M., Irick K., M., Narayanan, V.
-Third Eye: A shopping assistant for the visually impaired.
-Computer Vol.
-50, Issue 2, pp.
-16-24, 2017.
-\bibitem{Liu} Liu, Ch., Mao, J., Sha, F., Yuille, A. Attention Correctness in Neural Image Captioning. Proceedings of the Thirty-First AAAI Conference on Artificial Intelligence, pp. 4176-4182, 2017.
-\bibitem{Laina} Laina, I., Rupprecht, C., Belagiannis, V., Tombari, F., Navab, N.
-Deeper depth prediction with fully convolutional residual networks.
-Fourth International Conference on 3D Vision (3DV), pp.
-239-248, 2016.
-\bibitem{Ohn-Bar}  Ohn-Bar, E., Kitani, K., Asakawa, Ch. Personalized Dynamics Models for Adaptive Assistive Navigation Interfaces. arXiv:1804.04118, [cs.LG], 2018.
-\bibitem{Ren} Ren, Sh., He, K., Girshick, R., and Sun, J.
-Faster R-CNN: Towards real-time object detection with region proposal networks.
-In Advances in neural information processing systems, pp.
-91-99, 2015.
-
-\bibitem{Kensing} Kensing, F., Simonsen, J., and B\o dker, K. MUST: A Method for Participatory Design. Hum-Comput Interact, vol. 13, no. 2, pp. 167-198, Jun. 1998.
-
-\bibitem{Carroll} Carroll, J. M., Rosson, M. B. Participatory design in community informatics. Des. Stud., vol. 28, no. 3, pp. 243-261, May 2007.
-
-\bibitem{Owayjan} Owayjan, M., Hayek, A., Nassrallah, H., Eldor, M.
-Smart Assistive Navigation System for Blind and Visually Impaired Individuals.
-2015 International Conference on Advances in Biomedical Engineering (ICABME), 2015.
 
@@
 2014 International Conference on Optimization of Electrical and Electronic Equipment (OPTIM), 2014.
+
+\bibitem{Kensing} Kensing, F., Simonsen, J., and B\o dker, K. MUST: A Method for Participatory Design. Hum-Comput Interact, vol. 13, no. 2, pp. 167-198, Jun. 1998.
+
+\bibitem{Laina} Laina, I., Rupprecht, C., Belagiannis, V., Tombari, F., Navab, N.
+Deeper depth prediction with fully convolutional residual networks.
+Fourth International Conference on 3D Vision (3DV), pp.
+239-248, 2016.
+
+\bibitem{Liu} Liu, Ch., Mao, J., Sha, F., Yuille, A. Attention Correctness in Neural Image Captioning. Proceedings of the Thirty-First AAAI Conference on Artificial Intelligence, pp. 4176-4182, 2017.
+
+\bibitem{Ohn-Bar}  Ohn-Bar, E., Kitani, K., Asakawa, Ch. Personalized Dynamics Models for Adaptive Assistive Navigation Interfaces. arXiv:1804.04118, [cs.LG], 2018.
+
+\bibitem{Owayjan} Owayjan, M., Hayek, A., Nassrallah, H., Eldor, M.
+Smart Assistive Navigation System for Blind and Visually Impaired Individuals.
+2015 International Conference on Advances in Biomedical Engineering (ICABME), 2015.
+
+\bibitem{Poggi} Poggi, M., Mattoccia, S.
+A wearable mobility aid for the visually impaired based on embedded 3d vision and deep learning.
+Proceeding of IEEE Symposium on Compututers and Communication, pp.
+208-213, 2016.
+
+\bibitem{Ren} Ren, Sh., He, K., Girshick, R., and Sun, J.
+Faster R-CNN: Towards real-time object detection with region proposal networks.
+In Advances in neural information processing systems, pp.
+91-99, 2015.
+
+\bibitem{Zientara} Zientara, P.,A., Lee, S., Smith, G., H., Brenner, R., Itti, L., Rosson M., B., Carroll, J., M., Irick K., M., Narayanan, V.
+Third Eye: A shopping assistant for the visually impaired.
+Computer Vol.
+50, Issue 2, pp.
+16-24, 2017.
 

### 2018-10-04 bare_conf.tex
small changes.

@@
 In this article we describe a system, which employs modern computer vision techniques for compensation of lost or impaired vision function in humans.
-Many of the previously proposed electronic aids for the blind count on highly specialized hardware, for instance smart glasses \cite{Zientara}, Microsoft Kinnect sensors \cite{Owayjan}, helmet-mounted photo sensors and cameras \cite{Larisa}.
+Many of the previously proposed electronic aids for the blind count on highly specialized hardware, for instance smart glasses \cite{Zientara}, Microsoft Kinnect sensors \cite{Owayjan}, helmet-mounted photo sensors and cameras \cite{Dunai}.
 Such systems often lack convenience and brings additional complexity into daily tasks, which visually impaired people currently manage by the help of a white cane.
@@
 outdoor/indoor navigation, object/face recognition, obstacle detection, etc.).
-On the other side, due to remotelly carried visual analysis, in some cases the suggested system may suffer from too large latency, its reliability depends on stability and quality of Internet connection.
+On the other side, due to remotelly conducted visual analysis, in some cases the suggested system may suffer from too large latency, its reliability depends on stability and quality of Internet connection.
 
@@
 
-\bibitem{Larisa} Dunai, L.
+\bibitem{Dunai} Dunai, L.
 D., Lengua, I.

### 2018-10-04 bare_conf.tex
some typos fixed, more text added.

@@
 The interface consists of a wearable forehead belt, integrating RGB and depth cameras, tactile feedback device and bone conductive headphones.
-Altough more expensive than standard ones, bone conductive headphones allow the user to perceive audio information from the surrounding environment, which is essential for the visually impaired people.
+Although more expensive than standard ones, bone conductive headphones allow the user to perceive audio information from the surrounding environment, which is essential for the visually impaired people.
 
@@
 The cornerstone of this project is the interface between the visually impaired person and the assistive technology.
-We are proposing a combination of audio and tactile feedback, which may improve the interaction between the assitive technology and the user.
+We are proposing a combination of audio and tactile feedback, which may improve the interaction between the assistive technology and the user.
 Similar interfaces were suggested by research communities earlier \cite{Zientara}, \cite{Poggi}, however, current knowledge on user preferences and evaluation of various options of tactile feedback (placement on the body, frequencies, strength, etc.) is limited.
@@
 Main advantages of therein suggested system are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via Internet connection, present the signal to the user by combined bone conductive headphone-tactile actuator, comparatively low cost and consequently increased potential availability of the device.
-The suggested system also integrates well with the main blind person's aid - the white cane.
+The suggested system also supplements the main blind person's aid - the white cane.
 The hardware architecture can be used as the basis for various computer vision-based software modules, allowing to help visually impaired users in everyday routines (e.g.
@@
 On the other side, due to remotelly conducted visual analysis, in some cases the suggested system may suffer from too large latency, its reliability depends on stability and quality of Internet connection.
+We are currently  implementing suggested the architecture into working prototype for preliminary evaluation by potential end users.
 

### 2018-10-07 bare_conf.tex
some typos, several paragraphs in Results and Discussion were rewritten

@@
 During the past decades significant effort was devoted to develop computer vision and other sensor based aids (e.g.
-\cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara}) for helping the blind and visually impaired users to perceive the surrounding world.
-However, computer vision is rapidly evolving field, and systems based on the aforementioned approaches often lack accuracy and reliability in real-world conditions.
+\cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara}) for helping the blind and visually impaired users to better perceive the surrounding world.
+However, computer vision is a rapidly evolving field; systems based on the aforementioned approaches become outdated in a relitively short time and often lack accuracy and reliability in real-world conditions in comparisson to the state-of-the-art technologies.
 In this article we describe a system, which employs modern computer vision techniques for compensation of lost or impaired vision function in humans.
 Many of the previously proposed electronic aids for the blind count on highly specialized hardware, for instance smart glasses \cite{Zientara}, Microsoft Kinnect sensors \cite{Owayjan}, helmet-mounted photo sensors and cameras \cite{Dunai}.
-Such systems often lack convenience and brings additional complexity into daily tasks, which visually impaired people currently manage by the help of a white cane.
-This project puts major emphasis on developing a tool, which seamlessly integrates with the hardware visually impaired person already has on-hand and is used to (smartphone).
-%This paper describes a high level architecture of the proposed technology aid for visually impaired people %(kartojasi su In this article we describe a system, which employs modern computer vision ...)
+Such systems often lack convenience and bring additional complexity into daily tasks, which visually impaired people currently manage by the help of a white cane.
+This project puts major emphasis on developing a tool, which seamlessly integrates with the hardware visually impaired persons already have on-hand and is used to (smartphone).
+This paper describes a high level architecture of the technology aid for visually impaired people utilising the latest achievemets in the field of computer vision.
+%(kartojasi su In this article we describe a system, which employs modern computer vision ...)
+%Andrius: nieko tokio, jei sakinys kartojasi Abstract'e. Sitai pastraipai reikia concluding sentence. Aisku galima ji perfrazuot kaip nors kitaip.
 
@@
 
-Following the principles of participatory design \cite{Kensing}, \cite{Carroll} we included the final users into the design process of the system.
+Following the principles of the participatory design \cite{Kensing}, \cite{Carroll} we included the end-users into the design process of the system.
 Two visually impaired persons participated in discussion and focus group meetings together with the project team to identify the key properties of the solution.
@@
 User-centered design sessions with visually impaired persons provided substantial input for the design of the proposed system (Fig.~\ref{fig:schematics}).
-The process made it clear that understanding of the user needs was limited in the project group.
+The process made it clear that understanding of the user needs was limited in the project team.
 Based on the results of the user-centered design process, we present the outline of the system for impaired human vision compensation.
@@
 
-The cornerstones of the proposed solution are its inferface and external server, capable running computationally demanding modern image processing algorithms.
+%The cornerstones of the proposed solution are its inferface and external server, capable running computationally demanding modern image processing algorithms.
 
-The interface consists of a wearable forehead belt, integrating RGB and depth cameras, tactile feedback device and bone conductive headphones.
-Although more expensive than standard ones, bone conductive headphones allow the user to perceive audio information from the surrounding environment, which is essential for the visually impaired people.
+User interface consists of a wearable forehead belt, integrating RGB and depth cameras, tactile feedback device and bone conductive headphones.
+Although more expensive than standard ones, bone conductive headphones do not block the ears and allow the user to perceive audio information from the surrounding environment, which is essential for the visually impaired people.
 
-External server processes received visual data according to user request with computer vision algorithms: faster RCNN object detector \cite{Ren}, trained to detect important objects, CNN-RNN-based scene description \cite{Liu}, place recognition \cite{Ohn-Bar}, face recognition \cite{Amos}, obstacle detection \cite{Laina}, among others.
-After completing an analysis this server transmits feedback signal back to the smartphone device for presenting it to the user via the above described interface.
+%visus sutrumpinimus reikia pirma parasyt pilnai, pvz Neural Network (NN)
+External server processes visual data employing a set of computer vision algorithms: faster RCNN object detector \cite{Ren}, trained to detect important objects, CNN-RNN-based scene description \cite{Liu}, place recognition \cite{Ohn-Bar}, face recognition \cite{Amos}, obstacle detection \cite{Laina}, among others.
+After completing the analysis results are transmitted back to the smartphone and represented to the user through the aforementioned interface.
 
@@
 To our surprise, only 5-8 distinctive object classes (for instance, buss stop, pedestrian crossing, doors, stairs, etc) were of major importance while navigating.
-Additional information, such as type of a passing car, blossoming flowers in the park or person passing riding a bicycle was considered as overwhelming and distractive.
+Additional information, such as type of a passing car, blossoming flowers in the park or a person riding a bicycle was considered as overwhelming and distractive.
 
@@
 %Povilai, paziurek ar cia viskas OK, pridek ka nors nuo saves
-Computer vision technology is under rapid development and during last years made major breakthrough in performance and efficiency.
-Deep learning neural networks, which are de facto standard in modern image/video processing, are now well supported by software libraries and dedicated hardware built-in even in relatively low-power computational devices, such as smartphones.
+Computer vision technology is under rapid development and during the last years made a major breakthrough in performance and efficiency.
+Deep learning neural networks, which are de facto standard in modern image/video processing, are now well supported by software libraries and dedicated processing hardware is built-in even in relatively low-power computational devices, such as smartphones.
 These devices are also equipped with 4G Internet connectivity and sufficient computational power to perform initial data processing locally.
@@
 We are proposing a combination of audio and tactile feedback, which may improve the interaction between the assistive technology and the user.
-Similar interfaces were suggested by research communities earlier \cite{Zientara}, \cite{Poggi}, however, current knowledge on user preferences and evaluation of various options of tactile feedback (placement on the body, frequencies, strength, etc.) is limited.
+Similar interfaces were suggested by research communities earlier \cite{Zientara}, \cite{Poggi}, however, existing knowledge on user preferences and evaluation of various options of tactile feedback (placement on the body, frequencies, strength, etc.) is limited.
 
-Appearance, usability and cost of the final solution is of major importance to the users.
+Appearance, usability and cost of the end product are of major importance to the users.
 The proposed assistive technology should supplement the tool that visually impaired persons used for decades - the white cane.
@@
 It provides information on the surrounding objects 1-2 meters in front of the user.
-While the cane can used to detect a nearby obstacle, electronic travel aid could be beneficial for longer range (10-20m) route planning and object recognition.
+While the cane can used to detect a nearby obstacle, electronic travel aid could be beneficial for longer range (2-10m) route planning and object detection.
 However, it should integrate seamlessly into the existing navigation practices of visually impaired people.
@@
 
-In this article we outlined an idea of complex computer vision-based sensor architecture, which can help to partially compensate impaired or lost human sight.
-Main advantages of therein suggested system are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via Internet connection, present the signal to the user by combined bone conductive headphone-tactile actuator, comparatively low cost and consequently increased potential availability of the device.
-The suggested system also supplements the main blind person's aid - the white cane.
-The hardware architecture can be used as the basis for various computer vision-based software modules, allowing to help visually impaired users in everyday routines (e.g.
+In this article we outlined an idea of complex computer vision-based sensor architecture, which may help to partially compensate impaired or lost human sight.
+Main advantages of therein suggested system are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via the Internet connection, present the output of video processing to the user through a combined audio/tactile interface.
+%bone conductive headphone-tactile actuator, comparatively low cost and consequently increased potential availability of the device. 
+The suggested system does not aim to replace the main travelling aid of visually impaired people - the white cane.
+Instead, this computer vision tool aims to push the perception of the surounding environment boundary from 1-2 meters (achieved by using the white cane) to 2-10 meters.
+It may improve route planning and identification of objects of interest (for instance, doors, stairs, elevators, bus stopps, etc.).
+This functionality corresponds with the main requirement for electronic travelling aids identified by the end users - direction and distance estimation to a selected object.
+The proposed hardware architecture can be used as a basis for various computer vision-based software modules, aiming to assist visually impaired users in daily activities (e.g.
 outdoor/indoor navigation, object/face recognition, obstacle detection, etc.).
-On the other side, due to remotelly conducted visual analysis, in some cases the suggested system may suffer from too large latency, its reliability depends on stability and quality of Internet connection.
+
+The proposed architecture is based on several assumptions, which may be characterized as limitations of the system.
+Technical feasibility of the solution is dependent on the availability of high bandwidth Internet connection ensuring access to high-power data processing components.
+Insuficient bandwidth may result in latency, which may not be tolerated by the users.
+
+%Andrius: galima butu paminet limited knowledge on tactile interfaces for navigation purposes, placement, frequences, strenths, etc...
+
+Economical feasibility of the proposed solution may also be questioned.
+Advanced technology (high-end smartphone, depth camera, tactile feedback device, bone conductive headphones) is needed to ensure reliable functioning of the system.
+A combination of such components may be perceived as costly by the end users.
+More research is needed to demonstrate the benefits of the system in real-world scenarios.
+
+%On the other side, due to remotelly conducted visual analysis, in some cases the suggested system may suffer from too large latency, its reliability depends on stability and quality of Internet connection.
 We are currently  implementing suggested the architecture into working prototype for preliminary evaluation by potential end users.

### 2018-10-08 bare_conf.tex
conductive -> conduction :)

@@
 
-User interface consists of a wearable forehead belt, integrating RGB and depth cameras, tactile feedback device and bone conductive headphones.
-Although more expensive than standard ones, bone conductive headphones do not block the ears and allow the user to perceive audio information from the surrounding environment, which is essential for the visually impaired people.
+User interface consists of a wearable forehead belt, integrating RGB and depth cameras, tactile feedback device and bone conduction headphones.
+Although more expensive than standard ones, bone conduction headphones do not block the ears and allow the user to perceive audio information from the surrounding environment, which is essential for the visually impaired people.
 
@@
 
-%The proposed system  consists of three major parts: is a computational device the user currently uses for completing other daily tasks.
-It consists of sensors and actuators, integrated into smartphone-based computational core, which was chosen due its avialability to wide population, and capability to perform the required computations or forward visual information to the external server via the Internet connection.
-Sensors are mounted on forehead belt include: RGB camera, depth camera, IMU.
-Actuator set consists of bone conductive headphones, and head belt for presenting tactile-feedback to the user.
-%We suggest to use bone conductive headphones, ...
-
-%\textbf{Inference} subsystem consists of server computer with internet connection and set of computer vision algorithms, selected according to our methodology ed (see.
-Sec.~\ref{sec:method}): Faster RCNN object detector \cite{?}, trainto detect important objects (doors, floors, elevators, stairs, corridor junctions, etc.), CNN-RNN-based scene description \cite{Liu},\cite{Ren}, \cite{Dai}, place recognition \cite{Ohn-Bar}, face recognition \cite{Amos}, obstacle detection \cite{Laina}, and possibly other modules.
-
-%HVCS operation cycle is started by \textbf{Device} reading sensor data and transmitting it to the server for an analysis.
-Server calculates feedback signal and transmits it back to the device for presenting to the user.
-
 \section{Discussion}
@@
 Main advantages of therein suggested system are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via the Internet connection, present the output of video processing to the user through a combined audio/tactile interface.
-%bone conductive headphone-tactile actuator, comparatively low cost and consequently increased potential availability of the device. 
+%bone conduction headphone-tactile actuator, comparatively low cost and consequently increased potential availability of the device. 
 The suggested system does not aim to replace the main travelling aid of visually impaired people - the white cane.
@@
 Economical feasibility of the proposed solution may also be questioned.
-Advanced technology (high-end smartphone, depth camera, tactile feedback device, bone conductive headphones) is needed to ensure reliable functioning of the system.
+Advanced technology (high-end smartphone, depth camera, tactile feedback device, bone conduction headphones) is needed to ensure reliable functioning of the system.
 A combination of such components may be perceived as costly by the end users.
@@
 
-%\bibitem{Poggi} Poggi, M., Mattoccia, S.
-A wearable mobility aid for the visually impaired based on embedded 3D vision and deep learning.
-2016 IEEE Symposium on Computers and Communication (ISCC), 2016
-
 \end{thebibliography}

### 2018-10-09 bare_conf.tex
bibliography fix.
bare_conf.tex
updated affiliation
bare_conf.tex
Darius Plikynas and acknowledgment is added

@@
 \IEEEauthorblockN{~\\[-0.4ex]\large Audrius Indriulionis\\[0.3ex]\normalsize}
-\IEEEauthorblockA{Vilnius Gediminas Technical University\\
-Vilnius, Lithuania}
+\IEEEauthorblockA{Vilnius Gediminas Technical University,\\
+Nature Research Center, Vilnius, Lithuania}
+
 \and
@@
 University Hospital of North Norway\\
-Tromsø, Norway}}
+Tromsø, Norway}
+
+\and
+\author{\IEEEauthorblockN{~\\[-0.4ex]\large Darius Plikynas\\[0.3ex]\normalsize}
+\IEEEauthorblockA{Vilnius Gediminas Technical University\\
+Vilnius, Lithuania}
+}
 
@@
 % use section* for acknowledgement
-%\section*{Acknowledgment}
+\section*{Acknowledgment}
+This research is/was funded by the European Regional Development Fund according to the supported activity ‘Research Projects Implemented by World-class Researcher Groups’ under Measure No.
+01.2.2-LMT-K-718.
+
 %The authors would like to thank...
@@
 \begin{thebibliography}{1}
-\bibitem{Amos} Amos, B., Ludwiczuk, B., and Satyanarayanan, M. Openface:
-A general-purpose face recognition library with mobile applications. Technical report, CMU-CS-16-118, CMU School of Computer Science, 2016.
 
@@
 
-\bibitem{Carroll} Carroll, J. M., Rosson, M. B. Participatory design in community informatics. Des. Stud., vol. 28, no. 3, pp. 243-261, May 2007.
-
 \bibitem{Csapo} Csap\'{o}, A., Wers\'{e}nyi, G., Nagy, H., Stockman, T.
@@
 275-286, 2015.
+
+\bibitem{Poggi} Poggi, M., Mattoccia, S.
+A wearable mobility aid for the visually impaired based on embedded 3d vision and deep learning.
+Proceeding of IEEE Symposium on Compututers and Communication, pp.
+208-213, 2016.
+
+\bibitem{Zientara} Zientara, P.,A., Lee, S., Smith, G., H., Brenner, R., Itti, L., Rosson M., B., Carroll, J., M., Irick K., M., Narayanan, V.
+Third Eye: A shopping assistant for the visually impaired.
+Computer Vol.
+50, Issue 2, pp.
+16-24, 2017.
+
+\bibitem{Owayjan} Owayjan, M., Hayek, A., Nassrallah, H., Eldor, M.
+Smart Assistive Navigation System for Blind and Visually Impaired Individuals.
+2015 International Conference on Advances in Biomedical Engineering (ICABME), 2015.
 
@@
 
-\bibitem{Laina} Laina, I., Rupprecht, C., Belagiannis, V., Tombari, F., Navab, N.
-Deeper depth prediction with fully convolutional residual networks.
-Fourth International Conference on 3D Vision (3DV), pp.
-239-248, 2016.
-
-\bibitem{Liu} Liu, Ch., Mao, J., Sha, F., Yuille, A. Attention Correctness in Neural Image Captioning. Proceedings of the Thirty-First AAAI Conference on Artificial Intelligence, pp. 4176-4182, 2017.
-
-\bibitem{Ohn-Bar}  Ohn-Bar, E., Kitani, K., Asakawa, Ch. Personalized Dynamics Models for Adaptive Assistive Navigation Interfaces. arXiv:1804.04118, [cs.LG], 2018.
-
-\bibitem{Owayjan} Owayjan, M., Hayek, A., Nassrallah, H., Eldor, M.
-Smart Assistive Navigation System for Blind and Visually Impaired Individuals.
-2015 International Conference on Advances in Biomedical Engineering (ICABME), 2015.
-
-\bibitem{Poggi} Poggi, M., Mattoccia, S.
-A wearable mobility aid for the visually impaired based on embedded 3d vision and deep learning.
-Proceeding of IEEE Symposium on Compututers and Communication, pp.
-208-213, 2016.
+\bibitem{Carroll} Carroll, J. M., Rosson, M. B. Participatory design in community informatics. Des. Stud., vol. 28, no. 3, pp. 243-261, May 2007.
 
@@
 
-\bibitem{Zientara} Zientara, P.,A., Lee, S., Smith, G., H., Brenner, R., Itti, L., Rosson M., B., Carroll, J., M., Irick K., M., Narayanan, V.
-Third Eye: A shopping assistant for the visually impaired.
-Computer Vol.
-50, Issue 2, pp.
-16-24, 2017.
+\bibitem{Liu} Liu, Ch., Mao, J., Sha, F., Yuille, A. Attention Correctness in Neural Image Captioning. Proceedings of the Thirty-First AAAI Conference on Artificial Intelligence, pp. 4176-4182, 2017.
+
+\bibitem{Ohn-Bar}  Ohn-Bar, E., Kitani, K., Asakawa, Ch. Personalized Dynamics Models for Adaptive Assistive Navigation Interfaces. arXiv:1804.04118, [cs.LG], 2018.
+
+\bibitem{Amos} Amos, B., Ludwiczuk, B., and Satyanarayanan, M. Openface:
+A general-purpose face recognition library with mobile applications. Technical report, CMU-CS-16-118, CMU School of Computer Science, 2016.
+
+\bibitem{Laina} Laina, I., Rupprecht, C., Belagiannis, V., Tombari, F., Navab, N.
+Deeper depth prediction with fully convolutional residual networks.
+Fourth International Conference on 3D Vision (3DV), pp.
+239-248, 2016.
 

### 2018-10-09 bare_conf.tex
Author list fixed, some text changes.

--- 2018-10-08 bare_conf.tex
@@
 % affiliations
-\author{\IEEEauthorblockN{~\\[-0.4ex]\large Povilas Daniu\v{s}is\\[0.3ex]\normalsize}
-\IEEEauthorblockA{Vilnius Gediminas Technical University\\
-Vilnius, Lithuania}
-\and
-\IEEEauthorblockN{~\\[-0.4ex]\large Audrius Indriulionis\\[0.3ex]\normalsize}
-\IEEEauthorblockA{Vilnius Gediminas Technical University\\
-Vilnius, Lithuania}
-\and
-\IEEEauthorblockN{~\\[-0.4ex]\large Andrius Budrionis\\[0.3ex]\normalsize}
-\IEEEauthorblockA{Vilnius Gediminas Technical University\\
-Vilnius, Lithuania\\
-Norwegian Centre for E-health Research\\
-University Hospital of North Norway\\
-Tromsø, Norway}}
+%\author{\IEEEauthorblockN{~\\[-0.4ex]\large Povilas Daniu\v{s}is\\[0.3ex]\normalsize}
+%\IEEEauthorblockA{Vilnius Gediminas Technical University\\
+%Vilnius, Lithuania}
+%\and
+%\IEEEauthorblockN{~\\[-0.4ex]\large Audrius Indriulionis\\[0.3ex]\normalsize}
+%\IEEEauthorblockA{Vilnius Gediminas Technical University,\\
+%Nature Research Center, Vilnius, Lithuania}
+%\and
+%\IEEEauthorblockN{~\\[-0.4ex]\large Andrius Budrionis\\[0.3ex]\normalsize}
+%\IEEEauthorblockA{Vilnius Gediminas Technical University\\
+%Vilnius, Lithuania\\
+%Norwegian Centre for E-health Research\\
+%University Hospital of North Norway\\
+%Tromsø, Norway}
+%\and
+%\author{\IEEEauthorblockN{~\\[-0.4ex]\large Darius Plikynas\\[0.3ex]%\normalsize}
+%\IEEEauthorblockA{Vilnius Gediminas Technical University\\
+%Vilnius, Lithuania}
+%}}
 
@@
 % 
-%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
-%Homer Simpson\IEEEauthorrefmark{2},
-%James Kirk\IEEEauthorrefmark{3}, 
-%Montgomery Scott\IEEEauthorrefmark{3} and
-%Eldon Tyrell\IEEEauthorrefmark{4}}
-%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-%Georgia Institute of Technology,
-%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-%Email: homer@thesimpsons.com}
-%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-%Telephone: (800) 555--1212, Fax: (888) 555--1212}
-%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
+\author{\IEEEauthorblockN{Povilas Daniu\v{s}is\IEEEauthorrefmark{1},
+Audrius Indriulionis\IEEEauthorrefmark{1}\IEEEauthorrefmark{3},
+Andrius Budrionis\IEEEauthorrefmark{1}\IEEEauthorrefmark{2} and 
+Darius Plikynas\IEEEauthorrefmark{1}}
+\IEEEauthorblockA{\IEEEauthorrefmark{1}Vilnius Gediminas Technical University,\\
+Vilnius, Lithuania.
+}
+\IEEEauthorblockA{\IEEEauthorrefmark{2}Norwegian Centre for E-health Research, University Hospital of North Norway,\\
+Troms\o, Norway.}
+\IEEEauthorblockA{\IEEEauthorrefmark{3}Nature Research Center,\\ 
+Vilnius, Lithuania.
+}}
 
@@
 Many of the previously proposed electronic aids for the blind count on highly specialized hardware, for instance smart glasses \cite{Zientara}, Microsoft Kinnect sensors \cite{Owayjan}, helmet-mounted photo sensors and cameras \cite{Dunai}.
-Such systems often lack convenience and bring additional complexity into daily tasks, which visually impaired people currently manage by the help of a white cane.
+Such a systems often lack convenience and bring additional complexity into daily tasks, which visually impaired people currently manage by the help of a white cane.
 This project puts major emphasis on developing a tool, which seamlessly integrates with the hardware visually impaired persons already have on-hand and is used to (smartphone).
@@
 
-%The cornerstones of the proposed solution are its inferface and external server, capable running computationally demanding modern image processing algorithms.
+% Man atrodo, kad cia du svarbiausi punktai, kuriuos reiktu akcentuoti.
+The cornerstones of the proposed solution are its user inferface and external vision processor - server, capable of running computationally demanding modern computer vision algorithms.
 
+% User interface
 User interface consists of a wearable forehead belt, integrating RGB and depth cameras, tactile feedback device and bone conduction headphones.
@@
 
+% External vision processor
 %visus sutrumpinimus reikia pirma parasyt pilnai, pvz Neural Network (NN)
-External server processes visual data employing a set of computer vision algorithms: faster RCNN object detector \cite{Ren}, trained to detect important objects, CNN-RNN-based scene description \cite{Liu}, place recognition \cite{Ohn-Bar}, face recognition \cite{Amos}, obstacle detection \cite{Laina}, among others.
+External server processes visual data employing a set of computer vision algorithms, selected according to our method (see Sec.~\ref{sec:method}): faster regions with convolutional neural network features (faster R-CNN) object detector \cite{Ren}, trained to detect important objects, convolutional and recurrent neural network (CNN and RNN)-based scene description \cite{Liu}, place recognition \cite{Ohn-Bar}, face recognition \cite{Amos}, obstacle detection \cite{Laina}, among others.
 After completing the analysis results are transmitted back to the smartphone and represented to the user through the aforementioned interface.
@@
   \begin{center}
-    \includegraphics[scale=0.7]{./img/cropped_diagram.pdf}  
+    \includegraphics[scale=0.9]{./img/cropped_diagram.pdf}  
   \end{center}
@@
 \end{figure}
-
-%\end{wrapfigure}
-
-%Following the above methodology we suggest the impaired human vision compensation system (\textbf{HVCS}), consisting of \textbf{Device} and \textbf{Inference} components (see Fig.~\ref{fig:schematics}).
-
-%padalijimas i 2 komponentus man nelabai aiskus. As dalinciau i input (kameros, sensoriai), output (ausines, vibratoriu matricos), processing (local, remote). 
-% tai kas dabar yra prie Inference, siulau perfrazuot kaip Functionality, ka as minejau Method.
-Taip pat visa Results skyreli reiktu labiau susiet su Method.
-Reiktu, kad visi 4 Method pamineti punktai isrysketu ir Results.
-%Results skyrelyje nereiktu taip stipriai fokusuotis i kitu grupiu tyrimus ir juos cituoti. Rezultatai juk musu.
 

### 2018-10-09 bare_conf.tex
more text added.

@@
 %\boldmath
-In this short article we describe and discuss architecture of computer vision-based system for partial compensation of lost or impaired human vision.
+In this short article we describe and discuss high level architecture of computer vision-based system for partial compensation of lost or impaired human vision.
 \end{abstract}
@@
 
-The key part of the proposed system is a smartphone device, connecting user interface and data processing components into a well-functioning ecosystem.
+The key part of the proposed system is a smartphone device, connecting user interface (UI) and data processing components into a well-functioning ecosystem.
 Smartphone was selected due to its high availability and capability to perform required computations or forward visual information for processing to the external server via the Internet connection.
 
-% Man atrodo, kad cia du svarbiausi punktai, kuriuos reiktu akcentuoti.
-The cornerstones of the proposed solution are its user inferface and external vision processor - server, capable of running computationally demanding modern computer vision algorithms.
+% Man atrodo, kad cia du esminiai sistemos komponentai, kuriuos reiktu akcentuoti:
+The cornerstones of the proposed solution are its user interface and vision processing system, consisting of external server, equipped with a set of computer vision algorithms, selected and combined according to the above methodology.
 
 % User interface
-User interface consists of a wearable forehead belt, integrating RGB and depth cameras, tactile feedback device and bone conduction headphones.
+User interface consists of a wearable forehead belt, integrating RGB and depth cameras, inertial measurement unit (IMU), tactile feedback device and bone conduction headphones.
 Although more expensive than standard ones, bone conduction headphones do not block the ears and allow the user to perceive audio information from the surrounding environment, which is essential for the visually impaired people.
+Additionally, tactile actuators may improve the quality of users perception (e.g.
+by indicating the direction of detected object with vibromotor in the corresponding direction on the forehead, instead of providing longer and less convenient to perceive text-to-speach description of the event).
+UI can interface smartphone component via USB or Wifi connection.
 
@@
 %visus sutrumpinimus reikia pirma parasyt pilnai, pvz Neural Network (NN)
-External server processes visual data employing a set of computer vision algorithms, selected according to our method (see Sec.~\ref{sec:method}): faster regions with convolutional neural network features (faster R-CNN) object detector \cite{Ren}, trained to detect important objects, convolutional and recurrent neural network (CNN and RNN)-based scene description \cite{Liu}, place recognition \cite{Ohn-Bar}, face recognition \cite{Amos}, obstacle detection \cite{Laina}, among others.
-After completing the analysis results are transmitted back to the smartphone and represented to the user through the aforementioned interface.
+Although modern high-end smartphones contain quite powerful computers inside, many computer vision algorithms often demand hardware of significantly higher computational capacity (e.g.
+server with graphics processing unit (GPU)).
+This motivates us to employ external server for vision data processing.
+In our design we assume such a server with a set of computer vision algorithms implemented and exposed via web services: faster regions with convolutional neural network features (faster R-CNN) object detector \cite{Ren}, trained to detect important objects, convolutional and recurrent neural network (CNN and RNN)-based scene description \cite{Liu}, which provides textual annotation of a given RGB image, place recognition \cite{Ohn-Bar}, face detection and recognition \cite{Amos}, obstacle detection \cite{Laina}, among others.
+After completing the analysis it's results are transmitted back to the smartphone component and represented to the user through the aforementioned interface.
 
@@
   \begin{center}
-    \includegraphics[scale=0.9]{./img/cropped_diagram.pdf}  
+    \includegraphics[scale=1.0]{./img/cropped_diagram.pdf}  
   \end{center}
@@
 %Povilai, paziurek ar cia viskas OK, pridek ka nors nuo saves
+% Pamineti mobilenet ir pan.
 Computer vision technology is under rapid development and during the last years made a major breakthrough in performance and efficiency.
@@
 We are proposing a combination of audio and tactile feedback, which may improve the interaction between the assistive technology and the user.
-Similar interfaces were suggested by research communities earlier \cite{Zientara}, \cite{Poggi}, however, existing knowledge on user preferences and evaluation of various options of tactile feedback (placement on the body, frequencies, strength, etc.) is limited.
+Similar interfaces were suggested by research communities earlier \cite{Zientara}, \cite{Poggi}, however, existing knowledge on user preferences and evaluation of various options of tactile feedback (types of actuators, placement on the body, frequencies, strength, etc.) is limited.
 
@@
 The suggested system does not aim to replace the main travelling aid of visually impaired people - the white cane.
-Instead, this computer vision tool aims to push the perception of the surounding environment boundary from 1-2 meters (achieved by using the white cane) to 2-10 meters.
+Instead, this computer vision tool aims to enhance and push the perception of the surounding environment boundary from 1-2 meters (achieved by using the white cane) to 2-10 meters.
 It may improve route planning and identification of objects of interest (for instance, doors, stairs, elevators, bus stopps, etc.).
@@
 outdoor/indoor navigation, object/face recognition, obstacle detection, etc.).
+
+%Detalisation of algorithms
 
@@
 
+%\bibitem{Verilook} \url{http://www.neurotechnology.com}
+
 \end{thebibliography}

### 2018-10-11 bare_conf.tex
More text added to Discussion.

@@
 This paper describes a high level architecture of the technology aid for visually impaired people utilising the latest achievemets in the field of computer vision.
-%(kartojasi su In this article we describe a system, which employs modern computer vision ...)
-%Andrius: nieko tokio, jei sakinys kartojasi Abstract'e. Sitai pastraipai reikia concluding sentence. Aisku galima ji perfrazuot kaip nors kitaip.
 
@@
 Main advantages of therein suggested system are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via the Internet connection, present the output of video processing to the user through a combined audio/tactile interface.
-%bone conduction headphone-tactile actuator, comparatively low cost and consequently increased potential availability of the device. 
+Comparing to an existing commercial products e.g.
+\cite{orcam}, \cite{horus}, our approach is advantageous, since it does not rely only on computational capacity of mobile handset.
+Such a combination of local interface and remote vision processor will be even more efficient in the future, with switching of mobile networks to 5G.
+Combined audio/tactile interface also may be more convenient for users, since it allows to provide more concentrated information comparing to purely audio or purely tactile interface.
+
 The suggested system does not aim to replace the main travelling aid of visually impaired people - the white cane.
@@
 
+\bibitem{orcam} https://www.orcam.com/en/
+
+\bibitem{horus} http://www.horus.tech
+
 %\bibitem{Verilook} \url{http://www.neurotechnology.com}

### 2018-10-11 bare_conf.tex
some minor input.

@@
 This motivates us to employ external server for vision data processing.
-In our design we assume such a server with a set of computer vision algorithms implemented and exposed via web services: faster regions with convolutional neural network features (faster R-CNN) object detector \cite{Ren}, trained to detect important objects, convolutional and recurrent neural network (CNN and RNN)-based scene description \cite{Liu}, which provides textual annotation of a given RGB image, place recognition \cite{Ohn-Bar}, face detection and recognition \cite{Amos}, obstacle detection \cite{Laina}, among others.
+In our design we assume such a server with a set of computer vision algorithms implemented and exposed via web services: faster regions with convolutional neural network features (faster R-CNN) object detector \cite{Ren}, trained to detect important objects, convolutional and recurrent neural network (CNN and RNN)-based scene description \cite{Liu}, which provides textual annotation of a given RGB image, place recognition \cite{Ohn-Bar}, face detection and recognition \cite{Amos}, \cite{Verilook}, obstacle detection \cite{Laina}, among others.
 After completing the analysis it's results are transmitted back to the smartphone component and represented to the user through the aforementioned interface.
@@
 
-In this article we outlined an idea of complex computer vision-based sensor architecture, which may help to partially compensate impaired or lost human sight.
+In this article we outlined an idea of complex computer vision-based cybernetic sensor architecture, which may help to partially compensate impaired or lost human sight.
 Main advantages of therein suggested system are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via the Internet connection, present the output of video processing to the user through a combined audio/tactile interface.
@@
 \cite{orcam}, \cite{horus}, our approach is advantageous, since it does not rely only on computational capacity of mobile handset.
-Such a combination of local interface and remote vision processor will be even more efficient in the future, with switching of mobile networks to 5G.
-Combined audio/tactile interface also may be more convenient for users, since it allows to provide more concentrated information comparing to purely audio or purely tactile interface.
+Such a combination of mobile interface and remote vision processor will be even more efficient in the future, with switching of mobile networks to 5G.
+Combined audio/tactile interface also may be more convenient for the users, since it allows to provide more concentrated information comparing to purely audio or purely tactile interface.
 
@@
 
+\bibitem{Verilook} https://www.neurotechnology.com/verilook.html
+
 \bibitem{Laina} Laina, I., Rupprecht, C., Belagiannis, V., Tombari, F., Navab, N.
@@
 
-%\bibitem{Verilook} \url{http://www.neurotechnology.com}
-
 \end{thebibliography}

### 2018-10-12 bare_conf.tex
some text editing.

@@
 Additionally, tactile actuators may improve the quality of users perception (e.g.
-by indicating the direction of detected object with vibromotor in the corresponding direction on the forehead, instead of providing longer and less convenient to perceive text-to-speach description of the event).
+by indicating the direction of detected object with vibromotor in the corresponding area on the forehead belt, instead of providing longer and less convenient to perceive audio description of the event).
 UI can interface smartphone component via USB or Wifi connection.
@@
 %visus sutrumpinimus reikia pirma parasyt pilnai, pvz Neural Network (NN)
-Although modern high-end smartphones contain quite powerful computers inside, many computer vision algorithms often demand hardware of significantly higher computational capacity (e.g.
+Although modern high-end smartphones are quite powerful computers themselves, many computer vision algorithms often demand hardware of significantly higher computational capacity (e.g.
 server with graphics processing unit (GPU)).
@@
 
-In this article we outlined an idea of complex computer vision-based cybernetic sensor architecture, which may help to partially compensate impaired or lost human sight.
+In this article we outlined an idea of computer vision-based cybernetic sensor architecture, which may help to partially compensate impaired or lost human sight.
 Main advantages of therein suggested system are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via the Internet connection, present the output of video processing to the user through a combined audio/tactile interface.
@@
 
-\bibitem{orcam} https://www.orcam.com/en/
+\bibitem{orcam} https://www.orcam.com
 

### 2018-10-12 bare_conf.tex
some editing.

--- 2018-10-11 bare_conf.tex
@@
 Although more expensive than standard ones, bone conduction headphones do not block the ears and allow the user to perceive audio information from the surrounding environment, which is essential for the visually impaired people.
-Additionally, tactile actuators may improve the quality of users perception (e.g.
-by indicating the direction of detected object with vibromotor in the corresponding direction on the forehead, instead of providing longer and less convenient to perceive text-to-speach description of the event).
+The tactile feedback in certain cases may improve the quality of users perception (e.g.
+by indicating the direction of detected object with vibromotor in the corresponding area on the forehead belt, instead of providing longer and less convenient to perceive audio description of the event).
 UI can interface smartphone component via USB or Wifi connection.
@@
 \cite{orcam}, \cite{horus}, our approach is advantageous, since it does not rely only on computational capacity of mobile handset.
-Such a combination of local interface and remote vision processor will be even more efficient in the future, with switching of mobile networks to 5G.
-Combined audio/tactile interface also may be more convenient for users, since it allows to provide more concentrated information comparing to purely audio or purely tactile interface.
+Such a combination of mobile interface and remote vision processor will be even more efficient in the future, with switching of mobile networks to 5G.
+Combined audio/tactile interface also may be more convenient for the users, since it allows to provide the feedback more efficiently, comparing to purely audio or purely tactile means.
 
@@
 More research is needed to demonstrate the benefits of the system in real-world scenarios.
-
-%On the other side, due to remotelly conducted visual analysis, in some cases the suggested system may suffer from too large latency, its reliability depends on stability and quality of Internet connection.
-We are currently  implementing suggested the architecture into working prototype for preliminary evaluation by potential end users.
 
@@
 
+%\bibitem{Verilook} VeroLook SDK, https://www.neurotechnology.com/verilook.html
+
 \bibitem{Laina} Laina, I., Rupprecht, C., Belagiannis, V., Tombari, F., Navab, N.
@@
 
-\bibitem{orcam} https://www.orcam.com/en/
+\bibitem{orcam} https://www.orcam.com
 
 \bibitem{horus} http://www.horus.tech
-
-%\bibitem{Verilook} \url{http://www.neurotechnology.com}
 

### 2018-10-13 bare_conf.tex
Some paragraphs added. Abstract extended. More references added.

@@
 In this short article we describe and discuss high level architecture of computer vision-based system for partial compensation of lost or impaired human vision.
+Combining standard smartphone device, external deep learning based vision processor and audio-tactile user interface into compact visual perception compensation device the suggested architecture may be advantageous both for researchers and industrial product developers.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Computer vision; Mobile application; Aid for blind and visually impaired; Tactile feedback; Impaired human vision compensation.%
+Computer vision; Deep learning; Mobile application; Aid for blind and visually impaired; Audio feedback; Tactile feedback; Impaired human vision compensation.%
 \end{IEEEkeywords}
@@
 server with graphics processing unit (GPU)).
-This motivates us to employ external server for vision data processing.
-In our design we assume such a server with a set of computer vision algorithms implemented and exposed via web services: faster regions with convolutional neural network features (faster R-CNN) object detector \cite{Ren}, trained to detect important objects, convolutional and recurrent neural network (CNN and RNN)-based scene description \cite{Liu}, which provides textual annotation of a given RGB image, place recognition \cite{Ohn-Bar}, face detection and recognition \cite{Amos}, obstacle detection \cite{Laina}, among others.
+This motivates us to employ an external server for vision data processing.
+In our design we assume such a server with a set of computer vision algorithms implemented and exposed via web services: faster regions with convolutional neural network features (faster R-CNN) object detector \cite{Ren}, trained to detect important objects, convolutional and recurrent neural network (CNN and RNN)-based scene description \cite{Liu}, which provides textual annotation of a given RGB image, place recognition \cite{Ohn-Bar}, face detection and recognition \cite{Amos}, obstacle detection \cite{Laina}, action recognition \cite{Valor} among others.
 After completing the analysis it's results are transmitted back to the smartphone component and represented to the user through the aforementioned interface.
+
+% How user controls system
+Gesture or voice command recognition can be used to select system's operation regime (e.g. optical character recognition (OCR), currency recognition, object detection, navigation aid).
+
+% Potential applications
+Social networking functionality was accepted as a potentially important feature allowing other users/volunteers to describe certain objects (for instance, temporary road works) with exact location and description.
+Navigating around such obstacles can be challenging for computer vision-based tools and may decrease user's trust in the tool.
+Integration of additional information from other users, governmental organizations and volunteers could be of high value for the visually impaired people.
 
@@
 Deep learning neural networks, which are de facto standard in modern image/video processing, are now well supported by software libraries and dedicated processing hardware is built-in even in relatively low-power computational devices, such as smartphones.
+The application of both open source and commercial computer vision software libraries (e.g.
+\cite{Verilook} face recognition kit) could reduce development costs.
 These devices are also equipped with 4G Internet connectivity and sufficient computational power to perform initial data processing locally.
@@
 Vol.
-9, issule 4,  pp.
+9, issue 4,  pp.
 275-286, 2015.
@@
 
-%\bibitem{Verilook} VeroLook SDK, https://www.neurotechnology.com/verilook.html
-
 \bibitem{Laina} Laina, I., Rupprecht, C., Belagiannis, V., Tombari, F., Navab, N.
@@
 
-\bibitem{orcam} https://www.orcam.com
+\bibitem{Valor} Varol, G., Laptev, I., Schmid, C.
+Long-Term Temporal Convolutions for Action Recognition.
+IEEE Transactions on Pattern Analysis and Machine Intelligence.
+Vol.
+40, issue 6, pp.
+1510 - 1517.
 
-\bibitem{horus} http://www.horus.tech
+\bibitem{Verilook} VeriLook SDK, https://www.neurotechnology.com/verilook.html
+
+\bibitem{orcam} Orcam system, https://www.orcam.com
+
+\bibitem{horus} Horus system, http://www.horus.tech
 

### 2018-10-13 bare_conf.tex
small fixes.

@@
 In this short article we describe and discuss high level architecture of computer vision-based system for partial compensation of lost or impaired human vision.
-Combining standard smartphone device, external deep learning based vision processor and audio-tactile user interface into compact visual perception compensation device the suggested architecture may be advantageous both for researchers and industrial product developers.
+Combining standard smartphone device, external deep learning based vision processor and audio-tactile user interface into compact visual perception compensation device the suggested architecture may be advantageous both for adacemic researchers and commercial product developers.
 \end{abstract}
@@
 This motivates us to employ an external server for vision data processing.
-In our design we assume such a server with a set of computer vision algorithms implemented and exposed via web services: faster regions with convolutional neural network features (faster R-CNN) object detector \cite{Ren}, trained to detect important objects, convolutional and recurrent neural network (CNN and RNN)-based scene description \cite{Liu}, which provides textual annotation of a given RGB image, place recognition \cite{Ohn-Bar}, face detection and recognition \cite{Amos}, obstacle detection \cite{Laina}, action recognition \cite{Valor} among others.
+In our design we assume such a server with a set of computer vision algorithms implemented and exposed via web services: faster regions with convolutional neural network features (faster R-CNN) object detector \cite{Ren}, trained to detect important objects, convolutional and recurrent neural network (CNN and RNN)-based scene description \cite{Liu}, which provides textual annotation of a given RGB image, place recognition \cite{Ohn-Bar}, face detection and recognition \cite{Amos}, obstacle detection \cite{Laina}, action recognition \cite{Valor}, among others.
 After completing the analysis it's results are transmitted back to the smartphone component and represented to the user through the aforementioned interface.
@@
 \cite{orcam}, \cite{horus}, our approach is advantageous, since it does not rely only on computational capacity of mobile handset.
-Such a combination of mobile interface and remote vision processor will be even more efficient in the future, with switching of mobile networks to 5G.
+Such a combination of mobile interface and remote vision processor will be even more efficient in the future, with switching of the mobile networks to 5G.
 Combined audio/tactile interface also may be more convenient for the users, since it allows to provide the feedback more efficiently, comparing to purely audio or purely tactile means.

### 2018-10-14 bare_conf.tex
text updates in Abstract, Results and Discussion

--- 2018-10-13 bare_conf.tex
@@
 %\boldmath
-In this short article we describe and discuss high level architecture of computer vision-based system for partial compensation of lost or impaired human vision.
-Combining standard smartphone device, external deep learning based vision processor and audio-tactile user interface into compact visual perception compensation device the suggested architecture may be advantageous both for researchers and industrial product developers.
+This paper presents a high level architecture for computer vision-based system for partial compensation of lost or impaired human vision.
+It combines standard smartphone device, external deep learning-based live video processoing infrastructure and audio/tactile user interface.
+The proposed architecture is based on  input from user-centered design process, involving end users into system development process.
+The paper discusses user needs and expectations towards electronic travelling aids for the blind and and highlights limitations of the existing solutions.
+The suggested architecture may be used as a basis for developing computer vision-based tools for visually impaired individuals.
+%In this short article we describe and discuss high level architecture of computer vision-based system for partial compensation of lost or impaired human vision.
+Combining standard smartphone device, external deep learning-based live video processoing infrastructure and audio/tactile user interface into compact visual perception compensation device .
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Computer vision; Deep learning; Mobile application; Aid for blind and visually impaired; Audio feedback; Tactile feedback; Impaired human vision compensation.%
+Computer vision; Deep learning; Mobile application; Aid for blind and visually impaired; Audio feedback; Tactile feedback; Impaired human vision compensation; User-centered design.%
 \end{IEEEkeywords}
-
 % For peer review papers, you can put extra information on the cover
@@
 \IEEEpeerreviewmaketitle
-
 \section{Introduction}
 \label{sec:introduction}
-
 More than $250$ million people worldwide have moderate to severe vision impairment, while ($\approx 36$ million are blind) \cite{Bourne}.
 During the past decades significant effort was devoted to develop computer vision and other sensor based aids (e.g.
-\cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara}) for helping the blind and visually impaired users to better perceive the surrounding world.
+\cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara}) for helping the blind and visually impaired users to perceive the surrounding world better.
 However, computer vision is a rapidly evolving field; systems based on the aforementioned approaches become outdated in a relitively short time and often lack accuracy and reliability in real-world conditions in comparisson to the state-of-the-art technologies.
@@
 Many of the previously proposed electronic aids for the blind count on highly specialized hardware, for instance smart glasses \cite{Zientara}, Microsoft Kinnect sensors \cite{Owayjan}, helmet-mounted photo sensors and cameras \cite{Dunai}.
-Such a systems often lack convenience and bring additional complexity into daily tasks, which visually impaired people currently manage by the help of a white cane.
+Such systems often lack convenience and bring additional complexity into daily tasks, which visually impaired people currently manage by the help of a white cane.
 This project puts major emphasis on developing a tool, which seamlessly integrates with the hardware visually impaired persons already have on-hand and is used to (smartphone).
@@
 \item Interface between the visually impaired person and the assisted technology;
-\item Appearance, usability and potential costs of the final product. 
+\item Appearance, usability and potential costs of the proposed product. 
 \end{enumerate}
-Design process involved testing of the existing mobile phone app (Seeing AI) for assisting visually impaired persons.
-Semi-structured tests were performed by the visually impaired participants accompanied by a researcher from a project group.
+Design process included testing of the existing mobile phone app (Seeing AI) for assisting visually impaired people.
+Semi-structured tests were performed by the visually impaired participants accompanied by a researcher from the project group.
 Strengths and weaknesses of the existing solutions are reflected in the design of the proposed system.
@@
 % Man atrodo, kad cia du esminiai sistemos komponentai, kuriuos reiktu akcentuoti:
-The cornerstones of the proposed solution are its user interface and vision processing system, consisting of external server, equipped with a set of computer vision algorithms, selected and combined according to the above methodology.
+%The cornerstones of the proposed solution are its user interface and vision processing system, consisting of external server, equipped with a set of computer vision algorithms, selected and combined according to the above methodology.
 
 % User interface
-User interface consists of a wearable forehead belt, integrating RGB and depth cameras, inertial measurement unit (IMU), tactile feedback device and bone conduction headphones.
-Although more expensive than standard ones, bone conduction headphones do not block the ears and allow the user to perceive audio information from the surrounding environment, which is essential for the visually impaired people.
-The tactile feedback in certain cases may improve the quality of users perception (e.g.
-by indicating the direction of detected object with vibromotor in the corresponding area on the forehead belt, instead of providing longer and less convenient to perceive audio description of the event).
-UI can interface smartphone component via USB or Wifi connection.
+UI consists of a wearable forehead belt, integrating RGB and depth cameras, inertial measurement unit (IMU), tactile feedback device and bone conduction headphones.
+Although more expensive than standard ones, bone conduction headphones do not block the ears and allow the user to perceive audio information from the surrounding environment and the system at the same time, which is essential for the visually impaired people.
+Some types of guidance information may be more efficiently perceived through tactile feedback device than audio channel.
+For instance, indicating the direction of a detected object with a vibromotor on the corresponding area on the forehead belt, instead of providing audio description.
+More research is needed to clarity how variuos types of guidance information should be represented to the user in the most convenient and efficient way.
+
+%The tactile feedback may improve the quality of users perception (e.g. by ). UI can interface smartphone component via USB or Wifi connection.
 
@@
 %visus sutrumpinimus reikia pirma parasyt pilnai, pvz Neural Network (NN)
-Although modern high-end smartphones are quite powerful computers themselves, many computer vision algorithms often demand hardware of significantly higher computational capacity (e.g.
-server with graphics processing unit (GPU)).
-This motivates us to employ an external server for vision data processing.
-In our design we assume such a server with a set of computer vision algorithms implemented and exposed via web services: faster regions with convolutional neural network features (faster R-CNN) object detector \cite{Ren}, trained to detect important objects, convolutional and recurrent neural network (CNN and RNN)-based scene description \cite{Liu}, which provides textual annotation of a given RGB image, place recognition \cite{Ohn-Bar}, face detection and recognition \cite{Amos}, obstacle detection \cite{Laina}, action recognition \cite{Valor} among others.
-After completing the analysis it's results are transmitted back to the smartphone component and represented to the user through the aforementioned interface.
+Although modern high-end smartphones are powerful computational devices, many computer vision algorithms  require hardware of significantly higher processing power (e.g.
+a server equipped with a high-end graphics processing unit (GPU)).
+Therefore, an external server is used for live vision data processing.
+In our design we envision a computational server hosting set of computer vision algorithms implemented and exposed via web services: faster regions with convolutional neural network features (faster R-CNN) object detector \cite{Ren}, trained to detect important objects, convolutional and recurrent neural network-based (CNN and RNN) scene descriptor \cite{Liu}, which provides textual annotation of a given RGB image, place recognition \cite{Ohn-Bar}, face detection and recognition \cite{Amos}, obstacle detection \cite{Laina}, action recognition \cite{Valor}, among others.
+After video analysis is completed on the server side, results are transmitted back to the smartphone component and represented to the user through the aforementioned UI.
 
 % How user controls system
-Gesture or voice command recognition can be used to select system's operation regime (e.g. optical character recognition (OCR), currency recognition, object detection, navigation aid).
+The user interacts with the system through gestures, voice commands or a specifically designed user interface on the smartphone.
+User input is required for selecting the operation mode of the system, i.e.
+swithching between optical character recognition (OCR), currency recognition, object detection, navigation aid and other available functions.
 
 % Potential applications
-Social networking functionality was accepted as a potentially important feature allowing other users/volunteers to describe certain objects (for instance, temporary road works) with exact location and description.
+Social networking functionality was highlighted as a potentially important feature allowing other users/volunteers contribute to up-to-date and high quality guidance (for instance, temporary road works) with exact location and description.
 Navigating around such obstacles can be challenging for computer vision-based tools and may decrease user's trust in the tool.
@@
 
-Discussions on functionality and key features of the solution revealed a gap between the aims of the existing tools, which are often focused on advanced navigation and scene description features, and actual user needs.
-For example, the end users highlighted that a simplistic solution for navigating is lacking.
-%They were not excited about advanced object detection and scene description techniques, which may overcomplicate their daily life. 
-Major focus was put on a easy to use and minimalistic tool, which can be trusted.
+Discussions on the key features of the proposed solution revealed a gap between the functionality of the existing tools, which are often focused on advanced navigation and scene description features, and actual user needs.
+For example, the end-users highlighted that a simplistic solution for navigating is lacking.
+Major focus was put on an easy-to-use and minimalistic tool, which can be trusted.
 Reliable object detection, direction and approximate distance to an obstacle were highlighted as major requirements.
@@
 Additional information, such as type of a passing car, blossoming flowers in the park or a person riding a bicycle was considered as overwhelming and distractive.
-
-%Social networking functionality was accepted as a potentially important feature allowing other users/volunteers to describe certain objects (for instance, temporary road works) with exact location and description.
-Navigating around such obstacles can be challenging for computer vision-based tools and may decrease user's trust in the tool.
-Integration of additional information from other users, governmental organizations and volunteers could be of high value for the visually impaired people.
 
@@
 Deep learning neural networks, which are de facto standard in modern image/video processing, are now well supported by software libraries and dedicated processing hardware is built-in even in relatively low-power computational devices, such as smartphones.
-The application of both open source and commercial computer vision software libraries (e.g.
-\cite{Verilook} face recognition kit) could reduce development costs.
+%Andrius: as sita sakini ismesciau, man jis nelabai cia tinka
+The application of both open source and commercial computer vision software libraries (e.g. \cite{Verilook} face recognition kit) could reduce development costs. 
+%Andrius: site sakiniai turetu eiti iskart po "... such as snartphones."
 These devices are also equipped with 4G Internet connectivity and sufficient computational power to perform initial data processing locally.
@@
 The proposed assistive technology should supplement the tool that visually impaired persons used for decades - the white cane.
-Using a white cane requires little to none training, has very low costs and is relatively reliable.
+Using a white cane requires little to no training, has very low costs and is relatively reliable.
 It provides information on the surrounding objects 1-2 meters in front of the user.
-While the cane can used to detect a nearby obstacle, electronic travel aid could be beneficial for longer range (2-10m) route planning and object detection.
+While the cane can be used to detect nearby obstacles, electronic travel aid could be beneficial for longer range (2-10m) route planning and object detection.
 However, it should integrate seamlessly into the existing navigation practices of visually impaired people.
@@
 
-In this article we outlined an idea of complex computer vision-based  sensor architecture, which may help to partially compensate impaired or lost human sight.
-Main advantages of therein suggested system are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via the Internet connection, present the output of video processing to the user through a combined audio/tactile interface.
-Comparing to an existing commercial products e.g.
-\cite{orcam}, \cite{horus}, our approach is advantageous, since it does not rely only on computational capacity of mobile handset.
-Such a combination of mobile interface and remote vision processor will be even more efficient in the future, with switching of mobile networks to 5G.
-Combined audio/tactile interface also may be more convenient for the users, since it allows to provide the feedback more efficiently, comparing to purely audio or purely tactile means.
+%In this article we outlined an idea of complex computer vision-based sensor architecture, which may help to partially compensate impaired or lost human sight.
 
-The suggested system does not aim to replace the main travelling aid of visually impaired people - the white cane.
+This paper outlines a high level architecture of a computer vision-based system, which may help to partially compensate impaired or lost human vision.
+The main advantages of therein suggested system are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via the Internet connection and present the output of the video processing to the user through a combined audio/tactile interface.
+
+Similar functionality has been previuosly addressed by research communities \cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara} and industy \cite{orcam}, \cite{horus}.
+The main difference between the aforementioned commercial solutions and the proposed system is the ability to utilize external resources for computationally intensive live video processing tasks.
+While the availability of the computational power could be seen as the main advantage, it comes with high cost - dependency on a well-functioning mobile broadband.
+The development of the high-speed mobile networks (4G and 5G in the nearest future) is likely to make the major limitation of the proposed architecture obsolete, especially in densely populated areas containing many hazards for the blind.
+Combined audio/tactile interface may also be more convenient for the users, allowing to provide feedback in a more efficient way than using tactile or audio interfaces separately.
+
+%our approach is advantageous, since it does not rely only on computational capacity of mobile handset.
+Such a combination of mobile interface and remote vision processor will be even more efficient in the future, with switching of the mobile networks to 5G.
+
+It is important to emphasize that the suggested system does not aim to replace the main travelling aid of visually impaired people - the white cane.
 Instead, this computer vision tool aims to enhance and push the perception of the surounding environment boundary from 1-2 meters (achieved by using the white cane) to 2-10 meters.
 It may improve route planning and identification of objects of interest (for instance, doors, stairs, elevators, bus stopps, etc.).
-This functionality corresponds with the main requirement for electronic travelling aids identified by the end users - direction and distance estimation to a selected object.
+This functionality corresponds with the main requirement for electronic travelling aids highlighted by the end users - direction and distance estimation to a selected object.
 The proposed hardware architecture can be used as a basis for various computer vision-based software modules, aiming to assist visually impaired users in daily activities (e.g.

### 2018-10-14 bare_conf.tex
text updates in Abstract, Results and Discussion

@@
 This paper presents a high level architecture for computer vision-based system for partial compensation of lost or impaired human vision.
-It combines standard smartphone device, external deep learning-based live video processoing infrastructure and audio/tactile user interface.
-The proposed architecture is based on  input from user-centered design process, involving end users into system development process.
-The paper discusses user needs and expectations towards electronic travelling aids for the blind and and highlights limitations of the existing solutions.
+It combines standard smartphone device, external deep learning-based live video processing infrastructure and audio/tactile user interface.
+The proposed architecture is based on  input from user-centered design process, involving end users into system development.
+The paper discusses user needs and expectations towards electronic travelling aids for the blind and highlights limitations of the existing solutions.
 The suggested architecture may be used as a basis for developing computer vision-based tools for visually impaired individuals.
@@
 \cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara}) for helping the blind and visually impaired users to perceive the surrounding world better.
-However, computer vision is a rapidly evolving field; systems based on the aforementioned approaches become outdated in a relitively short time and often lack accuracy and reliability in real-world conditions in comparisson to the state-of-the-art technologies.
+However, computer vision is a rapidly evolving field; systems based on the aforementioned approaches become outdated in a relatively short time and often lack accuracy and reliability in real-world conditions in comparison to the state-of-the-art technologies.
 In this article we describe a system, which employs modern computer vision techniques for compensation of lost or impaired vision function in humans.
@@
 This project puts major emphasis on developing a tool, which seamlessly integrates with the hardware visually impaired persons already have on-hand and is used to (smartphone).
-This paper describes a high level architecture of the technology aid for visually impaired people utilising the latest achievemets in the field of computer vision.
+This paper describes a high level architecture of the technology aid for visually impaired people utilizing the latest achievements in the field of computer vision.
 
@@
 The key part of the proposed system is a smartphone device, connecting user interface (UI) and data processing components into a well-functioning ecosystem.
-Smartphone was selected due to its high availability and capability to perform required computations or forward visual information for processing to the external server via the Internet connection.
+Smartphone was selected due to its high availability and capability to perform required computations or forward visual information for processing to the external server via the Internet.
 
@@
 For instance, indicating the direction of a detected object with a vibromotor on the corresponding area on the forehead belt, instead of providing audio description.
-More research is needed to clarity how variuos types of guidance information should be represented to the user in the most convenient and efficient way.
+More research is needed to clarity how various types of guidance information should be represented to the user in the most convenient and efficient way.
 
@@
 Therefore, an external server is used for live vision data processing.
-In our design we envision a computational server hosting set of computer vision algorithms implemented and exposed via web services: faster regions with convolutional neural network features (faster R-CNN) object detector \cite{Ren}, trained to detect important objects, convolutional and recurrent neural network-based (CNN and RNN) scene descriptor \cite{Liu}, which provides textual annotation of a given RGB image, place recognition \cite{Ohn-Bar}, face detection and recognition \cite{Amos}, obstacle detection \cite{Laina}, action recognition \cite{Valor}, among others.
+In our design we envision a computational server hosting a set of computer vision algorithms implemented and exposed via web services: faster regions with convolutional neural network features (faster R-CNN) object detector \cite{Ren}, trained to detect important objects, convolutional and recurrent neural network-based (CNN and RNN) scene descriptor \cite{Liu}, which provides textual annotation of a given RGB image, place recognition \cite{Ohn-Bar}, face detection and recognition \cite{Amos}, obstacle detection \cite{Laina}, action recognition \cite{Valor}, among others.
 After video analysis is completed on the server side, results are transmitted back to the smartphone component and represented to the user through the aforementioned UI.
@@
 % How user controls system
-The user interacts with the system through gestures, voice commands or a specifically designed user interface on the smartphone.
-User input is required for selecting the operation mode of the system, i.e.
-swithching between optical character recognition (OCR), currency recognition, object detection, navigation aid and other available functions.
+The user interacts with the system through gestures, voice commands or specifically designed user interface on the smartphone.
+User input is required for selecting operation mode of the system, i.e.
+switching between optical character recognition (OCR), currency recognition, object detection, navigation aid and other available functions.
 
@@
 Major focus was put on an easy-to-use and minimalistic tool, which can be trusted.
-Reliable object detection, direction and approximate distance to an obstacle were highlighted as major requirements.
+Reliable object detection, direction and approximate distance to an obstacle were highlighted as the main requirements.
 To our surprise, only 5-8 distinctive object classes (for instance, buss stop, pedestrian crossing, doors, stairs, etc) were of major importance while navigating.
@@
 
-This paper outlines a high level architecture of a computer vision-based system, which may help to partially compensate impaired or lost human vision.
+This paper outlined a high level architecture of a computer vision-based system, which may help to partially compensate impaired or lost human vision.
 The main advantages of therein suggested system are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via the Internet connection and present the output of the video processing to the user through a combined audio/tactile interface.
 
-Similar functionality has been previuosly addressed by research communities \cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara} and industy \cite{orcam}, \cite{horus}.
+Similar functionality has been previously addressed by research communities \cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara} and industry \cite{orcam}, \cite{horus}.
 The main difference between the aforementioned commercial solutions and the proposed system is the ability to utilize external resources for computationally intensive live video processing tasks.
@@
 It is important to emphasize that the suggested system does not aim to replace the main travelling aid of visually impaired people - the white cane.
-Instead, this computer vision tool aims to enhance and push the perception of the surounding environment boundary from 1-2 meters (achieved by using the white cane) to 2-10 meters.
-It may improve route planning and identification of objects of interest (for instance, doors, stairs, elevators, bus stopps, etc.).
+Instead, this computer vision tool aims to enhance and push the perception of the surrounding environment boundary from 1-2 meters (achieved by using the white cane) to 2-10 meters.
+It may improve route planning and identification of objects of interest (for instance, doors, stairs, elevators, bus stops, etc.).
 This functionality corresponds with the main requirement for electronic travelling aids highlighted by the end users - direction and distance estimation to a selected object.
-The proposed hardware architecture can be used as a basis for various computer vision-based software modules, aiming to assist visually impaired users in daily activities (e.g.
+The proposed hardware architecture can be used as basis for various computer vision-based software modules, aiming to assist visually impaired users in daily activities (e.g.
 outdoor/indoor navigation, object/face recognition, obstacle detection, etc.).
@@
 Technical feasibility of the solution is dependent on the availability of high bandwidth Internet connection ensuring access to high-power data processing components.
-Insuficient bandwidth may result in latency, which may not be tolerated by the users.
+Insufficient bandwidth may result in latency, which may not be tolerated by the users.
 

### 2018-10-16 bare_conf.tex
some text, reference edition, added paragraph in Discussion.

@@
 \usepackage{graphicx}
+\usepackage{hyperref}
 
@@
 \author{\IEEEauthorblockN{Povilas Daniu\v{s}is\IEEEauthorrefmark{1},
-Audrius Indriulionis\IEEEauthorrefmark{1}\IEEEauthorrefmark{3},
-Andrius Budrionis\IEEEauthorrefmark{1}\IEEEauthorrefmark{2} and 
+Andrius Budrionis\IEEEauthorrefmark{1}\IEEEauthorrefmark{2},
+Audrius Indriulionis\IEEEauthorrefmark{1}\IEEEauthorrefmark{3} and 
 Darius Plikynas\IEEEauthorrefmark{1}}
@@
 This paper presents a high level architecture for computer vision-based system for partial compensation of lost or impaired human vision.
-It combines standard smartphone device, external deep learning-based live video processing infrastructure and audio/tactile user interface.
+It combines standard smartphone device, external deep learning-based image processing infrastructure and audio/tactile user interface.
 The proposed architecture is based on  input from user-centered design process, involving end users into system development.
@@
 More research is needed to clarity how various types of guidance information should be represented to the user in the most convenient and efficient way.
+USB and Wifi data links can be used for bidirectional data transmission between UI and smartphone component.
 
@@
 Computer vision technology is under rapid development and during the last years made a major breakthrough in performance and efficiency.
-Deep learning neural networks, which are de facto standard in modern image/video processing, are now well supported by software libraries and dedicated processing hardware is built-in even in relatively low-power computational devices, such as smartphones.
-%Andrius: as sita sakini ismesciau, man jis nelabai cia tinka
-The application of both open source and commercial computer vision software libraries (e.g. \cite{Verilook} face recognition kit) could reduce development costs. 
-%Andrius: site sakiniai turetu eiti iskart po "... such as snartphones."
-These devices are also equipped with 4G Internet connectivity and sufficient computational power to perform initial data processing locally.
+Deep learning neural networks, which are de facto standard in modern image/video processing in many real-world problems allow to achieve accuracies, similar to that of human decision (e.g.
+face recognition \cite{Amos}, object detection \cite{Ren}, among others).
+These models are now well supported by software libraries (e.g.
+\cite{Tensorflow}) and dedicated processing hardware is built-in even in relatively low-power computational devices, such as smartphones.
+These devices are also equipped with 4G Internet connectivity and sufficient computational power to perform partial or in certain cases even full vision data processing locally.
 The maturity of the aforementioned technologies suggest that our proposed computational aid for visually impaired persons may be highly feasible.
@@
 
+% live video pakeiciau i  image or video, mano nuomone ne taip ambicingai skamba.
+
 Similar functionality has been previously addressed by research communities \cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara} and industry \cite{orcam}, \cite{horus}.
-The main difference between the aforementioned commercial solutions and the proposed system is the ability to utilize external resources for computationally intensive live video processing tasks.
+The main difference between the aforementioned commercial solutions and the proposed system is the ability to utilize external resources for computationally intensive image or video processing tasks.
 While the availability of the computational power could be seen as the main advantage, it comes with high cost - dependency on a well-functioning mobile broadband.
 The development of the high-speed mobile networks (4G and 5G in the nearest future) is likely to make the major limitation of the proposed architecture obsolete, especially in densely populated areas containing many hazards for the blind.
+On the other side, increasing computational capacity of smartphones also may allow to conduct more advanced image or video processing locally.
 Combined audio/tactile interface may also be more convenient for the users, allowing to provide feedback in a more efficient way than using tactile or audio interfaces separately.
+
+Both open source (e.g.
+\cite{Tensorflow}) and state of the art commercial computer vision software (e.g.
+\cite{Verilook}) may be applied implementing the suggested architecture.
+Moreover, detalization and specification of the suggested system's hardware components following open hardware approach - by providing open repository with the detailed list of electronics components, schematics, and 3D models of mechanical parts, could provide a solid basis for semi-standard reference platform for the researchers in the field.
 
@@
 outdoor/indoor navigation, object/face recognition, obstacle detection, etc.).
-
-%Detalisation of algorithms
 
@@
 
-\bibitem{Verilook} VeriLook SDK, https://www.neurotechnology.com/verilook.html
+\bibitem{Tensorflow}  Abadi M., Agarwal A., Barham P., Brevdo E., Chen Z., Citro C., Corrado G., Davis A., Dean J., Devin M., et al.
+TensorFlow: Large-Scale Machine Learning on Heterogeneous Distributed Systems.
+2016.
+arXiv:1603.04467
 
-\bibitem{orcam} Orcam system, https://www.orcam.com
+\bibitem{orcam} Orcam system, https://www.orcam.com. [2018-10-16].
 
-\bibitem{horus} Horus system, http://www.horus.tech
+\bibitem{horus} Horus system, http://www.horus.tech. [2018-10-16].
+
+\bibitem{Verilook} Neurotechnology, VeriLook SDK. \\ https://www.neurotechnology.com/verilook.html. [2018-10-16].
 

### 2018-10-20 bare_conf.tex
added hyperref, some small text changes.
text updates integrating feedback from Darius. Original feedback is available in bare_conf_Darius_feedback.pdf. bare_conf_Darius_feedback_integrated.pdf shows which comments are not yet integrated, integrated comments are removed from this pdf

@@
 %\boldmath
-This paper presents a high level architecture for computer vision-based system for partial compensation of lost or impaired human vision.
+This paper presents a high-level architecture for computer vision-based system for partial compensation of lost or impaired human vision.
 It combines standard smartphone device, external deep learning-based image processing infrastructure and audio/tactile user interface.
@@
 \begin{IEEEkeywords}
-Computer vision; Deep learning; Mobile application; Aid for blind and visually impaired; Audio feedback; Tactile feedback; Impaired human vision compensation; User-centered design.%
+computer vision; deep learning; mobile application; aid for blind and visually impaired; audio feedback; tactile feedback; impaired human vision compensation; user-centered design.%
 \end{IEEEkeywords}
@@
 Such systems often lack convenience and bring additional complexity into daily tasks, which visually impaired people currently manage by the help of a white cane.
-This project puts major emphasis on developing a tool, which seamlessly integrates with the hardware visually impaired persons already have on-hand and is used to (smartphone).
+This project puts major emphasis on developing a tool, which seamlessly integrates with the hardware visually impaired persons already have on-hand and are used to (smartphone).
 This paper describes a high level architecture of the technology aid for visually impaired people utilizing the latest achievements in the field of computer vision.
@@
 \item Functionality and key features of the solution addressing real-life scenarios of visually impaired persons;
-\item Technical feasibility, connecting user needs to the latest development in computer vision and assisted technologies;
-\item Interface between the visually impaired person and the assisted technology;
+\item Technical feasibility, connecting user needs to the latest development in computer vision and assistive technologies;
+\item Interface between the visually impaired person and the assistive technology;
 \item Appearance, usability and potential costs of the proposed product. 
 \end{enumerate}
-Design process included testing of the existing mobile phone app (Seeing AI) for assisting visually impaired people.
-Semi-structured tests were performed by the visually impaired participants accompanied by a researcher from the project group.
+Participatory design process included testing of assistive technologies for the blind and visually impaired people using widely available mobile phone apps like Seeing AI, BlindWays, Be my eyes, Aipoly Vision, TapTapSee, etc.
+%Design process included testing of the existing mobile phone apps (Seeing AI, BlindWays, Be My Eyes, Aipoly Vision, TapTapSee) for assisting visually impaired people. 
+Semi-structured tests were performed by visually impaired participants and researchers from the project group.
 Strengths and weaknesses of the existing solutions are reflected in the design of the proposed system.
+
+%Darius
+To have an overview of research progress on assistive technologies for the blind in the last ten years, a systematic literature review three major research databases (Medline, IEEE xplore and ACM DL) was conducted.
+we carried out  systemic review of research articles in databases like  Medline, IEEE xplore, ACM DL.
+It revealed increasing research interest in the field (84 related publications were identified, while 17 were characterized as highly relevant for this project).
+Systemic review of the relevant patents and patent applications worldwide was performed using online services of the following databases: EspaceNet, GooglePatents, USPTO, PatentScope, FreePatentsOnline.
+It revealed several main technological trends in the area of assistive technologies for the blind persons.
+Based on the above aforementioned methodical review approaches, some our insights are presented in the Results section.
 
@@
 Both open source (e.g.
-\cite{Tensorflow}) and state of the art commercial computer vision software (e.g.
+\cite{Tensorflow}) and state of the art commercial computer vision software libraries (e.g.
 \cite{Verilook}) may be applied implementing the suggested architecture.

### 2018-10-21 bare_conf.tex
text updates integrating feedback from Darius, 2nd iteration. Original feedback is available in bare_conf_Darius_feedback.pdf. bare_conf_Darius_feedback_integrated.pdf shows which comments are not yet integrated, integrated comments are removed from this pdf

@@
 \end{enumerate}
-Participatory design process included testing of assistive technologies for the blind and visually impaired people using widely available mobile phone apps like Seeing AI, BlindWays, Be my eyes, Aipoly Vision, TapTapSee, etc.
+Participatory design process included testing of assistive technologies for the blind and visually impaired people using widely available mobile phone apps like Seeing AI, BlindWays, Be My Eyes, Aipoly Vision, TapTapSee, etc.
 %Design process included testing of the existing mobile phone apps (Seeing AI, BlindWays, Be My Eyes, Aipoly Vision, TapTapSee) for assisting visually impaired people. 
@@
 
+%Andrius: If we leave this section in manuscript, we should probably have a section addressing the findings of the reviews in the Results section.
 %Darius
-To have an overview of research progress on assistive technologies for the blind in the last ten years, a systematic literature review three major research databases (Medline, IEEE xplore and ACM DL) was conducted.
-we carried out  systemic review of research articles in databases like  Medline, IEEE xplore, ACM DL.
+To have an overview of research progress on assistive technologies for the blind in the last ten years, a systematic literature review in three major research databases (Medline, IEEE xplore and ACM DL) was conducted.
 It revealed increasing research interest in the field (84 related publications were identified, while 17 were characterized as highly relevant for this project).
+%we carried out  systemic review of research articles in databases like  Medline, IEEE xplore, ACM DL.  
 Systemic review of the relevant patents and patent applications worldwide was performed using online services of the following databases: EspaceNet, GooglePatents, USPTO, PatentScope, FreePatentsOnline.
 It revealed several main technological trends in the area of assistive technologies for the blind persons.
-Based on the above aforementioned methodical review approaches, some our insights are presented in the Results section.
+Based on the aforementioned methodical reviews, some our insights are presented in the Results section.
 
@@
 Although more expensive than standard ones, bone conduction headphones do not block the ears and allow the user to perceive audio information from the surrounding environment and the system at the same time, which is essential for the visually impaired people.
-Some types of guidance information may be more efficiently perceived through tactile feedback device than audio channel.
+
+However, some types of guidance information may be more efficiently perceived through tactile feedback device than audio channel.
 For instance, indicating the direction of a detected object with a vibromotor on the corresponding area on the forehead belt, instead of providing audio description.
@@
 
-This paper outlined a high level architecture of a computer vision-based system, which may help to partially compensate impaired or lost human vision.
+This paper outlined a high-level architecture of a computer vision-based system, which may help to partially compensate impaired or lost human vision.
 The main advantages of therein suggested system are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via the Internet connection and present the output of the video processing to the user through a combined audio/tactile interface.
@@
 The proposed architecture is based on several assumptions, which may be characterized as limitations of the system.
-Technical feasibility of the solution is dependent on the availability of high bandwidth Internet connection ensuring access to high-power data processing components.
+For instance, technical feasibility of the solution is dependent on the availability of high bandwidth Internet connection ensuring access to high-power data processing components.
 Insufficient bandwidth may result in latency, which may not be tolerated by the users.
@@
 A combination of such components may be perceived as costly by the end users.
-More research is needed to demonstrate the benefits of the system in real-world scenarios.
+More research is needed to demonstrate the cost-benefit analysis of the system in real-world scenarios.
 

### 2018-10-26 bare_conf.tex
few sentences added to additionally connect Method and Results.

@@
 It revealed increasing research interest in the field (84 related publications were identified, while 17 were characterized as highly relevant for this project).
+In order to better understand the applicability of modern computer vision technologies, we also conducted comprehensive analysis of recent advantages in the topic.
 %we carried out  systemic review of research articles in databases like  Medline, IEEE xplore, ACM DL.  
@@
 
-User-centered design sessions with visually impaired persons provided substantial input for the design of the proposed system (Fig.~\ref{fig:schematics}).
+User-centered design sessions with visually impaired persons and analysis of aforementioned data sources provided substantial input for the design of the proposed system (Fig.~\ref{fig:schematics}).
 The process made it clear that understanding of the user needs was limited in the project team.
-Based on the results of the user-centered design process, we present the outline of the system for impaired human vision compensation.
+Based on the results of the user-centered design process and conducted publication and patent analysis, we present the outline of the system for impaired human vision compensation.
 
@@
 \label{sec:discussion}
-%Didzioji Discussion teksto dalis man labiau tinka prie Results/Conclusion.
-Gal galim padiskutioti daugiau apie Limitations, Future Implications, Lessons Learned ar pan...
-Cia galime savo siuloma sistema lyginti su anksciau publikuotais rezultatais.
-
-%In this article we outlined an idea of complex computer vision-based sensor architecture, which may help to partially compensate impaired or lost human sight.
 
@@
 The main advantages of therein suggested system are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via the Internet connection and present the output of the video processing to the user through a combined audio/tactile interface.
-
-% live video pakeiciau i  image or video, mano nuomone ne taip ambicingai skamba.
 
@@
 
-%our approach is advantageous, since it does not rely only on computational capacity of mobile handset.
-Such a combination of mobile interface and remote vision processor will be even more efficient in the future, with switching of the mobile networks to 5G.
-
 It is important to emphasize that the suggested system does not aim to replace the main travelling aid of visually impaired people - the white cane.
@@
 
-%Andrius: galima butu paminet limited knowledge on tactile interfaces for navigation purposes, placement, frequences, strenths, etc...
-
 Economical feasibility of the proposed solution may also be questioned.
@@
 
-%The developed head-mounted tactile device is developed for head position and orientation tracking and could capture an image in front of visually impaired people.
-The tactile device with integrated 3D deph camera is integrated with smartphone by bluetooth which could preprocess the labeled image features.
-The developed high quality self navigation system is based on the computer vision methods especially enhancing the capabilities to detect and classify objects (e.g bus station, street crossings, ) with their surrounding objects.
-The authors expect to increase the capabilies of potentially blind to secure navigate especially for the planed destination (e.g.
-"home-office").
-Work left (outdoor/indoor) etc.
-
-% conference papers do not normally have an appendix
-
-% use section* for acknowledgement
 \section*{Acknowledgment}

### 2018-10-27 bare_conf.tex
small text changes

@@
 %Darius
-To have an overview of research progress on assistive technologies for the blind in the last ten years, a systematic literature review in three major research databases (Medline, IEEE xplore and ACM DL) was conducted.
-It revealed increasing research interest in the field (84 related publications were identified, while 17 were characterized as highly relevant for this project).
-In order to better understand the applicability of modern computer vision technologies, we also conducted comprehensive analysis of recent advantages in the topic.
+To have an overview on research progress on assistive technologies for the blind in the last ten years, a systematic literature review in three major research databases (Medline, IEEE xplore and ACM DL) was conducted.
+It revealed increasing research interest in the field (84 related publications were identified, while 17 were characterized as highly relevant for this project) and provided better understanding of the state-of-the-art in applying computer vision technologies to address the needs of the blind.
+%In order to better understand the applicability of modern computer vision technologies, we also conducted comprehensive analysis of recent advantages in the topic.
 %we carried out  systemic review of research articles in databases like  Medline, IEEE xplore, ACM DL.  
-Systemic review of the relevant patents and patent applications worldwide was performed using online services of the following databases: EspaceNet, GooglePatents, USPTO, PatentScope, FreePatentsOnline.
+The review was extended to relevant patents and patent applications worldwide.
+The search was performed in the following databases: EspaceNet, GooglePatents, USPTO, PatentScope, FreePatentsOnline.
+It revealed several technological trends in the field of assistive technologies for the blind persons.
+%Systemic review of the relevant patents and patent applications worldwide was performed using online services of the following databases: EspaceNet, GooglePatents, USPTO, PatentScope, FreePatentsOnline.
 It revealed several main technological trends in the area of assistive technologies for the blind persons.
-Based on the aforementioned methodical reviews, some our insights are presented in the Results section.
+Based on the aforementioned methodical reviews, our insights are presented in the Results section.
 
@@
 
-User-centered design sessions with visually impaired persons and analysis of aforementioned data sources provided substantial input for the design of the proposed system (Fig.~\ref{fig:schematics}).
+User-centered design sessions with visually impaired persons and analysis of the aforementioned data sources provided substantial input for the design of the proposed system (Fig.~\ref{fig:schematics}).
 The process made it clear that understanding of the user needs was limited in the project team.
-Based on the results of the user-centered design process and conducted publication and patent analysis, we present the outline of the system for impaired human vision compensation.
+Based on the results of the user-centered design process, scientific publications and patent analysis, we present the outline of the system for impaired human vision compensation.
 

### 2018-10-31 bare_conf.tex
reference style fixes.

@@
 Lancet Glob Health.
-2017 Sep;5(9):e888-97.
+Vol.
+5(9):e888-97, 2017.
 
@@
 40, issue 6, pp.
-1510 - 1517.
+1510 - 1517, 2016.
 
 \bibitem{Tensorflow}  Abadi M., Agarwal A., Barham P., Brevdo E., Chen Z., Citro C., Corrado G., Davis A., Dean J., Devin M., et al.
-TensorFlow: Large-Scale Machine Learning on Heterogeneous Distributed Systems.
-2016.
-arXiv:1603.04467
+TensorFlow: Large-Scale Machine Learning on Heterogeneous Distributed Systems, arXiv:1603.04467, 2016.
 
-\bibitem{orcam} Orcam system, https://www.orcam.com. [2018-10-16].
+\bibitem{orcam} Orcam. MyEye 2.0. [Online]. Available from https://www.orcam.com 2018-10-16.
 
-\bibitem{horus} Horus system, http://www.horus.tech. [2018-10-16].
+\bibitem{horus} Horus. Horus system. [Online]. Available from http://www.horus.tech 2018-10-16.
 
-\bibitem{Verilook} Neurotechnology, VeriLook SDK. \\ https://www.neurotechnology.com/verilook.html. [2018-10-16].
+\bibitem{Verilook} Neurotechnology, VeriLook SDK. [Online]. Available from https://www.neurotechnology.com/verilook.html 2018-10-16.
 

### 2019-01-15 bare_conf.tex
some corrections according to review.

@@
 \usepackage{hyperref}
+\usepackage{etoolbox}
 
@@
 \pagestyle{empty}
+
 \begin{document}
@@
 
+\setlength{\parskip}{0.1em} % reduce spacings between paragraphs
+
 \begin{abstract}
@@
 However, computer vision is a rapidly evolving field; systems based on the aforementioned approaches become outdated in a relatively short time and often lack accuracy and reliability in real-world conditions in comparison to the state-of-the-art technologies.
-In this article we describe a system, which employs modern computer vision techniques for compensation of lost or impaired vision function in humans.
+In this article, we describe a system, which employs modern computer vision techniques for compensation of lost or impaired vision function in humans.
 Many of the previously proposed electronic aids for the blind count on highly specialized hardware, for instance smart glasses \cite{Zientara}, Microsoft Kinnect sensors \cite{Owayjan}, helmet-mounted photo sensors and cameras \cite{Dunai}.
@@
 This paper describes a high level architecture of the technology aid for visually impaired people utilizing the latest achievements in the field of computer vision.
+
+% corr start
+This paper is structured as follows.
+We start our presentation with Section~\ref{sec:method}, which describes the methodological foundations of this research.
+Section~\ref{sec:results} detalizes the architecture of the aforementioned system.
+Finally, Section~\ref{sec:discussion} summarizes and discusses the results of conducted analysis.
+% corr end
 
@@
 
-User-centered design sessions with visually impaired persons and analysis of the aforementioned data sources provided substantial input for the design of the proposed system (Fig.~\ref{fig:schematics}).
+User-centered design sessions with visually impaired persons and analysis of the aforementioned data sources provided substantial input for the design of the proposed system (Figure~\ref{fig:schematics}).
 The process made it clear that understanding of the user needs was limited in the project team.
@@
 
-\begin{thebibliography}{1}
+\begin{thebibliography}{99}
 
@@
 
-\bibitem{Carroll} Carroll, J. M., Rosson, M. B. Participatory design in community informatics. Des. Stud., vol. 28, no. 3, pp. 243-261, May 2007.
+\bibitem{Carroll} \noindent Carroll, J. M., Rosson, M. B. Participatory design in community informatics. Des. Stud., vol. 28, no. 3, pp. 243-261, May 2007.
 

### 2019-01-15 bare_conf.tex
more fixes according to review.

@@
 The suggested architecture may be used as a basis for developing computer vision-based tools for visually impaired individuals.
-%In this short article we describe and discuss high level architecture of computer vision-based system for partial compensation of lost or impaired human vision.
-Combining standard smartphone device, external deep learning-based live video processoing infrastructure and audio/tactile user interface into compact visual perception compensation device .
 \end{abstract}
@@
 More than $250$ million people worldwide have moderate to severe vision impairment, while ($\approx 36$ million are blind) \cite{Bourne}.
-During the past decades significant effort was devoted to develop computer vision and other sensor based aids (e.g.
-\cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara}) for helping the blind and visually impaired users to perceive the surrounding world better.
+During the past decades significant effort was devoted to develop computer vision and other sensor based aids (e.g., \cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara}) for helping the blind and visually impaired users to perceive the surrounding world better.
 However, computer vision is a rapidly evolving field; systems based on the aforementioned approaches become outdated in a relatively short time and often lack accuracy and reliability in real-world conditions in comparison to the state-of-the-art technologies.
@@
 We start our presentation with Section~\ref{sec:method}, which describes the methodological foundations of this research.
-Section~\ref{sec:results} detalizes the architecture of the aforementioned system.
-Finally, Section~\ref{sec:discussion} summarizes and discusses the results of conducted analysis.
+Section~\ref{sec:results} focuses on the architecture of the suggested vision compensation system.
+Finally, Section~\ref{sec:discussion} summarizes and discusses the results of the conducted analysis.
 % corr end
@@
 Two visually impaired persons participated in discussion and focus group meetings together with the project team to identify the key properties of the solution.
-During the six discussion sessions major attention was paid to:
+During the six discussion sessions, major attention was paid to:
 \begin{enumerate}
@@
 
-The key part of the proposed system is a smartphone device, connecting user interface (UI) and data processing components into a well-functioning ecosystem.
+The key part of the proposed system is a smartphone device, connecting User interface (UI) and data processing components into a well-functioning ecosystem.
 Smartphone was selected due to its high availability and capability to perform required computations or forward visual information for processing to the external server via the Internet.
@@
 % User interface
-UI consists of a wearable forehead belt, integrating RGB and depth cameras, inertial measurement unit (IMU), tactile feedback device and bone conduction headphones.
+UI consists of a wearable forehead belt, integrating RGB and depth cameras, Inertial measurement unit (IMU), tactile feedback device and bone conduction headphones.
 Although more expensive than standard ones, bone conduction headphones do not block the ears and allow the user to perceive audio information from the surrounding environment and the system at the same time, which is essential for the visually impaired people.
@@
 
-%The tactile feedback may improve the quality of users perception (e.g. by ). UI can interface smartphone component via USB or Wifi connection.
-
 % External vision processor
 %visus sutrumpinimus reikia pirma parasyt pilnai, pvz Neural Network (NN)
-Although modern high-end smartphones are powerful computational devices, many computer vision algorithms  require hardware of significantly higher processing power (e.g.
-a server equipped with a high-end graphics processing unit (GPU)).
+Although modern high-end smartphones are powerful computational devices, many computer vision algorithms  require hardware of significantly higher processing power (e.g., a server equipped with a high-end Graphics processing unit (GPU)).
 Therefore, an external server is used for live vision data processing.
-In our design we envision a computational server hosting a set of computer vision algorithms implemented and exposed via web services: faster regions with convolutional neural network features (faster R-CNN) object detector \cite{Ren}, trained to detect important objects, convolutional and recurrent neural network-based (CNN and RNN) scene descriptor \cite{Liu}, which provides textual annotation of a given RGB image, place recognition \cite{Ohn-Bar}, face detection and recognition \cite{Amos}, obstacle detection \cite{Laina}, action recognition \cite{Valor}, among others.
+In our design we envision a computational server hosting a set of computer vision algorithms implemented and exposed via web services: faster Regions with convolutional neural network features (faster R-CNN) object detector \cite{Ren}, trained to detect important objects, convolutional and recurrent neural network-based (CNN and RNN) scene descriptor \cite{Liu}, which provides textual annotation of a given RGB image, place recognition \cite{Ohn-Bar}, face detection and recognition \cite{Amos}, obstacle detection \cite{Laina}, action recognition \cite{Valor}, among others.
 After video analysis is completed on the server side, results are transmitted back to the smartphone component and represented to the user through the aforementioned UI.
@@
 The user interacts with the system through gestures, voice commands or specifically designed user interface on the smartphone.
-User input is required for selecting operation mode of the system, i.e.
-switching between optical character recognition (OCR), currency recognition, object detection, navigation aid and other available functions.
+User input is required for selecting operation mode of the system, i.e., switching between Optical character recognition (OCR), currency recognition, object detection, navigation aid and other available functions.
 
@@
 Reliable object detection, direction and approximate distance to an obstacle were highlighted as the main requirements.
-To our surprise, only 5-8 distinctive object classes (for instance, buss stop, pedestrian crossing, doors, stairs, etc) were of major importance while navigating.
+To our surprise, only 5-8 distinctive object classes (for instance, buss stop, pedestrian crossing, doors, stairs, etc.) were of major importance while navigating.
 Additional information, such as type of a passing car, blossoming flowers in the park or a person riding a bicycle was considered as overwhelming and distractive.
@@
 Computer vision technology is under rapid development and during the last years made a major breakthrough in performance and efficiency.
-Deep learning neural networks, which are de facto standard in modern image/video processing in many real-world problems allow to achieve accuracies, similar to that of human decision (e.g.
-face recognition \cite{Amos}, object detection \cite{Ren}, among others).
-These models are now well supported by software libraries (e.g.
-\cite{Tensorflow}) and dedicated processing hardware is built-in even in relatively low-power computational devices, such as smartphones.
+Deep learning neural networks, which are de facto standard in modern image/video processing in many real-world problems allow to achieve accuracies, similar to that of human decision (e.g., face recognition \cite{Amos}, object detection \cite{Ren}, among others).
+These models are now well supported by software libraries (e.g., \cite{Tensorflow}) and dedicated processing hardware is built-in even in relatively low-power computational devices, such as smartphones.
 These devices are also equipped with 4G Internet connectivity and sufficient computational power to perform partial or in certain cases even full vision data processing locally.
@@
 
-Both open source (e.g.
-\cite{Tensorflow}) and state of the art commercial computer vision software libraries (e.g.
-\cite{Verilook}) may be applied implementing the suggested architecture.
+Both open source (e.g., \cite{Tensorflow}) and state of the art commercial computer vision software libraries (e.g., \cite{Verilook}) may be applied implementing the suggested architecture.
 Moreover, detalization and specification of the suggested system's hardware components following open hardware approach - by providing open repository with the detailed list of electronics components, schematics, and 3D models of mechanical parts, could provide a solid basis for semi-standard reference platform for the researchers in the field.
@@
 This functionality corresponds with the main requirement for electronic travelling aids highlighted by the end users - direction and distance estimation to a selected object.
-The proposed hardware architecture can be used as basis for various computer vision-based software modules, aiming to assist visually impaired users in daily activities (e.g.
-outdoor/indoor navigation, object/face recognition, obstacle detection, etc.).
+The proposed hardware architecture can be used as basis for various computer vision-based software modules, aiming to assist visually impaired users in daily activities (e.g., outdoor/indoor navigation, object/face recognition, obstacle detection, etc.).
 

### 2019-01-16 bare_conf.tex
fixes.

@@
 \usepackage{etoolbox}
+\usepackage[dvipsnames]{xcolor}
 
@@
 More than $250$ million people worldwide have moderate to severe vision impairment, while ($\approx 36$ million are blind) \cite{Bourne}.
-During the past decades significant effort was devoted to develop computer vision and other sensor based aids (e.g., \cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara}) for helping the blind and visually impaired users to perceive the surrounding world better.
+During the past decades significant effort was devoted to develop computer vision and other sensor based aids (e.g., \cite{Caraiman}-\cite{Zientara}) for helping the blind and visually impaired users to perceive the surrounding world better.
 However, computer vision is a rapidly evolving field; systems based on the aforementioned approaches become outdated in a relatively short time and often lack accuracy and reliability in real-world conditions in comparison to the state-of-the-art technologies.
@@
 
-% corr start
-This paper is structured as follows.
-We start our presentation with Section~\ref{sec:method}, which describes the methodological foundations of this research.
-Section~\ref{sec:results} focuses on the architecture of the suggested vision compensation system.
-Finally, Section~\ref{sec:discussion} summarizes and discusses the results of the conducted analysis.
+\textcolor{red}{We start our presentation with Section~\ref{sec:method}, describing the methodological foundations of this research.
+Section~\ref{sec:results} focuses on the architecture of the suggested human vision compensation system.
+Finally, Section~\ref{sec:discussion} summarizes and discusses the results of the conducted analysis.}
 % corr end
@@
 
-Following the principles of the participatory design \cite{Kensing}, \cite{Carroll} we included the end-users into the design process of the system.
+Following the principles of the participatory design \cite{Kensing}\cite{Carroll} we included the end-users into the design process of the system.
 Two visually impaired persons participated in discussion and focus group meetings together with the project team to identify the key properties of the solution.
@@
 We are proposing a combination of audio and tactile feedback, which may improve the interaction between the assistive technology and the user.
-Similar interfaces were suggested by research communities earlier \cite{Zientara}, \cite{Poggi}, however, existing knowledge on user preferences and evaluation of various options of tactile feedback (types of actuators, placement on the body, frequencies, strength, etc.) is limited.
+Similar interfaces were suggested by research communities earlier \cite{Poggi}\cite{Zientara}, however, existing knowledge on user preferences and evaluation of various options of tactile feedback (types of actuators, placement on the body, frequencies, strength, etc.) is limited.
 
@@
 
-Similar functionality has been previously addressed by research communities \cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara} and industry \cite{orcam}, \cite{horus}.
+Similar functionality has been previously addressed by research communities \cite{Caraiman}-\cite{Zientara} and industry \cite{orcam}\cite{horus}.
 The main difference between the aforementioned commercial solutions and the proposed system is the ability to utilize external resources for computationally intensive image or video processing tasks.
@@
 Vol.
-5(9):e888-97, 2017.
+5(9), pp.
+888-897, 2017.
 

### 2019-01-16 bare_conf.tex
some small fixes.

@@
 
-\textcolor{red}{We start our presentation with Section~\ref{sec:method}, describing the methodological foundations of this research.
+\textcolor{red}{We begin our presentation with Section~\ref{sec:method}, describing the methodological foundations of this research.
 Section~\ref{sec:results} focuses on the architecture of the suggested human vision compensation system.
@@
 Therefore, an external server is used for live vision data processing.
-In our design we envision a computational server hosting a set of computer vision algorithms implemented and exposed via web services: faster Regions with convolutional neural network features (faster R-CNN) object detector \cite{Ren}, trained to detect important objects, convolutional and recurrent neural network-based (CNN and RNN) scene descriptor \cite{Liu}, which provides textual annotation of a given RGB image, place recognition \cite{Ohn-Bar}, face detection and recognition \cite{Amos}, obstacle detection \cite{Laina}, action recognition \cite{Valor}, among others.
+In our design we envision a computational server hosting a set of computer vision algorithms implemented and exposed via web services: faster Regions with convolutional neural network features (faster R-CNN) object detector \cite{Ren}, trained to detect important objects, Convolutional neural network (CNN) and Recurrent neural network-based (RNN) scene descriptor \cite{Liu}, which provides textual annotation of a given RGB image, place recognition \cite{Ohn-Bar}, face detection and recognition \cite{Amos}, obstacle detection \cite{Laina}, action recognition \cite{Valor}, among others.
 After video analysis is completed on the server side, results are transmitted back to the smartphone component and represented to the user through the aforementioned UI.

### 2019-01-16 bare_conf.tex
some changes according to reviews.

@@
 Finally, Section~\ref{sec:discussion} summarizes and discusses the results of the conducted analysis.}
-% corr end
 
@@
 For instance, indicating the direction of a detected object with a vibromotor on the corresponding area on the forehead belt, instead of providing audio description.
-More research is needed to clarity how various types of guidance information should be represented to the user in the most convenient and efficient way.
-USB and Wifi data links can be used for bidirectional data transmission between UI and smartphone component.
+More research is needed to clarity how various types of guidance information should be represented to the user in the most convenient and efficient way \textcolor{red}{: for example, adsd .} USB and Wifi data links can be used for bidirectional data transmission between UI and smartphone component.
 
@@
 On the other side, increasing computational capacity of smartphones also may allow to conduct more advanced image or video processing locally.
-Combined audio/tactile interface may also be more convenient for the users, allowing to provide feedback in a more efficient way than using tactile or audio interfaces separately.
+\textcolor{red}{Although not always technically possible for more complex algorithm systems, local  implementations are especially important in areas, where wireless Internet connectivity is not available, since they allow to preserve at least partial functionality of the system.} Combined audio/tactile interface may also be more convenient for the users, allowing to provide feedback in a more efficient way than using tactile or audio interfaces separately.
 

### 2019-01-16 bare_conf.tex
Update bare_conf.tex
the affiliation part was changed (the two working places are not changed)
Please, provide an example of this issue

@@
 % 
-\author{\IEEEauthorblockN{Povilas Daniu\v{s}is\IEEEauthorrefmark{1},
-Andrius Budrionis\IEEEauthorrefmark{1}\IEEEauthorrefmark{2},
-Audrius Indriulionis\IEEEauthorrefmark{1}\IEEEauthorrefmark{3} and 
-Darius Plikynas\IEEEauthorrefmark{1}}
-\IEEEauthorblockA{\IEEEauthorrefmark{1}Vilnius Gediminas Technical University,\\
-Vilnius, Lithuania.
+%\author{\IEEEauthorblockN{Povilas Daniu\v{s}is\IEEEauthorrefmark{1},
+%Andrius Budrionis\IEEEauthorrefmark{1}\IEEEauthorrefmark{2},
+%Audrius Indriulionis\IEEEauthorrefmark{1}\IEEEauthorrefmark{3} and 
+%Darius Plikynas\IEEEauthorrefmark{1}}
+%\IEEEauthorblockA{\IEEEauthorrefmark{1}Vilnius Gediminas Technical University,\\
+%Vilnius, Lithuania.
+%}
+%\IEEEauthorblockA{\IEEEauthorrefmark{2}Norwegian Centre for E-health Research, University Hospital of North Norway,\\
+%Troms\o, Norway.}
+%\IEEEauthorblockA{\IEEEauthorrefmark{3}Nature Research Center,\\ 
+%Vilnius, Lithuania.
+%}}
+
+\author{
+\begin{tabular}[t]{c@{\extracolsep{2em}}c} 
+Povilas Daniu\v{s}is & Audrius Indriulionis \\
+{\scriptsize Department of Business Technologies  and Entrepreneurship }& {\scriptsize Department of  of Business Technologies and Entrepreneurship}\\ 
+{\scriptsize Vilnius Gediminas Technical University} & {\scriptsize Vilnius Gediminas Technical University}\\
+{\scriptsize Vilnius, Lithuania} & {\scriptsize Vilnius, Lithuania}\\
+{\scriptsize email: povilas.daniusis@vgtu.lt} & {\scriptsize email: audrius.indriulionis@vgtu.lt} \\
+& \\
+Andrius Budrionis & Darius Plikynas \\
+{\scriptsize Norwegian Centre for E-health Research} & {\scriptsize Department of Business Technologies and Entrepreneurship}\\ 
+{\scriptsize University Hospital of North Norway} & {\scriptsize Vilnius Gediminas Technical University}\\
+{\scriptsize Troms\o, Norway} & {\scriptsize Vilnius, Lithuania}\\
+{\scriptsize email: andrius.budrionis@vgtu.lt} & {\scriptsize email: darius.plikynas@vgtu.lt} \\
+\end{tabular}
 }
-\IEEEauthorblockA{\IEEEauthorrefmark{2}Norwegian Centre for E-health Research, University Hospital of North Norway,\\
-Troms\o, Norway.}
-\IEEEauthorblockA{\IEEEauthorrefmark{3}Nature Research Center,\\ 
-Vilnius, Lithuania.
-}}
 

### 2019-01-16 bare_conf.tex
Update bare_conf.tex

@@
 \begin{tabular}[t]{c@{\extracolsep{2em}}c} 
-Povilas Daniu\v{s}is & Audrius Indriulionis \\
-{\scriptsize Department of Business Technologies  and Entrepreneurship }& {\scriptsize Department of  of Business Technologies and Entrepreneurship}\\ 
+Povilas Daniu\v{s}is & Andrius Budrionis \\
+{\scriptsize Department of Business Technologies  and Entrepreneurship }& {\scriptsize Norwegian Centre for E-health Research}\\ 
+{\scriptsize Vilnius Gediminas Technical University} & {\scriptsize University Hospital of North Norway}\\
+{\scriptsize Vilnius, Lithuania} & {\scriptsize Troms\o, Norway}\\
+{\scriptsize email: povilas.daniusis@vgtu.lt} & {\scriptsize email: andrius.budrionis@vgtu.lt} \\
+& \\
+Audrius Indriulionis & Darius Plikynas \\
+{\scriptsize Department of Business Technologies and Entrepreneurship} & {\scriptsize Department of Business Technologies and Entrepreneurship}\\ 
 {\scriptsize Vilnius Gediminas Technical University} & {\scriptsize Vilnius Gediminas Technical University}\\
-{\scriptsize Vilnius, Lithuania} & {\scriptsize Vilnius, Lithuania}\\
-{\scriptsize email: povilas.daniusis@vgtu.lt} & {\scriptsize email: audrius.indriulionis@vgtu.lt} \\
-& \\
-Andrius Budrionis & Darius Plikynas \\
-{\scriptsize Norwegian Centre for E-health Research} & {\scriptsize Department of Business Technologies and Entrepreneurship}\\ 
-{\scriptsize University Hospital of North Norway} & {\scriptsize Vilnius Gediminas Technical University}\\
-{\scriptsize Troms\o, Norway} & {\scriptsize Vilnius, Lithuania}\\
-{\scriptsize email: andrius.budrionis@vgtu.lt} & {\scriptsize email: darius.plikynas@vgtu.lt} \\
+{\scriptsize Vilnius, Lithuania}} & {\scriptsize Vilnius, Lithuania}\\
+{\scriptsize email: audrius.indriulionis@vgtu.lt} & {\scriptsize email: darius.plikynas@vgtu.lt} \\
 \end{tabular}

### 2019-01-16 bare_conf.tex
Update bare_conf.tex

@@
 {\scriptsize Vilnius Gediminas Technical University} & {\scriptsize Vilnius Gediminas Technical University}\\
-{\scriptsize Vilnius, Lithuania}} & {\scriptsize Vilnius, Lithuania}\\
+{\scriptsize Vilnius, Lithuania} & {\scriptsize Vilnius, Lithuania}\\
 {\scriptsize email: audrius.indriulionis@vgtu.lt} & {\scriptsize email: darius.plikynas@vgtu.lt} \\

### 2019-01-18 bare_conf.tex
Update bare_conf.tex
The 2 versions of affilations are added, PDF file was not generated

@@
 
-\author{
-\begin{tabular}[t]{c@{\extracolsep{2em}}c} 
-Povilas Daniu\v{s}is & Andrius Budrionis \\
-{\scriptsize Department of Business Technologies  and Entrepreneurship }& {\scriptsize Norwegian Centre for E-health Research}\\ 
-{\scriptsize Vilnius Gediminas Technical University} & {\scriptsize University Hospital of North Norway}\\
-{\scriptsize Vilnius, Lithuania} & {\scriptsize Troms\o, Norway}\\
-{\scriptsize email: povilas.daniusis@vgtu.lt} & {\scriptsize email: andrius.budrionis@vgtu.lt} \\
-& \\
-Audrius Indriulionis & Darius Plikynas \\
-{\scriptsize Department of Business Technologies and Entrepreneurship} & {\scriptsize Department of Business Technologies and Entrepreneurship}\\ 
-{\scriptsize Vilnius Gediminas Technical University} & {\scriptsize Vilnius Gediminas Technical University}\\
-{\scriptsize Vilnius, Lithuania} & {\scriptsize Vilnius, Lithuania}\\
-{\scriptsize email: audrius.indriulionis@vgtu.lt} & {\scriptsize email: darius.plikynas@vgtu.lt} \\
-\end{tabular}
-}
+% first version of affilation
+%\author{\IEEEauthorblockN{Povilas Daniu\v{s}is\IEEEauthorrefmark{1},
+%Andrius Budrionis\IEEEauthorrefmark{1}\IEEEauthorrefmark{2},
+%Audrius Indriulionis\IEEEauthorrefmark{1}\IEEEauthorrefmark{3} and 
+%Darius Plikynas\IEEEauthorrefmark{1}}
+%\IEEEauthorblockA{\IEEEauthorrefmark{1} Department of Business Technologies  and Entrepreneurship\\ Vilnius Gediminas Technical University\\
+%Vilnius, Lithuania}
+%\IEEEauthorblockA{\IEEEauthorrefmark{2}Norwegian Centre for E-health Research\\ University %Hospital of North Norway\\
+%Troms\o, Norway}
+%\IEEEauthorblockA{\IEEEauthorrefmark{3} Laboratory of Quaternary Research\\ Nature Research Centre %\\ Vilnius, Lithuania\\
+%Email: \IEEEauthorrefmark{1} {povilas.daniusis, andrius.budrionis, audrius.indriulionis, %darius.plikynas} @vgtu.lt}}
+
+%%%%\IEEEauthorrefmark{2}andrius.budrionis@vgtu.lt,
+%%%%\IEEEauthorrefmark{3}audrius.indriulionis@vgtu.lt,
+%%%\\\IEEEauthorrefmark{4}darius.plikynas@vgtu.lt}}
+% second version of affilation
+\author[1]{Povilas Daniu\v{s} Darius Plikynas}
+\author[1,2]{Andrius Budrionis}
+\author[1,3]{ Audrius Indriulionis}
+\affil[1]{Department of Business Technologies  and Entrepreneurship 
+\authorcr Gediminas Technical University 
+\authorcr Vilnius, Lithuania
+\authorcr Email: {\tt \{povilas.daniusis, darius.plikynas\}@vgtu.lt}\vspace{1.5ex}}
+\affil[2]{Norwegian Centre for E-health Research 
+\authorcr University Hospital of North Norway
+\authorcr Troms\o, Norway
+ \authorcr Email: {\tt andrius.budrionis@ehealthresearch.no} \vspace{1.5ex}} 
+\affil[3]{Laboratory of Quaternary Research 
+\authorcr  Nature Research Centre
+\authorcr Vilnius, Lithuania
+\authorcr Email: {\tt audrius.indriulionis@gmail.com}}
 

### 2019-01-20 bare_conf.tex
Added missing packages.
fixes according to review remarks.

@@
 \usepackage[dvipsnames]{xcolor}
+\usepackage{authblk}
+\usepackage{blindtext}
 
@@
 % second version of affilation
-\author[1]{Povilas Daniu\v{s} Darius Plikynas}
+\author[1]{Povilas Daniu\v{s}is}
 \author[1,2]{Andrius Budrionis}
 \author[1,3]{ Audrius Indriulionis}
+\author[1]{ Darius Plikynas}
 \affil[1]{Department of Business Technologies  and Entrepreneurship 
@@
 For instance, indicating the direction of a detected object with a vibromotor on the corresponding area on the forehead belt, instead of providing audio description.
-More research is needed to clarity how various types of guidance information should be represented to the user in the most convenient and efficient way \textcolor{red}{: for example, adsd .} USB and Wifi data links can be used for bidirectional data transmission between UI and smartphone component.
+More research is needed to clarity how various types of guidance information should be represented to the user in the most convenient and efficient way \textcolor{red}{(e.g.
+presentation order of object detections may be configured by the system's user according to subjective importance of particular object classes or other personalized criteria).} USB and Wifi data links can be used for bidirectional data transmission between UI and smartphone component.
 
@@
 Smart Assistive Navigation System for Blind and Visually Impaired Individuals.
-2015 International Conference on Advances in Biomedical Engineering (ICABME), 2015.
+2015 International Conference on Advances in Biomedical Engineering (ICABME), pp.
+162-165, 2015.
 
@@
 Obstacle detectors for visually impaired people.
-2014 International Conference on Optimization of Electrical and Electronic Equipment (OPTIM), 2014.
+2014 International Conference on Optimization of Electrical and Electronic Equipment (OPTIM),  pp.
+809-816, 2014.
 

### 2019-01-20 bare_conf.tex
Bibliography fixes according to reviews.

@@
 
-\bibitem{Bourne} Bourne RRA, Flaxman SR, Braithwaite T, Cicinelli MV, Das A, Jonas JB, et al.; Vision Loss Expert Group.
+\bibitem{Bourne} R.
+R.
+A.
+Bourne et al.
+Vision Loss Expert Group.
 Magnitude, temporal trends, and projections of the global prevalence of blindness and distance and near vision impairment: a systematic review and meta-analysis.
@@
 
-\bibitem{Caraiman} Caraiman, S., Morar, A., Owczarek, M.,Burlacu, A., Rzeszotarski, D., Botezatu, N., Herghelegiu, P., Moldoveanu, F., Strumillo, P., Moldoveanu, A.
-Computer Vision for the Visually Impaired: the Sound of Vision System.
-IEEE International Conference on Computer Vision Workshops, pp.
-1480-1489, 2017.
+\bibitem{Caraiman} S. Caraiman et al. A. Computer Vision for the Visually Impaired: the Sound of Vision System. IEEE International Conference on Computer Vision Workshops, pp. 1480-1489, 2017.
 
-\bibitem{Csapo} Csap\'{o}, A., Wers\'{e}nyi, G., Nagy, H., Stockman, T.
+\bibitem{Csapo} A.
+Csap\'{o}, G.
+Wers\'{e}nyi, H.
+Nagy, and T.
+A.
+Stockman.
 A survey of assistive technologies and applications for blind users on mobile platforms: a review and foundation for research.
@@
 
-\bibitem{Poggi} Poggi, M., Mattoccia, S.
+\bibitem{Poggi} M.
+Poggi and S.
+Mattoccia.
 A wearable mobility aid for the visually impaired based on embedded 3d vision and deep learning.
@@
 
-\bibitem{Zientara} Zientara, P.,A., Lee, S., Smith, G., H., Brenner, R., Itti, L., Rosson M., B., Carroll, J., M., Irick K., M., Narayanan, V.
-Third Eye: A shopping assistant for the visually impaired.
-Computer Vol.
-50, Issue 2, pp.
-16-24, 2017.
+\bibitem{Zientara} P. A. Zientara at al. Third Eye: A shopping assistant for the visually impaired. Computer Vol. 50, Issue 2, pp. 16-24, 2017.
 
-\bibitem{Owayjan} Owayjan, M., Hayek, A., Nassrallah, H., Eldor, M.
+\bibitem{Owayjan} M.
+Owayjan, A.
+Hayek, H.
+Nassrallah, and M.
+Eldor.
 Smart Assistive Navigation System for Blind and Visually Impaired Individuals.
@@
 
-\bibitem{Dunai} Dunai, L.
-D., Lengua, I.
-L., Tortajada, I., Brusola Simon, F.
+\bibitem{Dunai} L.
+D.
+Dunai, I.
+L.
+Lengua, I.
+Tortajada, and F.
+B.
+Simon.
 Obstacle detectors for visually impaired people.
@@
 
-\bibitem{Kensing} Kensing, F., Simonsen, J., and B\o dker, K. MUST: A Method for Participatory Design. Hum-Comput Interact, vol. 13, no. 2, pp. 167-198, Jun. 1998.
+\bibitem{Kensing} F. Kensing, J. Simonsen, and K. B\o dker. MUST: A Method for Participatory Design. Human Computer Interaction, vol. 13, no. 2, pp. 167-198, Jun. 1998.
 
-\bibitem{Carroll} \noindent Carroll, J. M., Rosson, M. B. Participatory design in community informatics. Des. Stud., vol. 28, no. 3, pp. 243-261, May 2007.
+\bibitem{Carroll} J. M. Carroll and M. B. Rosson. Participatory design in community informatics. Des. Stud., vol. 28, no. 3, pp. 243-261, May 2007.
 
-\bibitem{Ren} Ren, Sh., He, K., Girshick, R., and Sun, J.
+\bibitem{Ren} Sh.
+Ren, K.
+He, R.
+Girshick, and J.
+Sun.
 Faster R-CNN: Towards real-time object detection with region proposal networks.
@@
 
-\bibitem{Liu} Liu, Ch., Mao, J., Sha, F., Yuille, A. Attention Correctness in Neural Image Captioning. Proceedings of the Thirty-First AAAI Conference on Artificial Intelligence, pp. 4176-4182, 2017.
+\bibitem{Liu} Ch. Liu, J. Mao, F. Sha, and A. Yuille. Attention Correctness in Neural Image Captioning. Proceedings of the Thirty-First AAAI Conference on Artificial Intelligence, pp. 4176-4182, 2017.
 
-\bibitem{Ohn-Bar}  Ohn-Bar, E., Kitani, K., Asakawa, Ch. Personalized Dynamics Models for Adaptive Assistive Navigation Interfaces. arXiv:1804.04118, [cs.LG], 2018.
+\bibitem{Ohn-Bar} E. Ohn-Bar, K. Kitani, and Ch. Asakawa. Personalized Dynamics Models for Adaptive Assistive Navigation Interfaces. arXiv:1804.04118, [cs.LG], 2018.
 
-\bibitem{Amos} Amos, B., Ludwiczuk, B., and Satyanarayanan, M. Openface:
+\bibitem{Amos} B. Amos, B. Ludwiczuk, and M. Satyanarayanan. Openface:
 A general-purpose face recognition library with mobile applications. Technical report, CMU-CS-16-118, CMU School of Computer Science, 2016.
 
-\bibitem{Laina} Laina, I., Rupprecht, C., Belagiannis, V., Tombari, F., Navab, N.
+\bibitem{Laina} I.
+Laina, C.
+Rupprecht, V.
+Belagiannis, F.
+Tombari, and N.
+Navab.
 Deeper depth prediction with fully convolutional residual networks.
@@
 
-\bibitem{Valor} Varol, G., Laptev, I., Schmid, C.
+%-------------------
+
+\bibitem{Valor} G.
+Varol, I.
+Laptev, and C.
+Schmid.
 Long-Term Temporal Convolutions for Action Recognition.
@@
 
-\bibitem{Tensorflow}  Abadi M., Agarwal A., Barham P., Brevdo E., Chen Z., Citro C., Corrado G., Davis A., Dean J., Devin M., et al.
-TensorFlow: Large-Scale Machine Learning on Heterogeneous Distributed Systems, arXiv:1603.04467, 2016.
+\bibitem{Tensorflow} M. Abadi et al. TensorFlow: Large-Scale Machine Learning on Heterogeneous Distributed Systems, arXiv:1603.04467, 2016.
 
-\bibitem{orcam} Orcam. MyEye 2.0. [Online]. Available from https://www.orcam.com 2018-10-16.
+%-------------------
 
-\bibitem{horus} Horus. Horus system. [Online]. Available from http://www.horus.tech 2018-10-16.
+\bibitem{orcam} Orcam. MyEye 2.0. [Online]. Available from https://www.orcam.com [retrieved: 1 2019].
 
-\bibitem{Verilook} Neurotechnology, VeriLook SDK. [Online]. Available from https://www.neurotechnology.com/verilook.html 2018-10-16.
+\bibitem{horus} Horus. Horus system. [Online]. Available from http://www.horus.tech [retrieved: 1 2019].
+
+\bibitem{Verilook} Neurotechnology, VeriLook SDK. [Online]. Available from https://www.neurotechnology.com/verilook.html [retrieved: 1 2019].
 

### 2019-01-20 bare_conf.tex
some language corrections

@@
 %\boldmath
-This paper presents a high-level architecture for computer vision-based system for partial compensation of lost or impaired human vision.
+This paper presents a high-level architecture of a computer vision-based system for partial compensation of lost or impaired human vision.
 It combines standard smartphone device, external deep learning-based image processing infrastructure and audio/tactile user interface.
-The proposed architecture is based on  input from user-centered design process, involving end users into system development.
-The paper discusses user needs and expectations towards electronic travelling aids for the blind and highlights limitations of the existing solutions.
+The proposed architecture is based on input from user-centered design process, involving end-users into system development.
+The paper discusses user needs and expectations for electronic travelling aids for the blind and highlights limitations of the existing solutions.
 The suggested architecture may be used as a basis for developing computer vision-based tools for visually impaired individuals.
@@
 More than $250$ million people worldwide have moderate to severe vision impairment, while ($\approx 36$ million are blind) \cite{Bourne}.
-During the past decades significant effort was devoted to develop computer vision and other sensor based aids (e.g., \cite{Caraiman}-\cite{Zientara}) for helping the blind and visually impaired users to perceive the surrounding world better.
+During the past decades significant effort was devoted to develop computer vision and other sensor-based aids (e.g., \cite{Caraiman}-\cite{Zientara}) for helping the blind and visually impaired users to perceive the surrounding world better.
 However, computer vision is a rapidly evolving field; systems based on the aforementioned approaches become outdated in a relatively short time and often lack accuracy and reliability in real-world conditions in comparison to the state-of-the-art technologies.
@@
 
-Following the principles of the participatory design \cite{Kensing}\cite{Carroll} we included the end-users into the design process of the system.
+Following the principles of the participatory design \cite{Kensing}\cite{Carroll} we included end-users into system design process.
 Two visually impaired persons participated in discussion and focus group meetings together with the project team to identify the key properties of the solution.
@@
 %Darius
-To have an overview on research progress on assistive technologies for the blind in the last ten years, a systematic literature review in three major research databases (Medline, IEEE xplore and ACM DL) was conducted.
+To have an overview on research progress on assistive technologies for the blind during the last ten years, a systematic literature review in three major research databases (Medline, IEEE xplore and ACM DL) was conducted.
 It revealed increasing research interest in the field (84 related publications were identified, while 17 were characterized as highly relevant for this project) and provided better understanding of the state-of-the-art in applying computer vision technologies to address the needs of the blind.
@@
 It revealed several main technological trends in the area of assistive technologies for the blind persons.
-Based on the aforementioned methodical reviews, our insights are presented in the Results section.
+Based on the aforementioned reviews, our insights are presented in the Results section.
 
@@
 For instance, indicating the direction of a detected object with a vibromotor on the corresponding area on the forehead belt, instead of providing audio description.
-More research is needed to clarity how various types of guidance information should be represented to the user in the most convenient and efficient way \textcolor{red}{(e.g.
-presentation order of object detections may be configured by the system's user according to subjective importance of particular object classes or other personalized criteria).} USB and Wifi data links can be used for bidirectional data transmission between UI and smartphone component.
+More research is needed to clarify how various types of guidance information should be represented to the user in the most convenient and efficient way \textcolor{red}{ For instance, the detected objects could be presented to the user in a configurable order, based on the subjective importance of particular object classes or other personalized criteria.} USB and Wifi data links can be used for bidirectional data transmission between UI and smartphone component.
 
@@
 %visus sutrumpinimus reikia pirma parasyt pilnai, pvz Neural Network (NN)
-Although modern high-end smartphones are powerful computational devices, many computer vision algorithms  require hardware of significantly higher processing power (e.g., a server equipped with a high-end Graphics processing unit (GPU)).
-Therefore, an external server is used for live vision data processing.
-In our design we envision a computational server hosting a set of computer vision algorithms implemented and exposed via web services: faster Regions with convolutional neural network features (faster R-CNN) object detector \cite{Ren}, trained to detect important objects, Convolutional neural network (CNN) and Recurrent neural network-based (RNN) scene descriptor \cite{Liu}, which provides textual annotation of a given RGB image, place recognition \cite{Ohn-Bar}, face detection and recognition \cite{Amos}, obstacle detection \cite{Laina}, action recognition \cite{Valor}, among others.
+Although modern high-end smartphones are powerful computational devices, many computer vision algorithms  require hardware of significantly higher processing capabilities (e.g., a server equipped with a high-end Graphics Processing Unit (GPU)).
+Therefore, an external server is used for live video data processing.
+In our design we envision a computational server hosting a set of computer vision algorithms implemented and exposed via web services: faster Regions with Convolutional Neural Network features (faster R-CNN) object detector \cite{Ren}, trained to detect important objects, Convolutional Neural Network (CNN) and Recurrent Neural Network-based (RNN) scene descriptor \cite{Liu}, which provides textual annotation of a given RGB image, place recognition \cite{Ohn-Bar}, face detection and recognition \cite{Amos}, obstacle detection \cite{Laina}, action recognition \cite{Valor}, among others.
 After video analysis is completed on the server side, results are transmitted back to the smartphone component and represented to the user through the aforementioned UI.
@@
 The user interacts with the system through gestures, voice commands or specifically designed user interface on the smartphone.
-User input is required for selecting operation mode of the system, i.e., switching between Optical character recognition (OCR), currency recognition, object detection, navigation aid and other available functions.
+User input is required for selecting operation mode of the system, i.e., switching between Optical Character Recognition (OCR), currency recognition, object detection, navigation aid and other available functions.
 
@@
 These models are now well supported by software libraries (e.g., \cite{Tensorflow}) and dedicated processing hardware is built-in even in relatively low-power computational devices, such as smartphones.
-These devices are also equipped with 4G Internet connectivity and sufficient computational power to perform partial or in certain cases even full vision data processing locally.
+These devices are also equipped with 4G Internet connectivity and sufficient computational power to perform partial or in certain cases even full visual data processing locally.
 The maturity of the aforementioned technologies suggest that our proposed computational aid for visually impaired persons may be highly feasible.
@@
 Similar functionality has been previously addressed by research communities \cite{Caraiman}-\cite{Zientara} and industry \cite{orcam}\cite{horus}.
-The main difference between the aforementioned commercial solutions and the proposed system is the ability to utilize external resources for computationally intensive image or video processing tasks.
+The main difference between the aforementioned commercial solutions and the proposed system is the ability to utilize external resources for computationally intensive image and video processing tasks.
 While the availability of the computational power could be seen as the main advantage, it comes with high cost - dependency on a well-functioning mobile broadband.
 The development of the high-speed mobile networks (4G and 5G in the nearest future) is likely to make the major limitation of the proposed architecture obsolete, especially in densely populated areas containing many hazards for the blind.
-On the other side, increasing computational capacity of smartphones also may allow to conduct more advanced image or video processing locally.
-\textcolor{red}{Although not always technically possible for more complex algorithm systems, local  implementations are especially important in areas, where wireless Internet connectivity is not available, since they allow to preserve at least partial functionality of the system.} Combined audio/tactile interface may also be more convenient for the users, allowing to provide feedback in a more efficient way than using tactile or audio interfaces separately.
+On the other side, increasing computational power of smartphones may also allow to perform more advanced image and video processing locally.
+\textcolor{red}{Although not always technically feasible, local  processing is especially important in low connectivity areas to ensure at least partial functionality of the system.} Combined audio/tactile interface may also be more convenient for the users, allowing to provide feedback in a more efficient way than using tactile or audio interfaces separately.
 
 Both open source (e.g., \cite{Tensorflow}) and state of the art commercial computer vision software libraries (e.g., \cite{Verilook}) may be applied implementing the suggested architecture.
-Moreover, detalization and specification of the suggested system's hardware components following open hardware approach - by providing open repository with the detailed list of electronics components, schematics, and 3D models of mechanical parts, could provide a solid basis for semi-standard reference platform for the researchers in the field.
+Moreover, a detailed specification of the suggested hardware components, following open hardware approach (providing an open repository containing a detailed list of electronic components, schematics, and 3D models of mechanical parts) could provide a solid basis for semi-standard reference platform for the researchers in the field.
 
@@
 It may improve route planning and identification of objects of interest (for instance, doors, stairs, elevators, bus stops, etc.).
-This functionality corresponds with the main requirement for electronic travelling aids highlighted by the end users - direction and distance estimation to a selected object.
+This functionality corresponds with the main requirement for electronic travelling aids highlighted by the end-users - direction and distance estimation to a selected object.
 The proposed hardware architecture can be used as basis for various computer vision-based software modules, aiming to assist visually impaired users in daily activities (e.g., outdoor/indoor navigation, object/face recognition, obstacle detection, etc.).
@@
 01.2.2-LMT-K-718.
-
 %The authors would like to thank...

### 2019-01-21 bare_conf.tex
small typo fix.

@@
 For instance, indicating the direction of a detected object with a vibromotor on the corresponding area on the forehead belt, instead of providing audio description.
-More research is needed to clarify how various types of guidance information should be represented to the user in the most convenient and efficient way \textcolor{red}{ For instance, the detected objects could be presented to the user in a configurable order, based on the subjective importance of particular object classes or other personalized criteria.} USB and Wifi data links can be used for bidirectional data transmission between UI and smartphone component.
+More research is needed to clarify how various types of guidance information should be represented to the user in the most convenient and efficient way.
+\textcolor{red}{ For instance, the detected objects could be presented to the user in a configurable order, based on the subjective importance of particular object classes or other personalized criteria.} USB and Wifi data links can be used for bidirectional data transmission between UI and smartphone component.
 
@@
 
-\bibitem{Amos} B. Amos, B. Ludwiczuk, and M. Satyanarayanan. Openface:
-A general-purpose face recognition library with mobile applications. Technical report, CMU-CS-16-118, CMU School of Computer Science, 2016.
+\bibitem{Amos} B.
+Amos, B.
+Ludwiczuk, and M.
+Satyanarayanan.
+Openface: A general-purpose face recognition library with mobile applications.
+Technical report, CMU-CS-16-118, CMU School of Computer Science, 2016.
 
@@
 40, issue 6, pp.
-1510 - 1517, 2016.
+1510-1517, 2016.
 

### 2019-01-21 bare_conf.tex
language corrections are now completed

@@
 More than $250$ million people worldwide have moderate to severe vision impairment, while ($\approx 36$ million are blind) \cite{Bourne}.
-During the past decades significant effort was devoted to develop computer vision and other sensor-based aids (e.g., \cite{Caraiman}-\cite{Zientara}) for helping the blind and visually impaired users to perceive the surrounding world better.
-However, computer vision is a rapidly evolving field; systems based on the aforementioned approaches become outdated in a relatively short time and often lack accuracy and reliability in real-world conditions in comparison to the state-of-the-art technologies.
+During the past decades significant effort was devoted to develop computer vision and other sensor-based aids \cite{Caraiman}-\cite{Zientara} for helping the blind and visually impaired users to perceive the surrounding world better.
+However, computer vision is a rapidly evolving field; the proposed systems become outdated in a relatively short time and often lack accuracy and reliability in real-world conditions in comparison to the state-of-the-art technologies.
 In this article, we describe a system, which employs modern computer vision techniques for compensation of lost or impaired vision function in humans.
@@
 Such systems often lack convenience and bring additional complexity into daily tasks, which visually impaired people currently manage by the help of a white cane.
-This project puts major emphasis on developing a tool, which seamlessly integrates with the hardware visually impaired persons already have on-hand and are used to (smartphone).
+This project puts major emphasis on developing a tool, which seamlessly integrates with the hardware visually impaired persons already have on-hand and are used to (a smartphone).
 This paper describes a high level architecture of the technology aid for visually impaired people utilizing the latest achievements in the field of computer vision.
 
-\textcolor{red}{We begin our presentation with Section~\ref{sec:method}, describing the methodological foundations of this research.
+\textcolor{red}{This paper is structured as follows.
+Section~\ref{sec:method}, describes the methodological foundations of this research.
 Section~\ref{sec:results} focuses on the architecture of the suggested human vision compensation system.
@@
 %Darius
-To have an overview on research progress on assistive technologies for the blind during the last ten years, a systematic literature review in three major research databases (Medline, IEEE xplore and ACM DL) was conducted.
+To have an overview on research progress on assistive technologies for the blind, a systematic literature review in three major research databases (Medline, IEEE xplore and ACM DL) was conducted covering publication period of 10 years.
 It revealed increasing research interest in the field (84 related publications were identified, while 17 were characterized as highly relevant for this project) and provided better understanding of the state-of-the-art in applying computer vision technologies to address the needs of the blind.
@@
 The search was performed in the following databases: EspaceNet, GooglePatents, USPTO, PatentScope, FreePatentsOnline.
-It revealed several technological trends in the field of assistive technologies for the blind persons.
+It revealed several technological trends in the field of assistive technologies for the blind.
 %Systemic review of the relevant patents and patent applications worldwide was performed using online services of the following databases: EspaceNet, GooglePatents, USPTO, PatentScope, FreePatentsOnline.
@@
 
-User-centered design sessions with visually impaired persons and analysis of the aforementioned data sources provided substantial input for the design of the proposed system (Figure~\ref{fig:schematics}).
+Participatory design sessions with visually impaired individuals and analysis of the aforementioned data sources provided substantial input for the design of the proposed system (Figure~\ref{fig:schematics}).
 The process made it clear that understanding of the user needs was limited in the project team.
-Based on the results of the user-centered design process, scientific publications and patent analysis, we present the outline of the system for impaired human vision compensation.
+Based on the results of the participatory design sessions, scientific publications and patent analysis, we present the outline of the system for impaired human vision compensation.
 
@@
 % User interface
-UI consists of a wearable forehead belt, integrating RGB and depth cameras, Inertial measurement unit (IMU), tactile feedback device and bone conduction headphones.
+UI consists of a wearable forehead belt, integrating RGB and depth cameras, Inertial Measurement Unit (IMU), tactile feedback device and bone conduction headphones.
 Although more expensive than standard ones, bone conduction headphones do not block the ears and allow the user to perceive audio information from the surrounding environment and the system at the same time, which is essential for the visually impaired people.
@@
 More research is needed to clarify how various types of guidance information should be represented to the user in the most convenient and efficient way.
-\textcolor{red}{ For instance, the detected objects could be presented to the user in a configurable order, based on the subjective importance of particular object classes or other personalized criteria.} USB and Wifi data links can be used for bidirectional data transmission between UI and smartphone component.
+\textcolor{red}{For instance, detected objects could be presented to the user in a configurable order, based on the importance of particular object classes to the user or other personalized criteria.} USB and Wifi data links can be used for bidirectional data transmission between UI and smartphone component.
 
@@
 The user interacts with the system through gestures, voice commands or specifically designed user interface on the smartphone.
-User input is required for selecting operation mode of the system, i.e., switching between Optical Character Recognition (OCR), currency recognition, object detection, navigation aid and other available functions.
+User input is required for selecting operation mode of the system, i.e., switching between Optical Character Recognition (OCR), currency recognition, object detection, navigation and other available functions.
 
@@
 % Pamineti mobilenet ir pan.
-Computer vision technology is under rapid development and during the last years made a major breakthrough in performance and efficiency.
+Computer vision technology is under a rapid development and during the last years made a major breakthrough in terms of performance and efficiency.
 Deep learning neural networks, which are de facto standard in modern image/video processing in many real-world problems allow to achieve accuracies, similar to that of human decision (e.g., face recognition \cite{Amos}, object detection \cite{Ren}, among others).
 These models are now well supported by software libraries (e.g., \cite{Tensorflow}) and dedicated processing hardware is built-in even in relatively low-power computational devices, such as smartphones.
-These devices are also equipped with 4G Internet connectivity and sufficient computational power to perform partial or in certain cases even full visual data processing locally.
+These devices are also equipped with 4G Internet connectivity and sufficient computational power to perform partial or, in certain cases, even full visual data processing locally.
 The maturity of the aforementioned technologies suggest that our proposed computational aid for visually impaired persons may be highly feasible.
@@
 While the availability of the computational power could be seen as the main advantage, it comes with high cost - dependency on a well-functioning mobile broadband.
-The development of the high-speed mobile networks (4G and 5G in the nearest future) is likely to make the major limitation of the proposed architecture obsolete, especially in densely populated areas containing many hazards for the blind.
-On the other side, increasing computational power of smartphones may also allow to perform more advanced image and video processing locally.
+The development of the high-speed mobile networks (4G and 5G in the nearest future) is likely to make this limitation obsolete, especially in densely populated areas containing many hazards for the blind.
+Moreover, increasing computational power of smartphones may also allow to perform more advanced image and video processing locally.
 \textcolor{red}{Although not always technically feasible, local  processing is especially important in low connectivity areas to ensure at least partial functionality of the system.} Combined audio/tactile interface may also be more convenient for the users, allowing to provide feedback in a more efficient way than using tactile or audio interfaces separately.
 
-Both open source (e.g., \cite{Tensorflow}) and state of the art commercial computer vision software libraries (e.g., \cite{Verilook}) may be applied implementing the suggested architecture.
+Both open source (e.g., \cite{Tensorflow}) and state-of-the-art commercial computer vision software libraries (e.g., \cite{Verilook}) may be applied implementing the suggested architecture.
 Moreover, a detailed specification of the suggested hardware components, following open hardware approach (providing an open repository containing a detailed list of electronic components, schematics, and 3D models of mechanical parts) could provide a solid basis for semi-standard reference platform for the researchers in the field.
@@
 This functionality corresponds with the main requirement for electronic travelling aids highlighted by the end-users - direction and distance estimation to a selected object.
-The proposed hardware architecture can be used as basis for various computer vision-based software modules, aiming to assist visually impaired users in daily activities (e.g., outdoor/indoor navigation, object/face recognition, obstacle detection, etc.).
+The proposed hardware architecture can be used as a basis for various computer vision-based software modules, aiming to assist visually impaired users in daily activities (e.g., outdoor/indoor navigation, object/face recognition, obstacle detection, etc.).
 
@@
 Advanced technology (high-end smartphone, depth camera, tactile feedback device, bone conduction headphones) is needed to ensure reliable functioning of the system.
-A combination of such components may be perceived as costly by the end users.
+A combination of such components may be perceived as costly by the end-users.
 More research is needed to demonstrate the cost-benefit analysis of the system in real-world scenarios.
@@
 
-\bibitem{Amos} B.
-Amos, B.
-Ludwiczuk, and M.
-Satyanarayanan.
-Openface: A general-purpose face recognition library with mobile applications.
-Technical report, CMU-CS-16-118, CMU School of Computer Science, 2016.
+\bibitem{Amos} B. Amos, B. Ludwiczuk, and M. Satyanarayanan. Openface:
+A general-purpose face recognition library with mobile applications. Technical report, CMU-CS-16-118, CMU School of Computer Science, 2016.
 
@@
 40, issue 6, pp.
-1510-1517, 2016.
+1510 - 1517, 2016.
 

### 2019-01-23 bare_conf.tex
changes from Povilas and languege corrections are merged
Typo fix.

@@
 
-The key part of the proposed system is a smartphone device, connecting User interface (UI) and data processing components into a well-functioning ecosystem.
+The key part of the proposed system is a smartphone device, connecting User Interface (UI) and data processing components into a well-functioning ecosystem.
 Smartphone was selected due to its high availability and capability to perform required computations or forward visual information for processing to the external server via the Internet.

### 2019-01-23 bare_conf.tex
changes before commit.

--- 2019-01-21 bare_conf.tex
@@
 \authorcr Vilnius, Lithuania
-\authorcr Email: {\tt audrius.indriulionis@gmail.com}}
+\authorcr Email: {\tt audrius.indriulionis@vgtu.lt}}
 
@@
 %\boldmath
-This paper presents a high-level architecture of a computer vision-based system for partial compensation of lost or impaired human vision.
+This paper presents a high-level architecture for computer vision-based system for partial compensation of lost or impaired human vision.
 It combines standard smartphone device, external deep learning-based image processing infrastructure and audio/tactile user interface.
-The proposed architecture is based on input from user-centered design process, involving end-users into system development.
-The paper discusses user needs and expectations for electronic travelling aids for the blind and highlights limitations of the existing solutions.
+The proposed architecture is based on  input from user-centered design process, involving end users into system development.
+The paper discusses user needs and expectations towards electronic travelling aids for the blind and highlights limitations of the existing solutions.
 The suggested architecture may be used as a basis for developing computer vision-based tools for visually impaired individuals.
@@
 More than $250$ million people worldwide have moderate to severe vision impairment, while ($\approx 36$ million are blind) \cite{Bourne}.
-During the past decades significant effort was devoted to develop computer vision and other sensor-based aids (e.g., \cite{Caraiman}-\cite{Zientara}) for helping the blind and visually impaired users to perceive the surrounding world better.
+During the past decades significant effort was devoted to develop computer vision and other sensor based aids (e.g., \cite{Caraiman}-\cite{Zientara}) for helping the blind and visually impaired users to perceive the surrounding world better.
 However, computer vision is a rapidly evolving field; systems based on the aforementioned approaches become outdated in a relatively short time and often lack accuracy and reliability in real-world conditions in comparison to the state-of-the-art technologies.
@@
 
-Following the principles of the participatory design \cite{Kensing}\cite{Carroll} we included end-users into system design process.
+Following the principles of the participatory design \cite{Kensing}\cite{Carroll} we included the end-users into the design process of the system.
 Two visually impaired persons participated in discussion and focus group meetings together with the project team to identify the key properties of the solution.
@@
 %Darius
-To have an overview on research progress on assistive technologies for the blind during the last ten years, a systematic literature review in three major research databases (Medline, IEEE xplore and ACM DL) was conducted.
+To have an overview on research progress on assistive technologies for the blind in the last ten years, a systematic literature review in three major research databases (Medline, IEEE xplore and ACM DL) was conducted.
 It revealed increasing research interest in the field (84 related publications were identified, while 17 were characterized as highly relevant for this project) and provided better understanding of the state-of-the-art in applying computer vision technologies to address the needs of the blind.
@@
 It revealed several main technological trends in the area of assistive technologies for the blind persons.
-Based on the aforementioned reviews, our insights are presented in the Results section.
+Based on the aforementioned methodical reviews, our insights are presented in the Results section.
 
@@
 For instance, indicating the direction of a detected object with a vibromotor on the corresponding area on the forehead belt, instead of providing audio description.
-More research is needed to clarify how various types of guidance information should be represented to the user in the most convenient and efficient way.
-\textcolor{red}{ For instance, the detected objects could be presented to the user in a configurable order, based on the subjective importance of particular object classes or other personalized criteria.} USB and Wifi data links can be used for bidirectional data transmission between UI and smartphone component.
+More research is needed to clarity how various types of guidance information should be represented to the user in the most convenient and efficient way \textcolor{red}{(e.g.
+presentation order of object detections may be configured by the system's user according to subjective importance of particular object classes or other personalized criteria).} USB and Wifi data links can be used for bidirectional data transmission between UI and smartphone component.
 
@@
 %visus sutrumpinimus reikia pirma parasyt pilnai, pvz Neural Network (NN)
-Although modern high-end smartphones are powerful computational devices, many computer vision algorithms  require hardware of significantly higher processing capabilities (e.g., a server equipped with a high-end Graphics Processing Unit (GPU)).
-Therefore, an external server is used for live video data processing.
-In our design we envision a computational server hosting a set of computer vision algorithms implemented and exposed via web services: faster Regions with Convolutional Neural Network features (faster R-CNN) object detector \cite{Ren}, trained to detect important objects, Convolutional Neural Network (CNN) and Recurrent Neural Network-based (RNN) scene descriptor \cite{Liu}, which provides textual annotation of a given RGB image, place recognition \cite{Ohn-Bar}, face detection and recognition \cite{Amos}, obstacle detection \cite{Laina}, action recognition \cite{Valor}, among others.
+Although modern high-end smartphones are powerful computational devices, many computer vision algorithms  require hardware of significantly higher processing power (e.g., a server equipped with a high-end Graphics processing unit (GPU)).
+Therefore, an external server is used for live vision data processing.
+In our design we envision a computational server hosting a set of computer vision algorithms implemented and exposed via web services: faster Regions with convolutional neural network features (faster R-CNN) object detector \cite{Ren}, trained to detect important objects, Convolutional neural network (CNN) and Recurrent neural network-based (RNN) scene descriptor \cite{Liu}, which provides textual annotation of a given RGB image, place recognition \cite{Ohn-Bar}, face detection and recognition \cite{Amos}, obstacle detection \cite{Laina}, action recognition \cite{Valor}, among others.
 After video analysis is completed on the server side, results are transmitted back to the smartphone component and represented to the user through the aforementioned UI.
@@
 The user interacts with the system through gestures, voice commands or specifically designed user interface on the smartphone.
-User input is required for selecting operation mode of the system, i.e., switching between Optical Character Recognition (OCR), currency recognition, object detection, navigation aid and other available functions.
+User input is required for selecting operation mode of the system, i.e., switching between Optical character recognition (OCR), currency recognition, object detection, navigation aid and other available functions.
 
@@
 These models are now well supported by software libraries (e.g., \cite{Tensorflow}) and dedicated processing hardware is built-in even in relatively low-power computational devices, such as smartphones.
-These devices are also equipped with 4G Internet connectivity and sufficient computational power to perform partial or in certain cases even full visual data processing locally.
+These devices are also equipped with 4G Internet connectivity and sufficient computational power to perform partial or in certain cases even full vision data processing locally.
 The maturity of the aforementioned technologies suggest that our proposed computational aid for visually impaired persons may be highly feasible.
@@
 Similar functionality has been previously addressed by research communities \cite{Caraiman}-\cite{Zientara} and industry \cite{orcam}\cite{horus}.
-The main difference between the aforementioned commercial solutions and the proposed system is the ability to utilize external resources for computationally intensive image and video processing tasks.
+The main difference between the aforementioned commercial solutions and the proposed system is the ability to utilize external resources for computationally intensive image or video processing tasks.
 While the availability of the computational power could be seen as the main advantage, it comes with high cost - dependency on a well-functioning mobile broadband.
 The development of the high-speed mobile networks (4G and 5G in the nearest future) is likely to make the major limitation of the proposed architecture obsolete, especially in densely populated areas containing many hazards for the blind.
-On the other side, increasing computational power of smartphones may also allow to perform more advanced image and video processing locally.
-\textcolor{red}{Although not always technically feasible, local  processing is especially important in low connectivity areas to ensure at least partial functionality of the system.} Combined audio/tactile interface may also be more convenient for the users, allowing to provide feedback in a more efficient way than using tactile or audio interfaces separately.
+On the other side, increasing computational capacity of smartphones also may allow to conduct more advanced image or video processing locally.
+\textcolor{red}{Although not always technically possible for more complex algorithm systems, local  implementations are especially important in areas, where wireless Internet connectivity is not available, since they allow to preserve at least partial functionality of the system.} Combined audio/tactile interface may also be more convenient for the users, allowing to provide feedback in a more efficient way than using tactile or audio interfaces separately.
 
 Both open source (e.g., \cite{Tensorflow}) and state of the art commercial computer vision software libraries (e.g., \cite{Verilook}) may be applied implementing the suggested architecture.
-Moreover, a detailed specification of the suggested hardware components, following open hardware approach (providing an open repository containing a detailed list of electronic components, schematics, and 3D models of mechanical parts) could provide a solid basis for semi-standard reference platform for the researchers in the field.
+Moreover, detalization and specification of the suggested system's hardware components following open hardware approach - by providing open repository with the detailed list of electronics components, schematics, and 3D models of mechanical parts, could provide a solid basis for semi-standard reference platform for the researchers in the field.
 
@@
 It may improve route planning and identification of objects of interest (for instance, doors, stairs, elevators, bus stops, etc.).
-This functionality corresponds with the main requirement for electronic travelling aids highlighted by the end-users - direction and distance estimation to a selected object.
+This functionality corresponds with the main requirement for electronic travelling aids highlighted by the end users - direction and distance estimation to a selected object.
 The proposed hardware architecture can be used as basis for various computer vision-based software modules, aiming to assist visually impaired users in daily activities (e.g., outdoor/indoor navigation, object/face recognition, obstacle detection, etc.).
@@
 01.2.2-LMT-K-718.
+
 %The authors would like to thank...
@@
 A.
-Bourne et al.
-Vision Loss Expert Group.
-Magnitude, temporal trends, and projections of the global prevalence of blindness and distance and near vision impairment: a systematic review and meta-analysis.
+Bourne et al., Magnitude, temporal trends, and projections of the global prevalence of blindness and distance and near vision impairment: a systematic review and meta-analysis.
 Lancet Glob Health.
@@
 
-\bibitem{Caraiman} S. Caraiman et al. A. Computer Vision for the Visually Impaired: the Sound of Vision System. IEEE International Conference on Computer Vision Workshops, pp. 1480-1489, 2017.
+\bibitem{Caraiman} S. Caraiman et al., Computer Vision for the Visually Impaired: the Sound of Vision System. IEEE International Conference on Computer Vision Workshops, pp. 1480-1489, 2017.
 
@@
 A.
-Stockman.
-A survey of assistive technologies and applications for blind users on mobile platforms: a review and foundation for research.
+Stockman, A survey of assistive technologies and applications for blind users on mobile platforms: a review and foundation for research.
 Journal on Multimodal User Interfaces.
@@
 Poggi and S.
-Mattoccia.
-A wearable mobility aid for the visually impaired based on embedded 3d vision and deep learning.
+Mattoccia, A wearable mobility aid for the visually impaired based on embedded 3d vision and deep learning.
 Proceeding of IEEE Symposium on Compututers and Communication, pp.
@@
 
-\bibitem{Zientara} P. A. Zientara at al. Third Eye: A shopping assistant for the visually impaired. Computer Vol. 50, Issue 2, pp. 16-24, 2017.
+\bibitem{Zientara} P. A. Zientara at al., Third Eye: A shopping assistant for the visually impaired. Computer Vol. 50, Issue 2, pp. 16-24, 2017.
 
@@
 Nassrallah, and M.
-Eldor.
-Smart Assistive Navigation System for Blind and Visually Impaired Individuals.
+Eldor, Smart Assistive Navigation System for Blind and Visually Impaired Individuals.
 2015 International Conference on Advances in Biomedical Engineering (ICABME), pp.
@@
 B.
-Simon.
-Obstacle detectors for visually impaired people.
+Simon, Obstacle detectors for visually impaired people.
 2014 International Conference on Optimization of Electrical and Electronic Equipment (OPTIM),  pp.
@@
 
-\bibitem{Kensing} F. Kensing, J. Simonsen, and K. B\o dker. MUST: A Method for Participatory Design. Human Computer Interaction, vol. 13, no. 2, pp. 167-198, Jun. 1998.
+\bibitem{Kensing} F. Kensing, J. Simonsen, and K. B\o dker, MUST: A Method for Participatory Design. Human Computer Interaction, vol. 13, no. 2, pp. 167-198, Jun. 1998.
 
-\bibitem{Carroll} J. M. Carroll and M. B. Rosson. Participatory design in community informatics. Des. Stud., vol. 28, no. 3, pp. 243-261, May 2007.
+\bibitem{Carroll} J. M. Carroll and M. B. Rosson, Participatory design in community informatics. Des. Stud., vol. 28, no. 3, pp. 243-261, May 2007.
 
@@
 Girshick, and J.
-Sun.
-Faster R-CNN: Towards real-time object detection with region proposal networks.
+Sun,  Faster R-CNN: Towards real-time object detection with region proposal networks.
 In Advances in neural information processing systems, pp.
@@
 
-\bibitem{Liu} Ch. Liu, J. Mao, F. Sha, and A. Yuille. Attention Correctness in Neural Image Captioning. Proceedings of the Thirty-First AAAI Conference on Artificial Intelligence, pp. 4176-4182, 2017.
+\bibitem{Liu} Ch. Liu, J. Mao, F. Sha, and A. Yuille, Attention Correctness in Neural Image Captioning. Proceedings of the Thirty-First AAAI Conference on Artificial Intelligence, pp. 4176-4182, 2017.
 
-\bibitem{Ohn-Bar} E. Ohn-Bar, K. Kitani, and Ch. Asakawa. Personalized Dynamics Models for Adaptive Assistive Navigation Interfaces. arXiv:1804.04118, [cs.LG], 2018.
+\bibitem{Ohn-Bar} E. Ohn-Bar, K. Kitani, and Ch. Asakawa, Personalized Dynamics Models for Adaptive Assistive Navigation Interfaces. arXiv:1804.04118, [cs.LG], 2018.
 
-\bibitem{Amos} B.
-Amos, B.
-Ludwiczuk, and M.
-Satyanarayanan.
-Openface: A general-purpose face recognition library with mobile applications.
-Technical report, CMU-CS-16-118, CMU School of Computer Science, 2016.
+\bibitem{Amos} B. Amos, B. Ludwiczuk, and M. Satyanarayanan, Openface:
+A general-purpose face recognition library with mobile applications. Technical report, CMU-CS-16-118, CMU School of Computer Science, 2016.
 
@@
 Tombari, and N.
-Navab.
-Deeper depth prediction with fully convolutional residual networks.
+Navab, Deeper depth prediction with fully convolutional residual networks.
 Fourth International Conference on 3D Vision (3DV), pp.
@@
 Laptev, and C.
-Schmid.
-Long-Term Temporal Convolutions for Action Recognition.
+Schmid, Long-Term Temporal Convolutions for Action Recognition.
 IEEE Transactions on Pattern Analysis and Machine Intelligence.
@@
 40, issue 6, pp.
-1510-1517, 2016.
+1510 - 1517, 2016.
 
-\bibitem{Tensorflow} M. Abadi et al. TensorFlow: Large-Scale Machine Learning on Heterogeneous Distributed Systems, arXiv:1603.04467, 2016.
+\bibitem{Tensorflow} M. Abadi et al., TensorFlow: Large-Scale Machine Learning on Heterogeneous Distributed Systems, arXiv:1603.04467, 2016.
 

### 2019-01-23 bare_conf.tex
Bibliography fixes.

--- 2019-01-23 bare_conf.tex
@@
 \usepackage{blindtext}
+\usepackage{dirtytalk}
 
@@
 A.
-Bourne et al.
-Vision Loss Expert Group.
-Magnitude, temporal trends, and projections of the global prevalence of blindness and distance and near vision impairment: a systematic review and meta-analysis.
-Lancet Glob Health.
-Vol.
+Bourne et al., \say{Magnitude, temporal trends, and projections of the global prevalence of blindness and distance and near vision impairment: a systematic review and meta-analysis,} Lancet Global Health, Vol.
 5(9), pp.
@@
 
-\bibitem{Caraiman} S. Caraiman et al. A. Computer Vision for the Visually Impaired: the Sound of Vision System. IEEE International Conference on Computer Vision Workshops, pp. 1480-1489, 2017.
+\bibitem{Caraiman} S. Caraiman et al., \say{A. Computer Vision for the Visually Impaired: the Sound of Vision System,} IEEE International Conference on Computer Vision Workshops, pp. 1480-1489, 2017.
 
@@
 A.
-Stockman.
-A survey of assistive technologies and applications for blind users on mobile platforms: a review and foundation for research.
-Journal on Multimodal User Interfaces.
-Vol.
+Stockman, \say{A survey of assistive technologies and applications for blind users on mobile platforms: a review and foundation for research,} Journal on Multimodal User Interfaces, Vol.
 9, issue 4,  pp.
@@
 Poggi and S.
-Mattoccia.
-A wearable mobility aid for the visually impaired based on embedded 3d vision and deep learning.
-Proceeding of IEEE Symposium on Compututers and Communication, pp.
+Mattoccia, \say{A wearable mobility aid for the visually impaired based on embedded 3d vision and deep learning,} Proceedings of IEEE Symposium on Compututers and Communication, pp.
 208-213, 2016.
 
-\bibitem{Zientara} P. A. Zientara at al. Third Eye: A shopping assistant for the visually impaired. Computer Vol. 50, Issue 2, pp. 16-24, 2017.
+\bibitem{Zientara} P. A. Zientara at al., \say{Third Eye: A shopping assistant for the visually impaired,} Computer, Vol. 50, Issue 2, pp. 16-24, 2017.
 
@@
 Nassrallah, and M.
-Eldor.
-Smart Assistive Navigation System for Blind and Visually Impaired Individuals.
-2015 International Conference on Advances in Biomedical Engineering (ICABME), pp.
+Eldor, \say{Smart Assistive Navigation System for Blind and Visually Impaired Individuals,} 2015 International Conference on Advances in Biomedical Engineering (ICABME), pp.
 162-165, 2015.
@@
 B.
-Simon.
-Obstacle detectors for visually impaired people.
-2014 International Conference on Optimization of Electrical and Electronic Equipment (OPTIM),  pp.
+Simon,    \say{Obstacle detectors for visually impaired people,} 2014 International Conference on Optimization of Electrical and Electronic Equipment (OPTIM),  pp.
 809-816, 2014.
 
-\bibitem{Kensing} F. Kensing, J. Simonsen, and K. B\o dker. MUST: A Method for Participatory Design. Human Computer Interaction, vol. 13, no. 2, pp. 167-198, Jun. 1998.
+\bibitem{Kensing} F. Kensing, J. Simonsen, and K. B\o dker, \say{MUST: A Method for Participatory Design,} Human Computer Interaction, Vol. 13, Issue 2, pp. 167-198, Jun. 1998.
 
-\bibitem{Carroll} J. M. Carroll and M. B. Rosson. Participatory design in community informatics. Des. Stud., vol. 28, no. 3, pp. 243-261, May 2007.
+\bibitem{Carroll} J. M. Carroll and M. B. Rosson, \say{Participatory design in community informatics,} Design Studies, Vol. 28, Issue 3, pp. 243-261, May 2007.
 
@@
 Girshick, and J.
-Sun.
-Faster R-CNN: Towards real-time object detection with region proposal networks.
-In Advances in neural information processing systems, pp.
+Sun, \say{Faster R-CNN: Towards real-time object detection with region proposal networks,} Advances in Neural Information Processing Systems, pp.
 91-99, 2015.
 
-\bibitem{Liu} Ch. Liu, J. Mao, F. Sha, and A. Yuille. Attention Correctness in Neural Image Captioning. Proceedings of the Thirty-First AAAI Conference on Artificial Intelligence, pp. 4176-4182, 2017.
+\bibitem{Liu} Ch.
+Liu, J.
+Mao, F.
+Sha, and A.
+Yuille, \say{Attention Correctness in Neural Image Captioning,} Proceedings of the Thirty-First AAAI Conference on Artificial Intelligence, pp.
+4176-4182, 2017.
 
-\bibitem{Ohn-Bar} E. Ohn-Bar, K. Kitani, and Ch. Asakawa. Personalized Dynamics Models for Adaptive Assistive Navigation Interfaces. arXiv:1804.04118, [cs.LG], 2018.
+\bibitem{Ohn-Bar} E. Ohn-Bar, K. Kitani, and Ch. Asakawa, \say{Personalized Dynamics Models for Adaptive Assistive Navigation Interfaces,} arXiv:1804.04118, [cs.LG], 2018.
 
@@
 Ludwiczuk, and M.
-Satyanarayanan.
-Openface: A general-purpose face recognition library with mobile applications.
-Technical report, CMU-CS-16-118, CMU School of Computer Science, 2016.
+Satyanarayanan, \say{Openface: A general-purpose face recognition library with mobile applications,} Technical report, CMU-CS-16-118, CMU School of Computer Science, 2016.
 
@@
 Tombari, and N.
-Navab.
-Deeper depth prediction with fully convolutional residual networks.
-Fourth International Conference on 3D Vision (3DV), pp.
+Navab, \say{Deeper depth prediction with fully convolutional residual networks,} Fourth International Conference on 3D Vision (3DV), pp.
 239-248, 2016.
@@
 Laptev, and C.
-Schmid.
-Long-Term Temporal Convolutions for Action Recognition.
-IEEE Transactions on Pattern Analysis and Machine Intelligence.
+Schmid, \say{Long-Term Temporal Convolutions for Action Recognition,}  IEEE Transactions on Pattern Analysis and Machine Intelligence.
 Vol.
-40, issue 6, pp.
+40, Issue 6, pp.
 1510-1517, 2016.
 
-\bibitem{Tensorflow} M. Abadi et al. TensorFlow: Large-Scale Machine Learning on Heterogeneous Distributed Systems, arXiv:1603.04467, 2016.
+\bibitem{Tensorflow} M. Abadi et al., \say{TensorFlow: Large-Scale Machine Learning on Heterogeneous Distributed Systems,} arXiv:1603.04467, 2016.
 
@@
 
-\bibitem{orcam} Orcam. MyEye 2.0. [Online]. Available from https://www.orcam.com [retrieved: 1 2019].
+\bibitem{orcam} Orcam. MyEye 2.0. [Online]. Available from https://www.orcam.com [Retrieved: January, 2019].
 
-\bibitem{horus} Horus. Horus system. [Online]. Available from http://www.horus.tech [retrieved: 1 2019].
+\bibitem{horus} Horus. Horus system. [Online]. Available from http://www.horus.tech [Retrieved: January, 2019].
 
-\bibitem{Verilook} Neurotechnology, VeriLook SDK. [Online]. Available from https://www.neurotechnology.com/verilook.html [retrieved: 1 2019].
+\bibitem{Verilook} Neurotechnology, VeriLook SDK. [Online]. Available from https://www.neurotechnology.com/verilook.html [Retrieved: January, 2019].
 

### 2019-01-25 bare_conf.tex
small fixes.

@@
 
-\textcolor{red}{This paper is structured as follows.
-Section~\ref{sec:method}, describes the methodological foundations of this research.
+This paper is structured as follows.
+Section~\ref{sec:method} describes the methodological foundations of this research.
 Section~\ref{sec:results} focuses on the architecture of the suggested human vision compensation system.
-Finally, Section~\ref{sec:discussion} summarizes and discusses the results of the conducted analysis.}
+Finally, Section~\ref{sec:discussion} summarizes and discusses the results of the conducted analysis.
 
@@
 More research is needed to clarify how various types of guidance information should be represented to the user in the most convenient and efficient way.
-\textcolor{red}{For instance, detected objects could be presented to the user in a configurable order, based on the importance of particular object classes to the user or other personalized criteria.} USB and Wifi data links can be used for bidirectional data transmission between UI and smartphone component.
+For instance, detected objects could be presented to the user in a configurable order, based on the importance of particular object classes to the user or other personalized criteria.
+USB and Wifi data links can be used for bidirectional data transmission between UI and smartphone component.
 
@@
 Moreover, increasing computational power of smartphones may also allow to perform more advanced image and video processing locally.
-\textcolor{red}{Although not always technically feasible, local  processing is especially important in low connectivity areas to ensure at least partial functionality of the system.} Combined audio/tactile interface may also be more convenient for the users, allowing to provide feedback in a more efficient way than using tactile or audio interfaces separately.
+Although not always technically feasible, local  processing is especially important in low connectivity areas to ensure at least partial functionality of the system.
+Combined audio/tactile interface may also be more convenient for the users, allowing to provide feedback in a more efficient way than using tactile or audio interfaces separately.
 
